### 2014-07-03 Writing/sampling_strategies.tex
on sampling

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\title{On Sampling}
\date{}
\begin{document}
  \maketitle

  \section{Continuous Sampling}
  Consider sampling in a 1D real line $L$. Let $S_{c} = \{q_{x} | \forall x \in L\}$, where $q_{x}$ is a sphere centered at $x$. Let $C(S_{c})$ be the space covered by $S_{c}$.

  \begin{theorem}
  Continuously sample spheres from left to right in the real line $L$, let the set of sphere be $S_{n}$, such that no sphere in $S_{n}$ is centered within any sphere of $S_{n}$. Then $C(S_{n}) = C(S_{c})$.
  \end{theorem}

  Proof:\\

  $\forall x \in L, \exists q_{x} \in S_{c}$, meaning every point in L is covered by one sphere centered at $x$ in $S_{c}$, $C(S_{c}) = L$. If sphere $q_{p}$ is not centered inside any spheres in $S_{n}$, then $q_{p} \in S_{n}$ and $p \in C(S_{n})$. Assume point $p$ is inside some existing spheres centered to the left of $p$, then $p \in C(S_{n})$, but we don't sample spheres at $p$.

  To sum up, if point $p$ is sampled, then $p \in C(S_{c})$ and $p \in C(S_{n})$, if point $p$ is not sampled, still $p \in C(S_{c})$ and $p \in C(S_{n})$. Therefore, $C(S_{n}) = C(S_{c})$.\\

  ---------------------------------------------------------------------- \\

  This holds true also for 2D and 3D cases. If a point $p$ is sampled, then $p \in C(S_{n})$, if $p$ is not sampled, that is because it is already inside some existing spheres, so $p \in C(S_{n})$.

  Continuously sample points that are not inside any sphere is equivalent to continuously sample on the boundary of existing spheres.

  \begin{theorem}
  Continuously sample spheres from left to right in the real line $L$, such that no sphere has radius less than $r_{min}$ and no sphere in $S_{m}$ is centered within any sphere of $S_{n}$. $C(S_{m}) = C(S_{c})$.
  \end{theorem}

  Proof:\\

  For point $p$ that is within $r_{min}$ distance away from obstacles, there exist a point $x$ that has clearance larger than $r_{min}$, such that $|p-x| > 0$, then p is covered by $q_{x}$.

  \includegraphics[scale=0.8]{sample_1_2}

  ---------------------------------------------------------------------- \\

  For 2D and 3D this is different:\\

  \includegraphics[scale=0.8]{sample2D_1_2}  \\

  A possible way to reduce the uncovered area is to more densely sample areas close to obstacles. For example, allow spheres to center inside existing spheres in this area.

  \begin{theorem}
  Let $S_{in}$ be a subset of $S_{m}$ by continuously sampling spheres from left to right in the real line $L$ with inaccurate metric. Assume the metric returns 1/n of the accurate metric, then any point $p$ within $(n-1) \cdot r_{min}$ distance away from obstacles, $p \notin C(S_(in))$.
  \end{theorem}

  Proof:\\

  Assume $p$ is $(n-1) \cdot r_{min}$ distance away from obstacles, if there exists point $x$ that is $n \cdot r_{min}$ distance away from obstacles, then sphere $q_{x}$ has radius $r_{min}$, $p \in q_{x}$.

  If $p$ is $(n-1) \cdot r_{min} - \epsilon$ distance away from obstacles, where $\epsilon >= 0$, we need a point $x$ that is within $n \cdot r_{min} - \frac{n \cdot \epsilon}{n-1}$ distance from obstacle.  The sphere sampled at $x$ has radius less than $r_{min}$ thus will not cover point p.\\

  \includegraphics[scale=0.8]{sample_1_3} \\

  --------------------------------------------------------------------\\

  This is also true for 2D and 3D cases. Introduce a line from the closest point in obstacle in normal direction, then the proof is the same. However, uncovered area as shown in Theorem 1.2 stays still.

  \begin{theorem}
  Let $S_{d}$ be a subset of $S_{in}$ by discrete sampling in the real line. Assume every two neighbor samples are $d$ distance away from each other. If $d <= \frac{r_{min}}{k}, k>=1$, in the worst case, any point $p$ that has clearance less than $\frac{r_{min} \cdot (n-1)}{k \cdot n} + (n-1) \cdot r_{min}$, $p \notin C(S_d)$.
  \end{theorem}

  As is shown in last theorem, the smallest clearance a point $x$ should have in order to be sampled is $n \cdot r_{min}$. $\exists \epsilon > 0$, point $x_{t}$ with clearance $n \cdot r_{min} + d - \epsilon$. The point the sphere $q_{x_{t}}$ can cover has clearance more than  $(n-1) \cdot r_{min} + \frac{d \cdot (n-1)}{n} - \frac{(n-1) \cdot \epsilon}{n}$. The worst case is $\epsilon = 0$, so the clearance is $(n-1) \cdot r_{min} + \frac{d \cdot (n-1)}{n} = (n-1) \cdot r_{min} + \frac{r_{min} \cdot (n-1)}{k \cdot n}$

  \includegraphics[scale=0.8]{sample_1_4}\\

  --------------------------------------------------------------------\\

  In 2D the possible position for $x_{t}$ is a square, it will be a cube in 3D, the result is very similar except for that the uncovered area introduced by Theorem 1.2 is still can't be removed.

\end{document}

### 2014-07-08 Writing/sampling_2d.tex
thinking about sampling in 2D

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{algpseudocode}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\title{Sampling in 2D}
\date{}
\begin{document}
  \maketitle

  Specify the 2D space $D \in \mathbb{R}^2$ to be a square without obstacles. Let $P = \{ p_1, p_2, ..., p_i, ... \}$ be a set of iso-cost contours where $\forall x \in p_i, clearance(x) = c_i$. \\

  For $x\in D$, we define $B_D(x)$ to be the largest closed disc centered at $x$ that is a subset of $D$, i.e., $B_D(x) = \overline{B}( x, \rho_{D}(x) )$, where $\overline{B}( x, \rho_{D}(x) )$ denotes the closed disc of radius $r \geq 0$, centered at $x$, and $\rho_{D}(x) = dist(x, \mathbb{R}^2 \setminus D)$ is the distance to the boundary for points inside $S$, and 0 for points outside $D$.

  The media axis $MA(D)$ of $S$ is defined to be the set of all points $x$ of $D$ whose $B_D(x)$ are maximal. $\cite{steven}$

  %$MA(D) = \{ x \in D | notexists y \in D$ $with$ $B_D(x) subsetneq B_D(y) \}$\\

  %Assume we are continuously sampling in the 2D space. $S_m = \{ B_D(x) | not \exists B_d(x) \in S_m with x' < x \wedge B_D(x') \subset B_D(x), \rho_D(x) \geq r_{min} \}$

  \includegraphics[scale=0.8]{./sampling2d/1.pdf}

  \section{Some Observations}
  \begin{enumerate}
  	\item Continuously sample all points $x \in MA(D)$ totally covers $D$.  $S_{c_{ma}} = \{B_D(x) | \forall x \in MA(D)\}$, $C(S_{c_{ma}}) = D$, where $C(S) = \cup_{\forall b \in S}$.

  	\item Continuously sample all points $x \in P$ totally covers $D$, too.  $S_{c_{iso}} = \{B_D(x) | \forall x \in P\}$, $C(S_{c_{iso}}) = D$.

  	\item Even if we can continuously sample in $MA(D)$, but restrict new balls to center outside existing ones, some areas near obstacles will be uncovered.

    \item Use iso-cost contours to sample small balls can cover these left areas. Questions: How many contours do we need? What are the costs for these contours?

  \end{enumerate}

  \includegraphics[scale=0.8]{./sampling2d/2discs.pdf}

  Assume a series of discs with the same radius $R$ and center on each other's boundary. Connect the centers, points within $\frac{\sqrt{3}R}{2}$ from the connecting line are guaranteed to be covered in the discs chain.\\

  If we want to cover all points in the left areas, assume the point farthest from obstacles has clearance $C_{max}$, we requires $(\frac{\sqrt{3}}{2} + 1) \cdot R = C_{max}$. $R = \frac{ 2\cdot C_{max} }{\sqrt{3}+2}$\\

  Now there are three possible situations:

  1. $R = r_{min}$.

  2. $R < r_{min}$.

  3. $R > r_{min}$.\\

  If $R = r_{min}$, fine, just sample the contour with cost $c_i = r_{min}$.

  If $R < r_{min}$, still sample the contour with cost $c_i = r_{min}$.

  If $R > r_{min}$, sample the contour with cost $c_i = R$. Then repeat the process.

  \includegraphics[scale=0.6]{./sampling2d/3.pdf}

  \section{Sampling on Media Axis}

  In $\cite{steven}$, the author proposed an algorithm to sample on the media axis:\\

  \includegraphics[scale=0.6]{./sampling2d/MAPRM.png}

  By changing the terminal condition in line 9, we can sample discs with any radius. \\

  \section{Growing the Obstacles}

  \begin{thebibliography}{1}

  \bibitem{steven} Steven A. Wilmarth, Nancy M. Amato, Peter F. Stiller. "MAPRM: A Probabilistic Roadmap Planner with Sampling on the Medial Axis of the Free Space", In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pp. 1024-1031, Detroit, MI, May 1999. Also, Technical Report, TR98-0022, Department of Computer Science and Engineering, Texas A \& M University, Nov 1998.

  \end{thebibliography}

\end{document}

### 2014-07-08 Writing/sampling_strategies.tex
thinking about sampling in 2D

@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
 \usepackage{graphicx}
@@
   \section{Continuous Sampling}
-  Consider sampling in a 1D real line $L$. Let $S_{c} = \{q_{x} | \forall x \in L\}$, where $q_{x}$ is a sphere centered at $x$. Let $C(S_{c})$ be the space covered by $S_{c}$.
+  Define $ball( x, r ) = \{ p \in \mathbb{R}: |p-x| \leq r \}$ as a ball in 1D.
+Consider sampling a 1D real line $L = [0, 1]$.
+Denote obstacles $O = \cup_{open intervals \in L}$, free space $F = \{ x \in L/O \}$.
+Let $S_{c} = \{ball(x,r) | \forall x \in L\}$.
+We define the sphere as a close sphere because we are using the upper bound of time for traveling from one configuration to another, the point on the boundary of a sphere is reachable.
+Let $C(S_{c})$ be the space covered by $S_{c}$.
+$C(S) = \cup_{b \in S}.$\\
+
+  \subsection{Outer Sample}  
+  Continuously sample spheres from left to right in the real line $L$, let the set of sphere be $S_{n}$, such that no sphere in $S_{n}$ is centered within any sphere of $S_{n}$.
+$S_{n} = \{ball(x)| \forall x_{i} \in \mathbb{R}, |x_{i} - x_{j}| \geq r_{j}, \forall j \neq i \}$.
 
   \begin{theorem}
-  Continuously sample spheres from left to right in the real line $L$, let the set of sphere be $S_{n}$, such that no sphere in $S_{n}$ is centered within any sphere of $S_{n}$.
-Then $C(S_{n}) = C(S_{c})$.
+  $C(S_{n}) = C(S_{c})$.
   \end{theorem}
@@
 
-  $\forall x \in L, \exists q_{x} \in S_{c}$, meaning every point in L is covered by one sphere centered at $x$ in $S_{c}$, $C(S_{c}) = L$.
-If sphere $q_{p}$ is not centered inside any spheres in $S_{n}$, then $q_{p} \in S_{n}$ and $p \in C(S_{n})$.
-Assume point $p$ is inside some existing spheres centered to the left of $p$, then $p \in C(S_{n})$, but we don't sample spheres at $p$.
+  $\forall p \in L, \exists q=(p,r) \in S_{c}$, meaning every point in L is covered by one sphere centered at $x$ in $S_{c}$, $C(S_{c}) = L$.
+If sphere $q=(p,r)$ is not centered inside any spheres in $S_{n}$, then $q \in S_{n}$ and $p \in C(S_{n})$.
+Assume point $p$ is inside some existing spheres centered to the left of $p$, then $p \in C(S_{n})$.
 
@@
   \begin{theorem}
-  Continuously sample spheres from left to right in the real line $L$, such that no sphere has radius less than $r_{min}$ and no sphere in $S_{m}$ is centered within any sphere of $S_{n}$.
-$C(S_{m}) = C(S_{c})$.
+  Sampling 1D real line $L$, $S_n$ is a finite set if the number of obstacles is finite.
+  \end{theorem}
+
+  Proof:
+
+  Specify the real line to be a line segment $L = \{ x| 0 \leq x \leq 1 \}$, with obstacles in both ends.
+Start sampling from left to right, assume we are now sampling the i-th point $0 < x_i <= 0.25$, $q_i = (x_i, r_i), r_i = x_i$.
+Because $|x_{i} - x_{i-1}| < x_i = r_i$, $q_{i-1} \notin S_n$.
+If $0.25 < x_{i+1} < 0.5$, $S_n = \{ q_{i+1}, q_{i+2} \}$.
+If $x_{i+1} = 0.5$, $S_n = \{ q_{i+1} \}$.
+Every real line segment can be cut into finite number of smaller line segments with obstacles in both ends, if the number of obstacles is finite.
+Therefore $S_n$ is a finite set.
+
+  \subsection{Minimum Radius Spheres}
+
+  Let $S_m$ be a subset of $S_n$, such that no sphere in $S_m$ has radius less than $r_{min}$. $S_m = \{ q=(x,r) | \forall q \in S_n, r \geq r_{min} \}$
+
+  \begin{theorem}
+  $S_m$ is a finite set.
   \end{theorem}
@@
 
-  For point $p$ that is within $r_{min}$ distance away from obstacles, there exist a point $x$ that has clearance larger than $r_{min}$, such that $|p-x| > 0$, then p is covered by $q_{x}$.
+  Consider 2D case first.\\
 
-  \includegraphics[scale=0.8]{sample_1_2}
+  ( The idea is to find some iso-contours, where every point in a contour is equally far from obstacles, and sample on these contours.
+Then prove 3 things: 1.
+finite sample on a contour.
+2.
+finite number of contours.
+3.
+the sampled spheres set satisfies the definition of $S_m$ )  \\
 
-  ---------------------------------------------------------------------- \\
+  To prove this, we need some medium conclusions: \\
 
-  For 2D and 3D this is different:\\
+  1.
+Let $\lambda$ be a finite path in 2D world, $S_p = \{ q = {x,r} | \forall x \in \lambda, r = C \}$, where $C$ is a constant.
+$S_p$ is a finite set.
+This is because every sphere with fixed radius will cover at least $2 \cdot C$ length of the path, as long as the path is finite, the number of spheres sampled in the path will not be infinite.\\
 
-  \includegraphics[scale=0.8]{sample2D_1_2}  \\
+  2. ( By choosing the distance between each contour, the number of contours is finite, because we have minimum distance from obstacles and upper bound distance from obstacles. )\\
 
-  A possible way to reduce the uncovered area is to more densely sample areas close to obstacles. For example, allow spheres to center inside existing spheres in this area.
+  3.
+( Assume we have some initial contours, say voronoi graph edges, and we sample spheres on the contour, if we choose the new contours to be 1/2 distance from obstacles to the existing contours, then sample on the new contour.
+Repeat the process until converge( the new contour is exactly $r_{min}$ away from obstacles).
+).\\
 
+  PS:\\
+
+  Sampling on media axis can be done without computing axis first.
+Read: MAPRM: A Probabilistic Roadmap Planner with Sampling on the Medial Axis of the Free Space, Steven A.
+Wilmarth, Nancy M.
+Amato, Peter F.
+Stiller, In Proc.
+IEEE Int.
+Conf.
+Robot.
+Autom.
+(ICRA), pp.
+1024-1031, Detroit, MI, May 1999.
+Also, Technical Report, TR98-0022, Department of Computer Science and Engineering, Texas A&M University, Nov 1998.
+
+==============================================================================
+
+==============================================================================
+
+==============================================================================\\  
+  %\includegraphics[scale=0.8]{sample_S_m}
+
+  %---------------------------------------------------------------------- \\
+
+  %For 2D and 3D this is different:\\
+
+  %\includegraphics[scale=0.8]{sample2D_S_m}  \\
+
+  %A possible way to reduce the uncovered area is to more densely sample areas close to obstacles. For example, allow spheres to center inside existing spheres in this area.
+
+  \subsection{Inaccurate Metric}
+  Sample spheres continuously in the space such that no sphere is inside existing ones and all spheres have radius more than $r_{min}$.
+Assume the sampling metric gives 1/n of the real distance to obstacles.
+Denote the set of spheres as $S_{in}$.
   \begin{theorem}
-  Let $S_{in}$ be a subset of $S_{m}$ by continuously sampling spheres from left to right in the real line $L$ with inaccurate metric.
-Assume the metric returns 1/n of the accurate metric, then any point $p$ within $(n-1) \cdot r_{min}$ distance away from obstacles, $p \notin C(S_(in))$.
+  Any point $p$ within $(n-1) \cdot r_{min}$ distance away from obstacles, $p \notin C(S_(in))$.
   \end{theorem}
@@
 
-  \includegraphics[scale=0.8]{sample_1_3} \\
+  \includegraphics[scale=0.8]{sample_S_in} \\
 
@@
 
-  \includegraphics[scale=0.8]{sample_1_4}\\
+  \includegraphics[scale=0.8]{sample_S_d}\\
 
@@
 
-  In 2D the possible position for $x_{t}$ is a square, it will be a cube in 3D, the result is very similar except for that the uncovered area introduced by Theorem 1.2 is still can't be removed.
+  In 2D the possible position for $x_{t}$ is a square, it will be a cube in 3D, the result is very similar except for that the uncovered area introduced by Theorem 1.2 is still can't be removed.\\
+
+==============================================================================
+
+==============================================================================
+
+==============================================================================\\
 

### 2014-07-10 MAPRM.py
Media Axis

@@ -1,0 +1,178 @@
+import pygame
+from pygame.locals import *
+import sys, os, time
+import math, copy
+import random
+
+from geometry import *
+from obstacles import *
+from utility import *
+
+class LineSearch:
+	def __init__( self, start, dir ):
+		self.start = start;
+		if dir:
+			self.dir   = dir.normalize();
+		pass;
+
+	def point2WallDist(self, point, width, height):
+		dist = 1000000000;
+		near = None;
+		if width - point.x > point.x:
+			dist = point.x;
+			near = v2( 0, point.y );
+		else:
+			dist = width - point.x;
+			near = v2( width, point.y );
+		if height - point.y > point.y:
+			if dist > point.y:
+				dist = point.y;
+				near = v2( point.x, 0 );
+		else:
+			if dist > height - point.y:
+				dist = height - point.y;
+				near = v2( point.x, height );
+		return near, dist;
+
+	def nearPoint( self, pnt, obstMgr, world ):
+		near, dist = obstMgr.closest_point( pnt );
+		near2Wall, dist2Wall = self.point2WallDist( pnt, world.WIDTH, world.HEIGHT );
+		if dist < dist2Wall:
+			retNear = near; 		retDist = dist;
+		else:
+			retNear = near2Wall;	retDist = dist2Wall;
+		return retNear, retDist;
+
+	def search(self, obstMgr, world, surf=None):
+		lastNear, lastDist  = self.nearPoint( self.start, obstMgr, world );
+		thisNear = copy.copy(lastNear); thisDist = lastDist;
+		idx      = 0;
+		while( lastNear == thisNear ):
+			#lastDist = thisDist;	lastNear = thisNear;
+			pnt = v2( self.start.x+self.dir.x*idx, self.start.y+self.dir.y*idx )
+			if surf:
+				pygame.draw.line( DISPLAYSURF, (100, 100, 100), (int(pnt.x), int(pnt.y)), (int(pnt.x), int(pnt.y)), 1 );
+				for event in pygame.event.get():
+					pass;
+    			pygame.display.update();
+    			#time.sleep( .1 );
+
+			thisNear, thisDist = self.nearPoint( pnt, obstMgr, world );
+			#print '-------'
+			#print "{0}\t{1}\t{2}".format(pnt, lastNear, thisNear);
+			
+			idx += 1;
[…]

### 2014-07-10 obstacles.py

@@ -49,6 +49,17 @@ class Polygon:
 		else:
 			return False;
 
+	def closest_point(self, point):
+		'''get the nearest point in the polygon to a point'''
+		nearestPoint = None;
+		minDist = 100000000;
+		for line in self.lines:
+			temp = line.closest_point( point );
+			dist = math.sqrt( (point.x-temp.x)**2 + (point.y-temp.y)**2);
+			if dist < minDist:
+				nearestPoint = temp;
+				minDist = dist;
+		return nearestPoint, minDist;
 
 
 class ObstManager:
@@ -77,6 +88,24 @@ class ObstManager:
 		'''return the min time for a robot to collide with any obstacles'''
 		dist = self.dist2obsts(robot);
 		return dist / 20.0;
+
+	def closest_point(self, point):
+		'''get the nearest point in obstacles to a point'''
+		minDist = 10000000000;
+		nearest = None;
+		for obst in self.obsts:
+			near, dist = obst.closest_point(point);
+			if dist < minDist:
+				nearest = near;
+				minDist = dist;
+		return nearest, minDist;
+
+	def inside( self, pnt ):
+		'''test if a point is inside any polygon'''
+		for obst in self.obsts:
+			if obst.inside(pnt):
+				return True;
+		return False;
 
 	def render(self, surf):
 		for obst in self.obsts:

### 2014-07-10 utility.py

@@ -1,4 +1,5 @@
 import math;
+import sys, os;
 
 def euclideanDist( config1, config2 ):
     length = len(config1);
@@ -74,7 +75,7 @@ def point2LineDist( point, end1, end2):
     else:
         return math.fabs( ab[0]*ac[1]-ab[1]*ac[0] ) / math.sqrt( ab[0]**2 + ab[1]**2 );
 
-def progressBar(self, percentage):
+def progressBar( percentage):
     percStr = ""
     for i in range( 0, int(percentage) ):
         percStr += '|';

### 2014-07-12 Writing/july11/sampling_2d.tex
iso cost

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{algpseudocode}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\title{Media Axis Sampling}
\date{}
\begin{document}
  \maketitle

  This is some media axis sampling outputs of algorithm mentioned in $\cite{steven}$. As mentioned last Tuesday, by changing the terminal condition a bit. We can sample spheres with any size.\\

  All the figures shown below are 800x800 sized. There are three rectangle obstacles in the middle of the 2d space. The space itself is white. All light gray areas are covered by no border discs. Black points are samples, as well as centers of discs.\\

  Figure \ref{fig:MA} shows the result of sampling on the media axis of the space. The result seems right. And as can be seen, almost the whole space is covered by discs centered at these media axis samples. 4 corners of the space are not well covered, we will talk about it later.\\

  We can also sample points in the space with any clearance. Figure \ref{fig:ISO} shows the result of sampling points 30(pixels) distance away from obstacles or the boundary of the space.\\

   All of the two figures contain 1000 samples( black points ). But they are not uniformly distributed on neither the media axis nor on the iso-cost contours. As can be seen in the pictures, samples near corner is much less than near obstacles. The reason is, the algorithm uniformly get random points in the space, and "push" them, along some direction, to the media axis. Therefore the probability of a narrow passage getting sampled depends on the volume of the passage, as well as the volume of its surrounding obstacles. Jory Denny $\cite{jory}$ mentioned a way to sample on media axis such that samples are uniformly distributed. By uniformly sampling, we can cover the corner of the space better. \\

  \begin{figure}[p]
  \centering
  \includegraphics[scale=0.5]{MediaAxis_Cover.PNG}  
  \caption{Sampling on Media Axis}   
  \label{fig:MA} 
  \end{figure}

  \begin{figure}[p]
  \centering
  \includegraphics[scale=0.5]{MediaAxis_cost_30.PNG}  
  \caption{Sampling on Media Axis}   
  \label{fig:ISO} 
  \end{figure}

  \begin{thebibliography}{1}

  \bibitem{steven} Steven A. Wilmarth, Nancy M. Amato, Peter F. Stiller. "MAPRM: A Probabilistic Roadmap Planner with Sampling on the Medial Axis of the Free Space", In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pp. 1024-1031, Detroit, MI, May 1999. Also, Technical Report, TR98-0022, Department of Computer Science and Engineering, Texas A \& M University, Nov 1998.

  \bibitem{jory} Jory Denny, Evan Greco, Shawna L. Thomas, Nancy M. Amato, "MARRT: Medial Axis Biased Rapidly-Exploring Random Trees",  In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), Hong Kong, China, Jun 2014.

  \end{thebibliography}

\end{document}

### 2014-07-12 MAPRM.py

@@ -3,14 +3,20 @@ from pygame.locals import *
 import sys, os, time
 import math, copy
 import random
+import Queue
 
 from geometry import *
 from obstacles import *
 from utility import *
 
+class Helper:
+	def __init__(self):
+		self.idx = 0.0;
+
 class LineSearch:
 	def __init__( self, start, dir ):
 		self.start = start;
+		self.idx = 0;
 		if dir:
 			self.dir   = dir.normalize();
 		pass;
@@ -46,10 +52,11 @@ class LineSearch:
 	def search(self, obstMgr, world, surf=None):
 		lastNear, lastDist  = self.nearPoint( self.start, obstMgr, world );
 		thisNear = copy.copy(lastNear); thisDist = lastDist;
-		idx      = 0;
+		helper = Helper();
+		pnt = copy.copy(self.start);
 		while( lastNear == thisNear ):
 			#lastDist = thisDist;	lastNear = thisNear;
-			pnt = v2( self.start.x+self.dir.x*idx, self.start.y+self.dir.y*idx )
+			pnt = v2( self.start.x+self.dir.x*helper.idx, self.start.y+self.dir.y*helper.idx )
 			if surf:
 				pygame.draw.line( DISPLAYSURF, (100, 100, 100), (int(pnt.x), int(pnt.y)), (int(pnt.x), int(pnt.y)), 1 );
 				for event in pygame.event.get():
@@ -61,8 +68,38 @@ class LineSearch:
 			#print '-------'
 			#print "{0}\t{1}\t{2}".format(pnt, lastNear, thisNear);
 			
-			idx += 1;
+			helper.idx += 1;
 		return pnt, thisDist;
+
+	def searchISO(self, obstMgr, world, cost, surf=None):
+		lastNear, lastDist  = self.nearPoint( self.start, obstMgr, world );
+		helper = Helper();
+		helper.idx = 0.0;
+		pnt = copy.copy(self.start);
+		acc = 1.0;
+
+		while( math.fabs(cost-lastDist) >= 1 ):
+			if( helper.idx > (cost/acc) ):
+				acc = acc / 2.0;
+				helper.idx = 0.0;
+				if acc <= 0.25:
+					break;
+
+			#lastDist = thisDist;	lastNear = thisNear;
+			pnt = v2( self.start.x+self.dir.x*helper.idx*acc, self.start.y+self.dir.y*helper.idx*acc )
+			if surf:
[…]

### 2014-07-12 MAPRM.py
july 11

@@ -206,7 +206,6 @@ class MAPRMSampler:
 
 		while not que.empty():
 			sample = que.get();
-			print sample;
 			newSamps = getNewSample( sample, cost );
 			if len(samples) > 2:
 				ifwithin = False;
@@ -225,8 +224,11 @@ class MAPRMSampler:
     			for newsamp in newSamps:
     				samples.append(newsamp);
     				que.put(newsamp);
-    				print que.empty();
+    				print que.qsize();
+    			continue;
 
+
+    	print que.qsize();
 		return samples;
 
 

### 2014-07-16 Writing/MedialAxis/medial_axis.tex
medial axis analysis

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{algpseudocode}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\title{Medial Axis Sampling}
\date{}
\begin{document}
  \maketitle

  \section{Demo}

  This is some medial axis sampling outputs of algorithm mentioned in $\cite{steven}$. As mentioned last Tuesday, by changing the terminal condition a bit. We can sample spheres with any size.\\

  All the figures shown below are 800x800 sized. There are three rectangle obstacles in the middle of the 2d space. The space itself is white. All light gray areas are covered by no-border discs. Black points are samples, as well as centers of discs.\\

  Figure \ref{fig:MA} shows the result of sampling on the medial axis of the space. The result seems right. And as can be seen, almost the whole space is covered by discs centered at these medial axis samples. 4 corners of the space are not well covered, we will talk about it later.\\

  We can also sample points in the space with any clearance. Figure \ref{fig:ISO} shows the result of sampling points 30(pixels) distance away from obstacles or the boundary of the space.\\

  Figure \ref{fig:MA_n} is the result of sampling on medial axis but restrict discs to be centered outside of existing ones. Apparently some areas are not covered. \\

  Figure \ref{fig:MAISO_n} is \ref{fig:MA_n} plus \ref{fig:ISO_n}, firstly sample on medial axis, then sample some small discs. Area left by the first step is better covered by the second step.\\

  Figure \ref{fig:MA} and Figure \ref{fig:ISO} contain 1000 samples( black points ). But they are not uniformly distributed on neither the medial axis nor on the iso-cost contours. As can be seen in the pictures, samples near corner is much less than near obstacles. The reason is, the algorithm uniformly get random points in the space, and "push" them, along some direction, to the medial axis. Therefore the probability of a narrow passage getting sampled depends on the volume of the passage, as well as the volume of its surrounding obstacles. Jory Denny $\cite{jory}$ mentioned a way to sample on medial axis such that samples are uniformly distributed. By uniformly sampling, we can cover the corner of the space better. \\

  Sampling continuously on iso-cost contours is impractical, because we will get infinite number of samples. Eventually we need to come up with a method to sample finite number of discs. Figure \ref{fig:ISO_n} shows the result of sampling on the boundary of existing spheres with clearance of 30 for each sample. All discs are centered outside of existing ones except for the first and the last one in a chain of discs. The algorithm always converges.\\

  \section{Reviewing Medial Axis Sampling}

  In \cite{steven}, Steven A. Wilmarth defined media axis as: \\

  "Consider sets $D$ that are the disjoint union of a finite number of closed polygons (including the interior, possibly with holes). For $x\in D$, we define $B_D(x)$ to be the largest closed disc centered at $x$ that is a subset of $D$, i.e., $B_D(x) = \overline{B}( x, \rho_{D}(x) )$, where $\overline{B}( x, \rho_{D}(x) )$ denotes the closed disc of radius $r \geq 0$, centered at $x$, and $\rho_{D}(x) = dist(x, \mathbb{R}^2 \setminus D)$ is the distance to the boundary for points inside $S$, and 0 for points outside $D$.

  The medial axis $MA(D)$ of $S$ is defined to be the set of all points $x$ of $D$ whose $B_D(x)$ are maximal.

  $MA(D) = \{ x \in D | \not \exists y \in D$ with $B_D(x) \subset B_D(y) \}$"\\

  He proposed an algorithm to sample on medial axis, which we used and modified to serve our purpose. The algorithm is as below:\\

  \includegraphics[scale=0.65]{MAPRM.png}

  ($\partial F$ is the boundary of the free space. $\partial F = \{ \mathbb{R}^2 \setminus D$ \})\\

  The key logic behind the algorithm is: given a point $p$ in free space, the possibility of it being on the medial axis is 0. Assume the nearest point on $\partial F$ to $p$ is $q$, and line $qp$ intersects with medial axis on point $m$ ($m \neq p$).  According to the definition, $m$ has more than one nearest points on $\partial F$, $\{ q \} \subset B_D(p) \subset B_D(m) \Longrightarrow |pq| \leq |mq|$. let $t$ be a point in line segment $pm$, $\{ q \} \subset B_D(t)$ and $|pq| \leq |tq| \leq |mq|$. $|tq|$ is maximized if and only if $t = m$\\

  \includegraphics[scale=1]{LineSearch.pdf}

  \section{Some Proofs}

  \begin{theorem}
  Continuously sample all points $x \in MA(D)$ totally covers space $D$.
  \end{theorem}

  Proof:

  The theorem is a direct result of the definition of medial axis. \\

  "$MA(D) = \{ x \in D | \not \exists y \in D$ with $B_D(x) \subset B_D(y) \}$"\\

  Therefore, $\forall y \in D, \exists x \in D, s.t. B_D(y) \subset B_D(x)$. \\

  $\{ y \} \subset B_D{y}$, so $\{ y \} \subset B_D(y) \subset B_D(x)$.\\

  \begin{theorem}
  Given an inaccurate metric $M(\cdot)$ that measures the distance from point $p$ to $\partial F$ and $M(p) \leq |pq|$, $M(m) \geq M(t), \forall t \in qm$. ($M(p)=M(pq)$ iff $q$ is the nearest point on $\partial F$ to $p$ ).
  \end{theorem}

  Proof:

  Let $p t_1, t_2, t_3 ... m$ be a series of points in line segment $pm$, $q$ is the nearest point on $\partial F$ to all of them. $|t_{i}q| = |t_{i}t_{i-1}| + |t_{i-1}q| \Longrightarrow M(t_{i}q) \geq M(t_{i}t_{i-1}) + M(t_{i-1}q)$. If $t_{i} \neq t_{i-1}$, $M(t_{i}t_{i-1}) > 0 \Longrightarrow M(t_{i}q) > M(t_{i-1}q)$.\\

  So, $M(mq) > M(tq), \forall t \in pm$. \\

  This theorem implies that knowing the direction of point $p$ to its nearest point $q$ on $\partial F$ or to medial axis, we can always use the algorithm proposed above to get a point on medial axis, even if we are given an inaccurate metric.

  \begin{theorem}
  In the direction of point $p$ to $m$, $\rho_{D}(x)$ increases fastest.
  \end{theorem}
  Proof:

  Given point $p$, assume its nearest point on $\partial F$ is $q$ which we don't know what $q$ is exactly. Draw a circle centered at $p$ with radius $r$. Assume point $k$ and $t$ are both on the edge of the circle, and the nearest points on $\partial F$ of $k$ and $t$ are $q$ and $q'$ which is still assumed an unknown point to us. We have to intermedial conclusions:\\

  1. $|tq'| \leq |tq|$. Because otherwise $q$ is the nearest point to $t$.

  2. $|kq| = |kp| + |pq|$. \\

  Since $|kp| = |tp|$, $|kp| + |pq| = |tp| + |pq| > |tq|$ (triangle inequality). Therefore $|kq| > |tq| \geq |tq'| \Longrightarrow \rho_{D}(k) > \rho_{D}(t)$. \\

  $k$ and $t$ can be viewed as two points that are the same distance from $p$ but in different directions. $\vec{qp}$ and $\vec{pm}$ has the same direction and in this direction $\rho_{D}(x)$ increases faster than others.

  \includegraphics[scale=1]{direction.pdf}\\

  The theorem implies that when we don't know a point's nearest point on $\partial F$, if we can find the direction to medial axis using the property of $\rho_{D}(x)$ increases fastest in the direction, we can still sample on the medial axis.\\

  This is particularly important for our diff drive planning, be cause we only know the time clearance of a configuration, but have know idea its nearest point on obstacles in C-Space.

  \begin{figure}[p]
  \centering
  \includegraphics[scale=0.5]{MediaAxis_Cover.PNG}  
  \caption{Sampling on Medial Axis}   
  \label{fig:MA} 
  \end{figure}

  \begin{figure}[p]
  \centering
  \includegraphics[scale=0.5]{MediaAxis_cost_30.PNG}  
  \caption{Sampling on Axis with clearance of 30}   
  \label{fig:ISO} 
  \end{figure}

  \begin{figure}[p]
  \centering
  \includegraphics[scale=0.5]{MedialAxis_cost_30_bnd.PNG}  
  \caption{Sampling on boundaries of existing discs with clearance of 30}   
  \label{fig:ISO_n} 
  \end{figure}

  \begin{figure}[p]
  \centering
  \includegraphics[scale=0.5]{MedialAxis_bnd.PNG}  
  \caption{Sampling on boundaries of existing discs with clearance of 30}   
  \label{fig:MA_n} 
  \end{figure}

  \begin{figure}[p]
  \centering
  \includegraphics[scale=0.5]{MedialAxis_bnd_iso.PNG}  
  \caption{Sampling on boundaries of existing discs with clearance of 30}   
  \label{fig:MAISO_n} 
  \end{figure}

  \begin{thebibliography}{1}

  \bibitem{steven} Steven A. Wilmarth, Nancy M. Amato, Peter F. Stiller. "MAPRM: A Probabilistic Roadmap Planner with Sampling on the Medial Axis of the Free Space", In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pp. 1024-1031, Detroit, MI, May 1999. Also, Technical Report, TR98-0022, Department of Computer Science and Engineering, Texas A \& M University, Nov 1998.

  \bibitem{jory} Jory Denny, Evan Greco, Shawna L. Thomas, Nancy M. Amato, "MARRT: Medial Axis Biased Rapidly-Exploring Random Trees",  In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), Hong Kong, China, Jun 2014.

  \end{thebibliography}

\end{document}

### 2014-07-16 MAPRM.py

@@ -41,6 +41,12 @@ class LineSearch:
 		return near, dist;
 
 	def nearPoint( self, pnt, obstMgr, world ):
+		if obstMgr.inside(pnt):
+			return None, 0.0;
+
+		if pnt.x < 0 or pnt.y < 0 or pnt.x > world.WIDTH or pnt.y > world.HEIGHT:
+			return None, 0.0; 
+
 		near, dist = obstMgr.closest_point( pnt );
 		near2Wall, dist2Wall = self.point2WallDist( pnt, world.WIDTH, world.HEIGHT );
 		if dist < dist2Wall:
@@ -55,19 +61,8 @@ class LineSearch:
 		helper = Helper();
 		pnt = copy.copy(self.start);
 		while( lastNear == thisNear ):
-			#lastDist = thisDist;	lastNear = thisNear;
-			pnt = v2( self.start.x+self.dir.x*helper.idx, self.start.y+self.dir.y*helper.idx )
-			if surf:
-				pygame.draw.line( DISPLAYSURF, (100, 100, 100), (int(pnt.x), int(pnt.y)), (int(pnt.x), int(pnt.y)), 1 );
-				for event in pygame.event.get():
-					pass;
-    			pygame.display.update();
-    			#time.sleep( .1 );
-
+			pnt = v2( self.start.x+self.dir.x*helper.idx, self.start.y+self.dir.y*helper.idx );
 			thisNear, thisDist = self.nearPoint( pnt, obstMgr, world );
-			#print '-------'
-			#print "{0}\t{1}\t{2}".format(pnt, lastNear, thisNear);
-			
 			helper.idx += 1;
 		return pnt, thisDist;
 
@@ -111,7 +106,12 @@ class MAPRMSampler:
 		searcher = LineSearch(None, None);
 		return searcher.nearPoint( pnt, self.obstMgr, self.world );
 
-	def sample(self, n):
+	def dist2Obst(self, pnt):
+		near = self.obstMgr.closest_point(pnt);
+		return math.sqrt( (near.x-pnt.x)**2 + (near.y-pnt.y)**2 );
+
+	def sampleMA(self, n, ifShowProgressbar = True):
+		'''Continuously sample on medial axis'''
 		samples = [];
 		while( len(samples) < n ):
 			rand_x = random.randint( 0, self.world.WIDTH );
@@ -133,10 +133,87 @@ class MAPRMSampler:
 			searcher       = LineSearch( start, dirt );
[…]

### 2014-07-16 obstacles.py

@@ -5,6 +5,7 @@ class Polygon:
 	"""Polygon class. An obstacle is defined as a polygon."""
 	def __init__( self, ptlist ):
 		"""@param ptlist: points list or tuple list, anti-clockwise ordered."""
+		self.vertices = ptlist;
 		self.lines = [];
 		for i in range(1, len(ptlist)):
 			line  = line_segment(ptlist[i-1], ptlist[i]);

### 2014-07-21 Writing/MedialAxis/CoverLeftArea.tex
MA new

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{algpseudocode}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\title{Reducing Small Discs}
\date{}
\begin{document}
  \maketitle

  \section{Demo}
  Graph below shows covering left areas by sampling iso-cost discs.

  \includegraphics[scale=0.5]{MedialAxis_bnd_iso_better.PNG}

  \section{Algorithm}

	\subsection{Measuring newly discovered area}
    Say we have a disc $ball(O_1, R)$ already, and a new disc $ball(O_2, r)$. The newly discovered area, read shaded in the graph, can be expressed as a function of $x$, denoted as $f(x)$. Obviously, $f(x)$ is monotonically increasing when $x \in [0, 2\cdot r]$. We can measure if a new disc discovers enough new area by measuring if $x$ is larger than a threashold. ( $x = d+r-R \geq threashold$ )

    \includegraphics[scale=1]{measuring_new_cover.pdf}

    Although this $f(x)$ function determines the relation between one new disc and another existing disc instead of a set of existing discs. The result seems pretty good. (No idea why, yet.)\\

	Measuring if a disc is useful:\\

	\begin{algorithmic}
    \State $maSamples \gets$ medial axis samples.	
	\State $isoSamp \gets$ one iso-cost sample. 
	\For{$samp \in maSamples$}
		\State $centerdist \gets |samp.center - isoSamp|$  \Comment{Distance between centers}
		\If{ $centerdist + isoSamp.radius - samp.radius \leq threashold$ }
			\indent \indent \Return False 
		\EndIf
	\EndFor

	\noindent \Return True;
	\end{algorithmic}

	\subsection{Generating small discs to cover left areas}

	\begin{enumerate}
	\item Generate Medial Axis Samples.
	\item Generate iso-cost small discs. Every disc is some distance away from existing ones.
	\item Test every iso-cost disc to see if it is useful. Keep only useful ones.
	\end{enumerate}

	\section{Questions}

	\begin{enumerate}
	\item Why the method to measure new discovered area works.
	\item How densely should we sample iso-cost discs?
	\item Which size disc should we sample?
	\end{enumerate}

\end{document}

### 2014-07-21 Writing/MedialAxis_v2/sampling_2d.tex
MA new

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{algpseudocode}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\title{Sampling}
\date{}
\begin{document}
  \maketitle

  \section{Sampling Uniformly on Medial Axis}
  \cite{jory} proposed an algorithm for sampling uniformly on medial axis. The key idea is: Randomly put a lot of sticks(line segments) with random orientations in the free-space, whatever dimensions it has. Since these sticks are uniformly distributed in the space, any surface will uniformly intersect with these sticks. Medial axis will also intersect with these sticks uniformly.\\

  Algorithm is as below:\\

  \begin{algorithmic}
    \State $maSamples \gets$ Empty Set.
    \State $pntset \gets$ randomly generated points in free space.
    \State $l \gets $ stick length.	 
	\For{$point \in pntset$}
		\State $dir \gets$ random direction  
		\State $stick \gets$ ( point, l, dir ) \Comment{start point + length + direction = a stick}
		\If{ $stick$ intersects with the medial axis }

			$sample \gets$ stick.search()

			$radius \gets$ clearance( sample ) \Comment{get the clearance at this point}

			$maSamples.append( ball(sample, radius) )$
		\EndIf
	\EndFor

	\noindent \Return $maSamples$;
  \end{algorithmic}

  \section{Sampling Balls Outside MA Samples }

  The idea of my algorithm is when we have a lot of random points in free space and some big discs on the medial axis, we don't want to waste points inside existing discs, instead, we "push" them to the boundary of these discs, and get new samples.

  Testing if a point is inside some discs seems to be a $O(n^2)$ time problem. But it can actually be done by choosing k-nearest neighbors of the centers of discs. Suppose in a 2D free space, we have some uniformly distributed points. They are uniformly distributed so, in a unit area, the expectation of the number of points is fixed. Assume a disc has radius $r$, its area is monotonic to $r^2$. Therefore the number of points inside the disc is monotonic to $r^2$, meaning that if we choose k-nearest points to the center of the disc, (k is a function of $r^2$), they are very likely to be inside the disc. There is no harm if some points are not actually inside the disc or some inside points are left, we only want to use these points to generate some points on the boundary of the disc by extending them in the direction from center to each of them. In fact, we want to choose a $k$ that is larger than the actual number of points inside.

  Since all discs touch obstacles, by choosing a larger $k$, we are virtually extending the radius of our discs, which results in a smaller density in arcs that are very close to obstacles than those far from obstacles.

  Now we have dense points on the boundary of existing discs. Using these points to sample new small discs to cover undiscovered area has some benefits compare with points not covered by any discs:

  1. They are more likely to get discs with larger radius.

  2. They are less likely to left some holes between discs.

  3. Experiments shows, initially, we need much less random points in the free space.

  \begin{thebibliography}{1}

  \bibitem{steven} Steven A. Wilmarth, Nancy M. Amato, Peter F. Stiller. "MAPRM: A Probabilistic Roadmap Planner with Sampling on the Medial Axis of the Free Space", In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pp. 1024-1031, Detroit, MI, May 1999. Also, Technical Report, TR98-0022, Department of Computer Science and Engineering, Texas A \& M University, Nov 1998.

  \bibitem{jory} Uniform Medial Axis Sampling.

  \end{thebibliography}

\end{document}

### 2014-07-21 MAPRM.py

@@ -262,7 +262,19 @@ class MAPRMSampler:
 			if near is not None and math.fabs( cost-currDist ) <= 0.4:
 				return point;
 
-	def sampleISOn( self, cost, surf=None ):
+	def checkWithinMaSamples(self, point, r, maSamples):
+		'''Check if the current iso sample is inside any medial axis samples.
+		@param point: 		current iso sample position.
+		@param r: 			current iso sample radius.
+		@param maSamples: 	medial axis samples.
+		'''
+		for masam in maSamples:
+			d = math.sqrt( (masam[0].x-point.x)**2 + (masam[0].y-point.y)**2 );
+			if d + r - masam[1] < r * (1.0/3.0):
+				return True;
+		return False;
+
+	def sampleISOn( self, cost, maSamples, surf=None ):
 		vertices = [];
 		inits = [];
 		inits.append( v2( cost, cost ) )
@@ -277,16 +289,16 @@ class MAPRMSampler:
 		samples = [];
  
 		for init in inits:
-			self.__sampleISOn__( init, cost, samples, surf );
+			self.__sampleISOn__( init, cost, samples, maSamples, surf );
 
 		return samples;
 
 
-	def __sampleISOn__( self, initPnt, cost, samples, surf ):
+	def __sampleISOn__( self, initPnt, cost, samples, maSamples, surf ):
 		'''Sample on the iso-cost contour such that no sample is centered in existing ones'''
 		def inside(point, center, radius):
 			distSqr = (point.x-center.x)**2 + (point.y-center.y)**2;
-			if distSqr < radius**2:
+			if distSqr < radius**2/4.0:
 				return True;
 			else:
 				return False;
@@ -295,7 +307,7 @@ class MAPRMSampler:
 			'''Get points on the boundary of the disc that has the same cost as the center'''
 			retSamps = [];
 			for idx in range(0, 360):
-				pnt = v2( point.x+float(dist)*math.cos(idx), point.y+float(dist)*math.sin(idx) );
+				pnt = v2( point.x+float(dist/2.0)*math.cos(idx), point.y+float(dist/2.0)*math.sin(idx) );
 				near, currDist = self.nearPoint(pnt);
 				if math.fabs( dist-currDist ) <= 0.4:
 					retSamps.append( pnt );
[…]

### 2014-07-21 UMAPRM.py

@@ -1,0 +1,542 @@
+import pygame
+from pygame.locals import *
+import sys, os, time
+import math, copy
+import random
+import Queue
+
+from geometry  import *
+from obstacles import *
+from utility   import *
+from priority_queue import *
+
+class Disc:
+	def __init__(self, center, radius):
+		self.center  = center;
+		self.radius  = radius;
+		self.samples = [];
+		self.bndsamples = [];
+		self.__closed__ = False;
+
+	def inside(self, point):
+		dist = (point - self.center).r();
+		if dist < self.radius:
+			return True;
+		else:
+			return False;
+
+	def isClosed(self):
+		return self.__closed__;
+
+	def dist(self, point):
+		'''distance from a point to the disc, negative if inside.'''
+		centerdist = (point - self.center).r();
+		return centerdist - self.radius;
+
+	def add(self, point):
+		'''if the point is inside it, add it to the sample set.'''
+		if not self.inside(point):
+			return False;
+
+		if self.__closed__:
+			return True;
+
+		self.samples.append( point );
+		return True;
+
+	def getbndpoints(self):
+		'''Push all points to the boundary of the disc'''
+		if self.__closed__:
+			return [];
+		self.bndsamples = [];
+		for point in self.samples:
+			dir = (point - self.center);
+			if dir.r() == 0:
+				dir = v2(1,3);
+			dir = dir.normalize();
+			bndPoint = self.center + dir * (self.radius+0.5);
+			self.bndsamples.append( bndPoint );
+
+		self.samples = [];
+		self.__closed__ = True;
+		return self.bndsamples;
+
+	def render(self, surf, mode=1, color = (0, 200, 0)):
+		'''render the disc.
+		mode = 1: render the disc only.
+		mode = 2: render the disc with inside points.
+		mode = 3: render the disc with boundaryy points. '''
+		if surf is None:
+			return;
+
+		pygame.draw.circle( surf, color, (int(self.center.x), int(self.center.y)), int(self.radius) )
+		
+		if mode == 2:
+			for point in self.samples:
+				pygame.draw.circle( surf, (50,50,50), (int(point.x), int(point.y)), 2 );
+		elif mode == 3:
+			for point in self.bndsamples:
[…]

### 2014-07-21 obstacles.py

@@ -79,8 +79,6 @@ class ObstManager:
 	def dist2obsts(self, robot):
 		'''return the min dist from the robot to any obstacles.'''
 		dists = [];
-		if self.intersects( robot ):
-			return 0;
 		for obst in self.obsts:
 			dists.append( obst.dist2robot(robot) );
 		return min(dists);
@@ -99,7 +97,11 @@ class ObstManager:
 			if dist < minDist:
 				nearest = near;
 				minDist = dist;
-		return nearest, minDist;
+
+		inside = 1;
+		if self.inside(point):
+			inside = -1;
+		return nearest, minDist*inside;
 
 	def inside( self, pnt ):
 		'''test if a point is inside any polygon'''

### 2014-07-21 test.py

@@ -1,10 +1,50 @@
+import pygame 
+import math
+import random
 from geometry import *
+from priority_queue import *
 
-A = v2(0, 0);      B = v2(100, 0);
-C = v2(-10, 20);    D = v2(0, 150);
-AB = line_segment(A, B);
-CD = line_segment(C, D);
 
-print AB.intersects_segment(CD);
+def k_nearest(  pointset, point, radius ):
+	'''Get k-nearest points in the point set to a givin point. k is determined by radius'''
+    	pq = PriorityQueue();
+  	for pnt in pointset:
+   		dist = (pnt-point).r();
+   		pq.push( pnt, dist );
 
-print AB.dist_line_seg(CD);
+	k = radius**2 / 50;
+   	if k > len(pointset):
+   		return pointset;
+      	k_near = [];
+       	for i in range(0,int(math.floor(k))):
+       		k_near.append( pq.pop() );
+
+       	return k_near;
+
+
+DISPLAYSURF = pygame.display.set_mode((800, 800));
+DISPLAYSURF.fill((255,255,255));
+
+pygame.draw.line( DISPLAYSURF, (0,0,0), (0, 700), (800, 700), 4 );
+pygame.draw.circle( DISPLAYSURF,(0,255,0), ( 400, 500 ), 200, 2 );
+
+pntset = [];
+for i in range(0,300):
+	rand_x = random.randint( 0, 800 );
+	rand_y = random.randint( 0, 700);
+	pnt = v2(rand_x, rand_y);
+	pygame.draw.line( DISPLAYSURF, (0,0,0), (rand_x, rand_y), (rand_x, rand_y), 2 );
+	pntset.append( pnt );
+
+bndsamples = [];
+knear = k_nearest(pntset, v2(400, 500), 200);
+for point in knear:
+	dir = (point - v2(400,500));
+	if dir.r() == 0:
+		dir = v2(1,3);
+	dir = dir.normalize();
+	bndPoint = v2(400, 500) + dir * (200);
+	pygame.draw.circle(DISPLAYSURF, (250, 0, 0), (int(bndPoint.x),int(bndPoint.y)), 3);
+	bndsamples.append( bndPoint );
+
+pygame.image.save( DISPLAYSURF, "boundaryPointDensity.PNG" );

### 2014-07-24 Writing/MedialAxis_v2/MASampling.tex
collect some data about ma sampling

--- 2014-07-21 Writing/MedialAxis_v2/sampling_2d.tex
@@
 
-  \begin{algorithmic}
+  \begin{algorithmic}[1]
+  \Function{UniformSampleMA}{pntset}
+    \State $pntset \gets$ randomly generated points in free space.
     \State $maSamples \gets$ Empty Set.
-    \State $pntset \gets$ randomly generated points in free space.
     \State $l \gets $ stick length.	 
@@
 		\State $dir \gets$ random direction  
-		\State $stick \gets$ ( point, l, dir ) \Comment{start point + length + direction = a stick}
+		\State $stick \gets$ ( point, l, dir ) \Comment{start point+length+direction=a stick}
 		\If{ $stick$ intersects with the medial axis }
 
-			$sample \gets$ stick.search()
+			\indent\indent $sample \gets$ stick.search()
 
-			$radius \gets$ clearance( sample ) \Comment{get the clearance at this point}
+			\indent\indent $radius \gets$ clearance( sample ) \Comment{get the clearance at this point}
 
-			$maSamples.append( ball(sample, radius) )$
+			\indent\indent $maSamples.append( ball(sample, radius) )$
 		\EndIf
@@
 
-	\noindent \Return $maSamples$;
+	\Return $maSamples$;
+  \EndFunction
   \end{algorithmic}
@@
 
+  \subsection{Algorithm}
+
+  \begin{algorithmic}[1]
+  \Function{SampleDiscs}{ n }
+    \State $pntset \gets$ n points uniformly distributed in free space
+  	\State $maSamples \gets$ UniformSampleMA($pntset$) \Comment{Get discs on MA}
+  	\State $bndSamples \gets EmptySet$ \Comment{Set of discs not on MA}
+  	\State $newDisc \gets$ True	\Comment{If we can get new discs}
+  	\State $lastRoundDiscs \gets maSamples$
+  	\While{$newDisc$}
+  		\State $newDisc \gets False$
+		\State $bndpnts \gets EmptySet$ \Comment{A set of disc boundary points}  		
+  		\For {$disc \in lastRoundDiscs$}
+
+  			\indent\indent $disc.KNearest(pntset)$; \Comment{Use k-nearest to get points inside it.}
+
+  			\indent\indent $bndpnts.append( disc.getBoundaryPoints() )$
+  		\EndFor
+  		\State $lastRoundDiscs \gets EmptySet$
+
+  		\For{$point \in bndpnts$}
+  			\If{$point$ not inside any existing discs} \Comment{$O(n^2)$ time}
+  				\indent\indent\indent $disc \gets getNewDisc(point)$ \Comment{get a new disc}
+  				\If{$disc.radius \geq minRadius$}
+
+  					\indent\indent\indent\indent $newDisc \gets True$
+
+  					\indent\indent\indent\indent $lastRoundDiscs.append( disc )$
+
+  					\indent\indent\indent\indent $bndSamples.append(disc);$
+  				\EndIf
+  			\EndIf
+
+  		\EndFor
+  	\EndWhile
+
+  	\Return $maSamples$, $bndSamples$
+  \EndFunction
+  \end{algorithmic}
+
+  \section{Build Topology PRM using MA Samples}
+  In last section, our algorithm returns two sets of discs: 1.
+discs centered on Medial Axis, 2.
+discs centered on somewhere else.
+What is useful for representing the topology of the space using the centers of Medial Axis samples to construct a graph.
+
+  Problem is, can we simplify the graph even more? Because the simpler our graph is, the faster we can find a path, and the less memory we need to represent a very large environment.
+
+  \subsection{Some thoughts}
+  "Discs" mention in this subsection are discs centered on the Medial Axis.
+  \begin{enumerate}
+	\item Some discs are more important than others.
+For example, in a 2d word, a disc connects with only two other discs is less important than a disc that connects with 3 or 4 or more discs, because by connecting more discs, a disc can provide more routes.
+
+    \item I guess those "more important" centers are very likely to form clusters. By clustering them, i think we can do clustering and get the center of each cluster.
+
+	\item Choose these "more important" centers as initial vertices of our simpler graph.
+For every pair of vertices, find the shortest chain of discs that connects them, using A* search.
+If the chain doesn't contain any discs centered at other important vertices, keep it.
+
+	\item Now we need to reduce some disc centers in each chain.
+It could be done by binary search for points that connect the start and end vertices of the chain.
+In the best case, all points except for the start and end vertices are reduced.
+In the worst case, all points are kept.
+
+  \end{enumerate}
+
   \begin{thebibliography}{1}

### 2014-07-24 UMAPRM.py

@@ -4,11 +4,13 @@ import sys, os, time
 import math, copy
 import random
 import Queue
+from datetime import datetime
 
 from geometry  import *
 from obstacles import *
 from utility   import *
 from priority_queue import *
+from pixel_reader   import *
 
 class Disc:
 	def __init__(self, center, radius):
@@ -175,6 +177,7 @@ class UMAPRMSampler:
 	def __init__(self, world):
 		self.world = world;
 		self.obstMgr = self.world.obstMgr;
+		self.MASamples = [];
 
 	def nearPoint(self, pnt):
 		searcher = LineSearch(None, None, 0, self.obstMgr, self.world);
@@ -187,14 +190,15 @@ class UMAPRMSampler:
 		near, dist = self.nearPoint( pnt );
 		return dist;
 
-	def k_nearest( self, pointset, point, radius ):
+	def k_nearest( self, totalpnts, pointset, point, radius ):
 		'''Get k-nearest points in the point set to a givin point. k is determined by radius'''
+	        rho = float(totalpnts) / (self.world.WIDTH*self.world.HEIGHT);
 	        pq = PriorityQueue();
         	for pnt in pointset:
         		dist = (pnt-point).r();
         		pq.push( pnt, dist );
 
-      		k = radius**2 / 50;
+      		k = math.pi*((radius*1.3 )**2) * rho;
       		if k > len(pointset):
       			return pointset;
         	k_near = [];
@@ -206,7 +210,7 @@ class UMAPRMSampler:
 	def sampleMAr(self, n, surf = None):
 		'''randomly generate points in c-space and sample on medial axis'''
 		pntset = [];
-		while len(pntset) < n:
+		while i in range(0,n):
 			#progressBar( float(len(pntset)) / n * 100);
 			rand_x = random.randint( 0, self.world.WIDTH );
 			rand_y = random.randint( 0, self.world.HEIGHT);
@@ -375,7 +379,7 @@ class UMAPRMSampler:
 	def sampleMAbk(self, n, surf = None):
 		'''randomly sample disc on MA, and sample on the boundary of existing discs'''
 		pntset = [];
-		while len(pntset) < n:
+		for i in range(0, n):
 			#progressBar( float(len(pntset)) / n * 100);
 			rand_x = random.randint( 0, self.world.WIDTH );
 			rand_y = random.randint( 0, self.world.HEIGHT);
[…]

### 2014-07-24 geometry.py

@@ -12,6 +12,9 @@ A small library of 2D geometric primitives.
  - circle:       a circle in the plane.
  - arc:          a directed arc of a circle.
  - path:         a list of line_segment and arc objects.
+
+--------------------------
+Modified by Yinan Zhang.
 """
 
 import pygame
@@ -24,7 +27,7 @@ from math import sqrt, pi, degrees, radians, cos, sin, acos, asin, atan2
 
 __all__ = [
   'pi', 'degrees', # re-exported from math
-  'angle', 'v2', 'line_segment', 'circle', 'arc', 'path',
+  'angle', 'v2', 'v3', 'line_segment', 'circle', 'arc', 'path',
 ]
  
 
@@ -72,6 +75,12 @@ class v2( object ):
     return self.x != other.x or  self.y != other.y
   def __hash__( self ):
     return hash(( self.x, self.y ))
+
+  def __len__(self):
+    return 2;
+
+  def __getitem__(self, key):
+    return (self.x, self.y)[key];
 
 
   def rsq( self ):
@@ -156,6 +165,135 @@ class v2( object ):
   def __complex__( self ):
     return self.x + 1j*self.y
 
+
+#========================================================================================
+# 3D vector
+#========================================================================================
+class v3( object ):
+  'Represents a 3D point with coordinates (x,y).'
+  __slots__ = ['x','y','z']
+
+  def __init__( self, x, y, z ):
+    self.x = x
+    self.y = y
+    self.z = z
+
+  '''
+  @classmethod
+  def polar( cls, r, radians ):
+    'Construct a vector from a length and angle.'
+    return cls( r*cos(radians), r*sin(radians) )
+
+  @classmethod
+  def from_angle( cls, radians ):
+    'Construct a unit vector from an angle.'
+    return cls( cos(radians), sin(radians) )
+  '''
+
+  def __str__( self ):
+    return '(%.3f,%.3f,%.3f)' % ( self.x, self.y, self.z )
+  def __repr__( self ):
+    return 'v3(%r,%r,%r)' % ( self.x, self.y, self.z )
+
+  def __eq__( self, other ):
+    return self.x == other.x and self.y == other.y and self.z == other.z
+  def __ne__( self, other ):
+    return self.x != other.x or  self.y != other.y or self.z != other.z
+  def __hash__( self ):
+    return hash(( self.x, self.y, self.z ))
+
+  def __len__(self):
+    return 3;
+  def __getitem__(self, key):
+    return (self.x, self.y, self.z)[key];
+
+
[…]

### 2014-07-24 obstacles.py

@@ -1,5 +1,6 @@
 from geometry import *
 from robot import *
+import pygame
 
 class Polygon:
 	"""Polygon class. An obstacle is defined as a polygon."""
@@ -18,8 +19,13 @@ class Polygon:
 
 	def render(self, surface, color):
 		"""render the polygon to surface."""
-		for line in self.lines:
-			line.render(surface, color, 1);
+		#for line in self.lines:
+		#	line.render(surface, color, 1);
+		#pass;
+		pointlist = [];
+		for vertex in self.vertices:
+			pointlist.append( (int(vertex.x), int(vertex.y)) );
+		pygame.draw.polygon(surface, color, pointlist);
 		pass;
 
 	def intersects(self, robot):
@@ -89,7 +95,8 @@ class ObstManager:
 		return dist / 20.0;
 
 	def closest_point(self, point):
-		'''get the nearest point in obstacles to a point'''
+		'''get the nearest point in obstacles to a point. 
+		!!!This works only in 2d c-space!!!'''
 		minDist = 10000000000;
 		nearest = None;
 		for obst in self.obsts:
@@ -104,7 +111,8 @@ class ObstManager:
 		return nearest, minDist*inside;
 
 	def inside( self, pnt ):
-		'''test if a point is inside any polygon'''
+		'''test if a point is inside any polygon.
+		!!!This works only in 2d c-space!!!'''
 		for obst in self.obsts:
 			if obst.inside(pnt):
 				return True;

### 2014-07-24 pixel_reader.py

@@ -1,0 +1,26 @@
+import pygame 
+import math
+
+
+
+class PixelReader:
+	'''A class to read and analysis pixel info'''
+	def __init__( self, surface ):
+		self.surface = surface.convert();
+		self.pxarray = pygame.PixelArray(surface);
+		self.width   = self.surface.get_width();
+		self.height  = self.surface.get_height();
+
+	def count(self, color):
+		'''Count the number of pixels with the give color'''
+		counter = 0;
+		for x in range( 0, self.width ):
+			for y in range( 0, self.height ):
+				#print self.pxarray[x,y];
+				#print self.surface.map_rgb(color);
+				if self.pxarray[x,y] == self.surface.map_rgb(color):
+					counter += 1;
+					pass;
+				pass;
+			pass;
+		return float(counter);

### 2014-07-24 sampling.py

@@ -13,6 +13,7 @@ class CoordMapping:
 		self.height = height;
 
 	def map(self, config):
+		'''Map a config from origin space to a scaled space'''
 		x_     = ((float(config.x) / float(self.width)) * 100.0) / (math.pi/2+1.0);
 		y_     = ((float(config.y) / float(self.height))* 100.0) / (math.pi/2+1.0);
 		theta_ = (float(config.orient)/ (2 * math.pi)) * 100.0;
@@ -29,6 +30,9 @@ class CoordMapping:
 		y 	  = float( config.y ) * (math.pi/2+1.0) * float(self.width) / 100.0;
 		theta = float( config.orient) * (2 * math.pi) / 100.0;
 		return Config( v2(x,y), theta ); 
+
+	def scaledSpaceSize(self):
+		return (100, 100, 100);
 
 
 class Sphere:

### 2014-07-24 samplingMA.py

@@ -1,0 +1,265 @@
+import sys, os
+import random
+from robot import *
+from obstacles import *
+from geometry import *
+from sampling import CoordMapping
+from space_partition import *
+
+class LineSearch:
+	def __init__( self, start, dir, length, obstMgr, robot, mapper ):
+		'''Search a line in c-space
+		@param start  : start configuration point   v3().
+		@param dir    : direction of the point      v3(). 
+		@param length : length of the line.
+		@param obstMgr: obstacles manager to detect collision.
+		@param robot  : the robot
+		@param mapper : configuration mapper. '''
+		self.dir   	 = dir;
+		self.len   	 = length;
+		self.obstMgr = obstMgr;
+		self.robot 	 = robot;
+		self.mapper  = mapper;
+		if dir:
+			self.dir = dir.normalize();
+		if dir is None:
+			return;
+
+		end = start + dir*length;
+		if self.dist2Obst(start) < self.dist2Obst(end):
+			self.start = start;
+			self.end   = end;
+		else:
+			self.start = end;
+			self.end   = start;
+		pass;
+
+	def dist2Obst(self, pnt):
+		'''Distance to obstacles in c-space.
+		@param pnt: config point in c-space.  mapped. v3()'''
+		config_ = Config( v2(pnt.x, pnt.y), pnt.z );
+		config  = self.mapper.unmap(config_);
+		self.robot.setConfig(config_);
+		timeclearance = self.obstMgr.time2obsts( self.robot, self.mapper );
+		return timeclearance;
+
+	def search(self):
+		'''search for the point in the medial axis'''
+		t = 1;
+		last_increse = False;
+		last_dist = self.dist2Obst(self.start);
+		while True:
+			temp = self.start + self.dir*t;
+			this_dist = self.dist2Obst(temp);
+			this_increase = ((this_dist-last_dist)>0);
+			if last_increse and not this_increase:
+				if not self.obstMgr.intersects(self.robot):
+					return temp, this_dist;
+				else:
+					return None, None;
+			else:
+				t += 1;
+				last_increse = this_increase;
+				last_dist = this_dist;
+
+			if t-1 >= self.len:
+				break;
+
+		return None, None;
+
+class Sphere:
+	'''A sphere in c-space is defined as (center, radius)'''
+	def __init__( self, center, radius ):
+		self.center = center;
+		self.radius = radius;
+		self.samples = [];
[…]

### 2014-07-24 space_partition.py

@@ -116,6 +116,12 @@ class SpacePartition:
         idx = self.indxHash( point );
         return self.mGrids[idx];
 
+    def getCurrentGridSpheres(self, point):
+        '''Given a point in n-D world, find the grid that contains it. 
+        And return all the spheres in the grid'''
+        grid = self.getContainingGrid(point);
+        return grid.container;
+
     def checkValid( self, point ):
         '''Check if a point is inside any spheres'''
         grid = self.getContainingGrid( point );

### 2014-07-24 world.py

@@ -5,7 +5,8 @@ import math
 
 from obstacles import *
 from robot import *
-from sampling import *
+from samplingMA import *
+from geometry import *
 
 
 class World:
@@ -90,8 +91,9 @@ pygame.quit();
 #####                   Sample
 ##################################################
 
-sampler = Sampler( gameWorld );
 
-##sampler.sample(100);
-sampler.sampleSlice( math.pi/4 );
+sampler = SamplerV2( gameWorld );
+
+sampler.sample(1000);
+#sampler.sampleSlice( math.pi/4 );
 sampler.save_data('spheres_complete.txt');

### 2014-07-24 samplingMA.py
diff drive sampling

@@ -176,7 +176,7 @@ class SamplerV2:
 		for sphere in self.samples:
 			formattedData += str( sphere.center[0] ) + "\t";
 			formattedData += str( sphere.center[1] ) + "\t";
-			#formattedData += str( sphere.center[2] ) + "\t";
+			formattedData += str( sphere.center[2] ) + "\t";
 			formattedData += str( sphere.radius);
 			formattedData += "\n";
 

### 2014-07-24 samplingMA.py
1

@@ -39,12 +39,13 @@ class LineSearch:
 		@param pnt: config point in c-space.  mapped. v3()'''
 		config_ = Config( v2(pnt.x, pnt.y), pnt.z );
 		config  = self.mapper.unmap(config_);
-		self.robot.setConfig(config_);
+		self.robot.setConfig(config);
 		timeclearance = self.obstMgr.time2obsts( self.robot, self.mapper );
 		return timeclearance;
 
 	def search(self):
 		'''search for the point in the medial axis'''
+		#print "\n=====================\nsearching..."
 		t = 1;
 		last_increse = False;
 		last_dist = self.dist2Obst(self.start);
@@ -52,6 +53,7 @@ class LineSearch:
 			temp = self.start + self.dir*t;
 			this_dist = self.dist2Obst(temp);
 			this_increase = ((this_dist-last_dist)>0);
+			#print this_dist;
 			if last_increse and not this_increase:
 				if not self.obstMgr.intersects(self.robot):
 					return temp, this_dist;
@@ -78,7 +80,7 @@ class Sphere:
 
 	def contains( self, point ):
 		'''determine if the sphre contains a point'''
-		dist = dist = (point - self.center).r();
+		dist = (point - self.center).r();
 		return dist <= self.radius;
 
 	def isClosed(self):
@@ -133,40 +135,14 @@ class SamplerV2:
 
 	def dist2obsts(self, config):
 		self.robot.setConfig(config);
-		return self.obstMgr.dist2obsts( self.robot );		l = 40;
-		maSamples = [];
-		for point in pntset:
-			#Check if within any discs.
-			good = True;
-			for disc in maSamples:
-				if disc.add( point ):
-					good = False;
-					#pntset.remove( point );
-					break;
-
-			if not good:
-				continue;
-
-			dir_x = random.randint( -100, 100 );
-			dir_y = random.randint( -100, 100);
-			if dir_x == dir_y == 0:
-				dir_x = dir_y = 50;
-			rand_dir = v2(dir_x, dir_y);
-			line_searcher = LineSearch( point, rand_dir, l, self.obstMgr, self.world );
-			maSample = line_searcher.search();
-			if maSample[0] is not None and maSample[1] >= 5:
-				newDisc = Disc( maSample[0], maSample[1] );
-				maSamples.append( newDisc );
-				#pntset.remove( point );
-
-		self.MASamples = copy.copy(maSamples);
[…]

### 2014-07-24 samplingMA.py
2

@@ -181,7 +181,7 @@ class SamplerV2:
 				self.partition.addSphere( sphere );
 
 
-	def __sampleMA__(self, pntset, rho ):
+	def __sampleMA__(self, pntset, rho = None ):
 		'''Sample spheres centered on Medial Axis in c-space.
 		@param pntset: A set of random points in free space. Coordinates are mapped.
 		@param rho   : number of points per unit volume.    '''
@@ -234,10 +234,33 @@ class SamplerV2:
 
 		spaceSize = self.mapper.scaledSpaceSize();
 		rho = float(n)/float( spaceSize[0]*spaceSize[1]*spaceSize[2] );
-		self.__sampleMA__(pntset, rho);
+		self.__sampleMA__(pntset);
 
 		self.samples += self.maSamples;
 
 		return self.maSamples;
 
+    	def randsample(self, n):
+		'''Sample spheres in c-space
+		@param n: (int) number of random points in free space'''
+		pntset = [];
+		for i in range(0, n):
+			#progressBar( float(len(pntset)) / n * 100);
+			rand_x 	   = random.randint( 0, self.world.WIDTH );
+			rand_y 	   = random.randint( 0, self.world.HEIGHT);
+			rand_theta = 0; #random.uniform( 0, 2*math.pi );
 
+			config  = Config(v2(rand_x, rand_y), rand_theta);
+			config_ = self.mapper.map( config );
+
+			if not self.partition.checkValid( v3(config_.x, config_.y, config_.orient) ):
+				continue;
+
+			# valid point	
+			self.robot.setConfig( config );
+			clearance = self.obstMgr.time2obsts( self.robot, self.mapper );
+			if clearance <= 0.1:
+				continue;				# disgard too small spheres
+			sphere = self.getSphere( config, clearance );
+			self.partition.addSphere( sphere );
+			self.samples.append( sphere );

### 2014-07-24 world.py

@@ -94,6 +94,6 @@ pygame.quit();
 
 sampler = SamplerV2( gameWorld );
 
-sampler.sample(1000);
+sampler.randsample(1000);
 #sampler.sampleSlice( math.pi/4 );
 sampler.save_data('spheres_complete.txt');

### 2014-07-24 samplingMA.py
3

@@ -252,12 +252,15 @@ class SamplerV2:
 
 			config  = Config(v2(rand_x, rand_y), rand_theta);
 			config_ = self.mapper.map( config );
+			self.robot.setConfig( config );
+			if self.obstMgr.intersects( self.robot ):
+				continue;
 
 			if not self.partition.checkValid( v3(config_.x, config_.y, config_.orient) ):
 				continue;
 
 			# valid point	
-			self.robot.setConfig( config );
+			
 			clearance = self.obstMgr.time2obsts( self.robot, self.mapper );
 			if clearance <= 0.1:
 				continue;				# disgard too small spheres

### 2014-07-24 world.py

@@ -94,6 +94,6 @@ pygame.quit();
 
 sampler = SamplerV2( gameWorld );
 
-sampler.randsample(1000);
+sampler.randsample(2000);
 #sampler.sampleSlice( math.pi/4 );
 sampler.save_data('spheres_complete.txt');

### 2014-07-24 obstacles.py
4

@@ -77,6 +77,8 @@ class ObstManager:
 
 	def intersects(self, robot):
 		'''determine if the robot intersects with any obstacles in the space'''
+		if self.inside( robot.position() ):
+			return True;
 		for obst in self.obsts:
 			if( robot.intersects(obst) ):
 				return True;

### 2014-07-24 samplingMA.py
5

@@ -189,6 +189,7 @@ class SamplerV2:
 		self.maSamples = [];
 		for point in pntset:
 			#Check if within any balls.
+			'''
 			good = True;
 			currentGridBalls = self.partition.getCurrentGridSpheres( point );
 			for ball in currentGridBalls:
@@ -198,7 +199,7 @@ class SamplerV2:
 
 			if not good:
 				continue;
-
+			'''
 			dir_x = random.randint( -100, 100 );
 			dir_y = random.randint( -100, 100 );
 			dir_z = 0; #random.randint( -100, 100 );
@@ -224,7 +225,7 @@ class SamplerV2:
 			#progressBar( float(len(pntset)) / n * 100);
 			rand_x 	   = random.randint( 0, self.world.WIDTH );
 			rand_y 	   = random.randint( 0, self.world.HEIGHT);
-			rand_theta = 0;#random.uniform( 0, 2*math.pi );
+			rand_theta = math.pi/2.0;#random.uniform( 0, 2*math.pi );
 
 			config  = Config(v2(rand_x, rand_y), rand_theta);
 			self.robot.setConfig( config );

### 2014-07-24 world.py

@@ -94,6 +94,6 @@ pygame.quit();
 
 sampler = SamplerV2( gameWorld );
 
-sampler.randsample(2000);
+sampler.sample(2000);
 #sampler.sampleSlice( math.pi/4 );
 sampler.save_data('spheres_complete.txt');

### 2014-07-24 samplingMA.py
6

@@ -26,7 +26,7 @@ class LineSearch:
 			return;
 
 		end = start + dir*length;
-		if self.dist2Obst(start) < self.dist2Obst(end):
+		if self.dist2Obst(start) > self.dist2Obst(end):
 			self.start = start;
 			self.end   = end;
 		else:
@@ -55,10 +55,16 @@ class LineSearch:
 			this_increase = ((this_dist-last_dist)>0);
 			#print this_dist;
 			if last_increse and not this_increase:
+				return temp, this_dist;
+				'''
+				config_ = Config( v2(temp.x, temp.y), te.z );
+				config  = self.mapper.unmap(config_);
+				self.robot.setConfig(config);
 				if not self.obstMgr.intersects(self.robot):
 					return temp, this_dist;
 				else:
 					return None, None;
+				'''
 			else:
 				t += 1;
 				last_increse = this_increase;
@@ -225,7 +231,7 @@ class SamplerV2:
 			#progressBar( float(len(pntset)) / n * 100);
 			rand_x 	   = random.randint( 0, self.world.WIDTH );
 			rand_y 	   = random.randint( 0, self.world.HEIGHT);
-			rand_theta = math.pi/2.0;#random.uniform( 0, 2*math.pi );
+			rand_theta = math.pi/4.0;#random.uniform( 0, 2*math.pi );
 
 			config  = Config(v2(rand_x, rand_y), rand_theta);
 			self.robot.setConfig( config );

### 2014-07-24 samplingMA.py
7

@@ -25,13 +25,18 @@ class LineSearch:
 		if dir is None:
 			return;
 
+
 		end = start + dir*length;
+
+		'''
 		if self.dist2Obst(start) > self.dist2Obst(end):
 			self.start = start;
 			self.end   = end;
 		else:
 			self.start = end;
-			self.end   = start;
+			self.end   = start;'''
+		self.start = start;
+		self.end = end;
 		pass;
 
 	def dist2Obst(self, pnt):

### 2014-07-24 obstacles.py
8

@@ -91,10 +91,10 @@ class ObstManager:
 			dists.append( obst.dist2robot(robot) );
 		return min(dists);
 
-	def time2obsts(self, robot, mapper):
+	def time2obsts(self, robot):
 		'''return the min time for a robot to collide with any obstacles'''
 		dist = self.dist2obsts(robot);
-		return dist / 20.0;
+		return dist / 5.0;
 
 	def closest_point(self, point):
 		'''get the nearest point in obstacles to a point. 

### 2014-07-24 samplingMA.py

@@ -45,7 +45,7 @@ class LineSearch:
 		config_ = Config( v2(pnt.x, pnt.y), pnt.z );
 		config  = self.mapper.unmap(config_);
 		self.robot.setConfig(config);
-		timeclearance = self.obstMgr.time2obsts( self.robot, self.mapper );
+		timeclearance = self.obstMgr.time2obsts( self.robot );
 		return timeclearance;
 
 	def search(self):
@@ -59,17 +59,16 @@ class LineSearch:
 			this_dist = self.dist2Obst(temp);
 			this_increase = ((this_dist-last_dist)>0);
 			#print this_dist;
+			if this_dist == 0.0:
+				return None, None;
 			if last_increse and not this_increase:
-				return temp, this_dist;
-				'''
-				config_ = Config( v2(temp.x, temp.y), te.z );
+				config_ = Config( v2(temp.x, temp.y), temp.z );
 				config  = self.mapper.unmap(config_);
 				self.robot.setConfig(config);
 				if not self.obstMgr.intersects(self.robot):
 					return temp, this_dist;
 				else:
 					return None, None;
-				'''
 			else:
 				t += 1;
 				last_increse = this_increase;
@@ -213,7 +212,7 @@ class SamplerV2:
 			'''
 			dir_x = random.randint( -100, 100 );
 			dir_y = random.randint( -100, 100 );
-			dir_z = 0; #random.randint( -100, 100 );
+			dir_z = 0;#random.randint( -100, 100 );
 			if dir_x == dir_y == dir_z == 0:
 				dir_x = dir_y = dir_z = 50;
 			rand_dir = v3(dir_x, dir_y, dir_z);
@@ -273,7 +272,7 @@ class SamplerV2:
 
 			# valid point	
 			
-			clearance = self.obstMgr.time2obsts( self.robot, self.mapper );
+			clearance = self.obstMgr.time2obsts( self.robot );
 			if clearance <= 0.1:
 				continue;				# disgard too small spheres
 			sphere = self.getSphere( config, clearance );

### 2014-07-28 UMAPRM.py
test

@@ -520,14 +520,15 @@ gameWorld = World( WIDTH, HEIGHT, obsts );
 print "Initializing sampler..."
 sampler = UMAPRMSampler(gameWorld);
 
-datafile2write = open( 'imgs/MAk_coverage/data.txt', 'w' );
-infostr = '';
-
 ##################################################
 #####           Render the world
 ##################################################
-for i in range( 1, 61 ):
-	for j in range(1, 41):
+filename = 'imgs/MAk_coverage/data_2.txt';
+datafile2write = open( filename, 'w' );
+
+for i in range( 1, 24 ):
+	for j in range(1, 11):		
+		infostr = '';
 		DISPLAYSURF = pygame.display.set_mode((WIDTH, HEIGHT));
 		DISPLAYSURF.fill((255,255,255));
 		for event in pygame.event.get():
@@ -537,7 +538,7 @@ for i in range( 1, 61 ):
         	pygame.display.update();
 		gameWorld.render( DISPLAYSURF );
 
-		num = 100*i;
+		num = 800 + 200*i;
 		print '=================================='
 		print num;
 		timestr = time.strftime('%a-%d-%b-%Y-%H:%M:%S')
@@ -545,21 +546,24 @@ for i in range( 1, 61 ):
 		starttime = datetime.now()
 		samples = sampler.sampleMAbk( num, DISPLAYSURF );
 		endtime = datetime.now()
-		print "time cost: {0} microseconds".format(((endtime - starttime).microseconds)/float(10));
+		print "time cost: {0} microseconds".format(((endtime - starttime).microseconds)/float(1000));
 		namestr += str(len(samples)) + '.PNG'
 		#pygame.image.save( DISPLAYSURF, namestr );
 
 
 		# Collect pixel info for analysis
-		infostr += "{0}\t{1}\t{2}\t".format( timestr, num, str(len(samples)) );
-		pixelreader = PixelReader( DISPLAYSURF );
+		#infostr += "{0}\t{1}\t{2}\t".format( timestr, num, str(len(samples)) );
+		pixelreader = PixelReader( DISPLAYSURF, gameWorld );
 		coverage = float(pixelreader.count( (255, 255, 255) ));
-		print 'Coverage:\t{0}'.format(coverage);
-		infostr += str(coverage) +'%\t{0}\n'.format( ((endtime - starttime).microseconds)/float(1000));
+		print "White Pixels: {0}".format(coverage);
[…]

### 2014-07-28 pixel_reader.py

@@ -1,25 +1,48 @@
 import pygame 
 import math
-
+from geometry import *
 
 
 class PixelReader:
 	'''A class to read and analysis pixel info'''
-	def __init__( self, surface ):
+	def __init__( self, surface, world ):
 		self.surface = surface.convert();
 		self.pxarray = pygame.PixelArray(surface);
 		self.width   = self.surface.get_width();
 		self.height  = self.surface.get_height();
+		self.obstMgr = world.obstMgr;
+		self.records = [];
+
+	def dist2wall(self, point, width, height):
+		dist = 1000000000;
+		near = None;
+		if width - point.x > point.x:
+			dist = float(point.x);
+		else:
+			dist = float(width - point.x);
+		if height - point.y > point.y:
+			if dist > point.y:
+				dist = float(point.y);
+		else:
+			if dist > height - point.y:
+				dist = float(height - point.y);
+		return dist;
 
 	def count(self, color):
 		'''Count the number of pixels with the give color'''
 		counter = 0;
-		for x in range( 0, self.width ):
-			for y in range( 0, self.height ):
+		for x in range( 1, self.width ):
+			for y in range( 1, self.height ):
 				#print self.pxarray[x,y];
 				#print self.surface.map_rgb(color);
 				if self.pxarray[x,y] == self.surface.map_rgb(color):
-					counter += 1;
+				 	near, dist = self.obstMgr.closest_point(v2(x,y));
+				 	if dist < 0:
+				 		continue;
+
+				 	dist2wall = self.dist2wall( v2(x,y), self.width, self.height );
+				 	counter += 1;					
+					self.records.append((v2(x,y), min(dist, dist2wall)));
 					pass;
 				pass;
 			pass;

### 2014-07-28 robot.py

@@ -65,12 +65,15 @@ class DiffDriveRobot:
 		self.config = config;
 		return self.getLine();
 
-	def render( self, surf ):
+	def render( self, surf, color_=None ):
 		'''Render the differential drive to the screen'''
 		if self.collision == False:
 			color = (80, 255, 80);
 		else:
 			color = (255,0,0);
+
+		if color_ is not None:
+			color = color_;
 
 		line = self.getLine();
 		line.render( surf, color, 5 );

### 2014-07-28 samplingMA.py

@@ -1,10 +1,20 @@
 import sys, os
 import random
+import time
 from robot import *
 from obstacles import *
 from geometry import *
 from sampling import CoordMapping
 from space_partition import *
+
+def display_update(t=0.0):
+	for event in pygame.event.get():
+		if event.type == pygame.QUIT:
+			pygame.quit();
+			sys.exit();
+
+	pygame.display.update();
+	time.sleep(t);
 
 class LineSearch:
 	def __init__( self, start, dir, length, obstMgr, robot, mapper ):
@@ -48,9 +58,9 @@ class LineSearch:
 		timeclearance = self.obstMgr.time2obsts( self.robot );
 		return timeclearance;
 
-	def search(self):
+	def search(self, surface=None):
 		'''search for the point in the medial axis'''
-		#print "\n=====================\nsearching..."
+		print "\n=====================\nsearching..."
 		t = 1;
 		last_increse = False;
 		last_dist = self.dist2Obst(self.start);
@@ -58,6 +68,9 @@ class LineSearch:
 			temp = self.start + self.dir*t;
 			this_dist = self.dist2Obst(temp);
 			this_increase = ((this_dist-last_dist)>0);
+			if surface is not None:
+				self.robot.render(surface);
+				display_update(0.2);
 			#print this_dist;
 			if this_dist == 0.0:
 				return None, None;
@@ -66,6 +79,9 @@ class LineSearch:
 				config  = self.mapper.unmap(config_);
 				self.robot.setConfig(config);
 				if not self.obstMgr.intersects(self.robot):
+					if surface is not None:
+						self.robot.render(surface, (255,0,0));
+						display_update(0.2);
 					return temp, this_dist;
 				else:
 					return None, None;
@@ -191,7 +207,7 @@ class SamplerV2:
 				self.partition.addSphere( sphere );
 
 
-	def __sampleMA__(self, pntset, rho = None ):
+	def __sampleMA__(self, pntset, surface=None, rho=None ):
 		'''Sample spheres centered on Medial Axis in c-space.
 		@param pntset: A set of random points in free space. Coordinates are mapped.
 		@param rho   : number of points per unit volume.    '''
@@ -217,7 +233,7 @@ class SamplerV2:
 				dir_x = dir_y = dir_z = 50;
 			rand_dir = v3(dir_x, dir_y, dir_z);
[…]

### 2014-07-28 world.py

@@ -58,7 +58,8 @@ for event in pygame.event.get():
         pygame.quit()
         sys.exit()
 gameWorld.render( DISPLAYSURF );
-pygame.image.save( DISPLAYSURF, 'world.PNG' );
+pygame.display.update();
+#pygame.image.save( DISPLAYSURF, 'world.PNG' );
 
 
 '''
@@ -93,7 +94,6 @@ pygame.quit();
 
 
 sampler = SamplerV2( gameWorld );
-
-sampler.sample(2000);
+sampler.sample(2000, DISPLAYSURF);
 #sampler.sampleSlice( math.pi/4 );
 sampler.save_data('spheres_complete.txt');

### 2014-07-28 Writing/Topology/some_questions.tex
data analysis

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{algpseudocode}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\title{Some Questions}
\date{}
\begin{document}
	Say we have a very simple world as shown in Figure \ref{fig:world}. The gray block in the middle is an obstacle. Dotted lines are medial axis. And our algorithm gives some discs. By connecting the centers of these discs, we got a rather sparse road map.\\

	If I understand the definition of "retraction" correctly, I simplify the topology of the road map as in Figure \ref{fig:topology}. The second graph in Figure \ref{fig:topology} should be homotopy equivalent to the road map. Suppose we do have an algorithm that is capable of doing the retraction.\\

	Now the simplified graph says there are 3 obstacles in the space. It seems this problem cannot be solved, because given 3 circles, you cannot identify if there is any obstacles be tween them. So are 4 and 5 circles. And this is just in a 2D space. It could be worse in 3D or higher dimension.

	What can we do with the simplified graph? It seems we can't use it to do motion planning because all points are in one place now. And we cannot use it to say how many obstacles there are, because of the problem above.

  \begin{figure}[p]
  \centering
  \includegraphics[scale=0.5]{init.pdf}  
  \caption{Simple World and Its road map from MA Sampling }   
  \label{fig:world} 
  \end{figure}

  \begin{figure}[p]
  \centering
  \includegraphics[scale=0.5]{topo.pdf}  
  \caption{Simplified topology}   
  \label{fig:topology} 
  \end{figure} 
\end{document}

### 2014-07-28 imgs/MAk_coverage/parse.py

@@ -1,0 +1,47 @@
+import pygame
+from pygame.locals import *
+import sys
+import math
+
+def parse(filename):
+
+	file2write= open( 'analysis.txt', 'w' );
+
+	file2read = open( filename, 'r' );
+	lineNum   = 0;
+	info_dict = dict();
+	last_num  = 1000;
+	counter = [0]*200;
+	for line in file2read:
+		info = line.split( '\t' );
+		if len(info) < 3:
+			continue;
+		num_pnts = int(info[0]);
+		num_disc = int(info[1]);
+		x_coord  = int(info[2]);
+		y_coord  = int(info[3]);
+		dist     = float(info[4]);
+		
+		if num_pnts == last_num:
+			counter[ int(dist) ] += 1;
+		else:
+			print "Finished parsing {0}".format(last_num);
+			new_info = '';
+			for i in range(0, len(counter)):
+				if counter[i] == 0:
+					continue;
+				info_str = "{0}\t{1}\t{2}\n".format( last_num, i, counter[i] );
+				new_info += info_str;
+			file2write.write( new_info );
+
+			counter = [0]*200;
+
+		last_num = num_pnts;
+
+
+	file2write.close();
+	file2read.close();
+	return;
+
+if __name__ == "__main__":
+	parse( "data_2.txt" );

### 2014-07-28 UMAPRM.py
analysis

@@ -523,11 +523,11 @@ sampler = UMAPRMSampler(gameWorld);
 ##################################################
 #####           Render the world
 ##################################################
-filename = 'imgs/MAk_coverage/data_2.txt';
+filename = 'imgs/MAk_coverage/data_3.txt';
 datafile2write = open( filename, 'w' );
 
 for i in range( 1, 24 ):
-	for j in range(1, 11):		
+	for j in range(1, 4):		
 		infostr = '';
 		DISPLAYSURF = pygame.display.set_mode((WIDTH, HEIGHT));
 		DISPLAYSURF.fill((255,255,255));
@@ -538,7 +538,7 @@ for i in range( 1, 24 ):
         	pygame.display.update();
 		gameWorld.render( DISPLAYSURF );
 
-		num = 800 + 200*i;
+		num = 200*i;
 		print '=================================='
 		print num;
 		timestr = time.strftime('%a-%d-%b-%Y-%H:%M:%S')
@@ -554,9 +554,9 @@ for i in range( 1, 24 ):
 		# Collect pixel info for analysis
 		#infostr += "{0}\t{1}\t{2}\t".format( timestr, num, str(len(samples)) );
 		pixelreader = PixelReader( DISPLAYSURF, gameWorld );
-		coverage = float(pixelreader.count( (255, 255, 255) ));
+		coverage = float(pixelreader.count( (255, 255, 255), samples ));
 		print "White Pixels: {0}".format(coverage);
-		infostr += str(coverage) +'\t{0}\n'.format( ((endtime - starttime).microseconds)/float(1000));
+		#infostr += str(coverage) +'\t{0}\n'.format( ((endtime - starttime).microseconds)/float(1000));
 		#DISPLAYSURF = None;
 
 		for record in pixelreader.records:

### 2014-07-28 imgs/MAk_coverage/parse.py

@@ -5,13 +5,13 @@ import math
 
 def parse(filename):
 
-	file2write= open( 'analysis.txt', 'w' );
+	file2write= open( 'analysis2.txt', 'w' );
 
 	file2read = open( filename, 'r' );
 	lineNum   = 0;
 	info_dict = dict();
-	last_num  = 1000;
-	counter = [0]*200;
+	last_num  = 200;
+	counter = [0]*300;
 	for line in file2read:
 		info = line.split( '\t' );
 		if len(info) < 3:
@@ -44,4 +44,4 @@ def parse(filename):
 	return;
 
 if __name__ == "__main__":
-	parse( "data_2.txt" );
+	parse( "data_3.txt" );

### 2014-07-28 pixel_reader.py

@@ -28,7 +28,7 @@ class PixelReader:
 				dist = float(height - point.y);
 		return dist;
 
-	def count(self, color):
+	def count(self, color, discs):
 		'''Count the number of pixels with the give color'''
 		counter = 0;
 		for x in range( 1, self.width ):
@@ -39,7 +39,8 @@ class PixelReader:
 				 	near, dist = self.obstMgr.closest_point(v2(x,y));
 				 	if dist < 0:
 				 		continue;
-
+				 	if self.insideDisc( x, y, discs ):
+				 		continue;
 				 	dist2wall = self.dist2wall( v2(x,y), self.width, self.height );
 				 	counter += 1;					
 					self.records.append((v2(x,y), min(dist, dist2wall)));
@@ -47,3 +48,9 @@ class PixelReader:
 				pass;
 			pass;
 		return float(counter);
+
+	def insideDisc(self, x, y, discs):
+		for disc in discs:
+			if disc.inside( v2(x,y) ):
+				return True;
+		return False;

### 2014-08-09 Writing/MedialAxis_v2/UncoveredPixels_2D.tex
thinking about breaking a graph into several parts

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.png,.jpg}
\usepackage{algpseudocode}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}

\title{Uncovered Pixels in 2D}
\date{}
\begin{document}
  \maketitle

  By setting the number of random points in the whole space from 200 ~ 7000, repeating 5 times, our algorithm collected some data about uncovered pixels in 2D space. The 2D space is 800x800 large, and all discs sampled by our algorithm have radius at least 10. The numbers in the charts below are the average number of 5 experiments.

  In the charts you are going to see, the x-axis indicates the number of random points in the whole space, the y-axis indicates the distance from such a point to obstacles or the boundary of the world, while the z-axis is the amount of pixels. For example, (7000, 10, 8) means, with initially 7000 points, our algorithm left 8 pixels that are 10 distance away from obstacles or boundaries.

  \section{Plotting Overview}

  \includegraphics[scale=0.5]{overview.PNG}

  As we can see in the picture, with more initial random points, we are expecting less far-from-obstacle points to be uncovered by discs. But still, we observe a few points exception points, which means our algorithm will left some holes in the free space to be uncovered, although such holes are really small. Increasing the number of random points seems to have the ability of reducing such exception points. There is no uncovered point that is 10 distance away from obstacles with 7000 initial random points.

  \section{Grown Obstacles}
  By setting the minimum radius of discs to be 10, we are expecting 0 point that is 10 distance away from obstacles to be uncovered. Our experiment seems to be supporting the theory. The graph below shows the number of points that have 10 to 30 clearance with different initial random points.

  \includegraphics[scale=0.45]{7000_10_8.PNG}

  With 7000 random points, there are still 8 points that are 10 distance away from obstacles, although we are expecting the number to be 0. This is probably not unacceptable, because the algorithm does not guarantee to sample every point on the boundary of existing discs. And 8 points out of 800x800 points is not too bad.

  \section{The Trend}

  By projecting data to x-y plane, we can see the trend of reducing far-from-obstacle points.

  \includegraphics[scale=0.6]{overhead_view.PNG}

\end{document}

### 2014-08-09 UMAPRM.py

@@ -526,8 +526,8 @@ sampler = UMAPRMSampler(gameWorld);
 filename = 'imgs/MAk_coverage/data_3.txt';
 datafile2write = open( filename, 'w' );
 
-for i in range( 1, 24 ):
-	for j in range(1, 4):		
+for i in range( 1, 36 ):
+	for j in range(1, 6):		
 		infostr = '';
 		DISPLAYSURF = pygame.display.set_mode((WIDTH, HEIGHT));
 		DISPLAYSURF.fill((255,255,255));

### 2014-08-09 topology/graph.py

@@ -1,0 +1,323 @@
+import sys, os, math
+
+class Node:
+	def __init__(self, name, group, value = 0):
+		self.name  = name;
+		self.value = value;
+		self.group = group;
+
+#	def __eq__( self, other ):
+#		return self.name == other.name and self.value == other.value;
+
+class Graph:
+	def __init__(self):
+		self.graphdict = dict();
+		'''
+		A graph is of this format:
+
+        {
+        	'A' : [('B', 1), ('C', 2)],
+        	'B' : [('A', 1), ('C', 3)],
+        	'C' : [('A', 2), ('B', 3)]
+        }
+
+       	     1
+        A ------- B
+         \       /
+        2 \     / 3
+           \   /
+             C 
+		'''  
+	############################################################
+	########			Utility private methods        #########
+
+	def __get_adj_nodes__(self, node):
+		edges = self.graphdict[node];
+		nodes = [];
+		for edge in edges:
+			nodes.append( edge[0] );
+		return nodes;
+
+	def __edge_eq__( self, edge1, edge2 ):
+		'''determine if two undirected edges are equal'''
+		node_eq   = False;
+		weight_eq = False;
+		if edge1[0] == edge2[0] and edge1[0] == edge2[0]:
+			node_eq = True;
+		elif edge1[0] == edge2[1] and edge1[1] == edge2[0]:
+			node_eq = True;
+		if edge1[2] == edge2[2]:
+			weight_eq = True;
+
+		return node_eq and weight_eq;
+
+
+	############################################################
+	########			Utility prublic methods        #########
+	def copy(self):
+		'''return a copy of the graph. Nodes and edges all remain the same memory addresses.
+		Only the reference of of graph itself is different. '''
+		newgraph  = Graph();
+		#all_nodes = self.get_all_nodes();
+		all_edges = self.get_all_edges();
+		newgraph.add_edges( all_edges );
+		return newgraph;
+
+	def size(self):
+		'''return the size of the graph. |E|'''
+		return len(self.get_all_edges());
+
+	def contains(self, node_or_edge):
+		'''determine if an edge or node exist in the graph'''
+		if isinstance( node_or_edge, tuple ):	# This is an edge
+			# Determine is the two nodes exist
+			if not self.graphdict.has_key( node_or_edge[0] ) or not self.graphdict.has_key( node_or_edge[1] ):
+				return False;
[…]

### 2014-08-09 topology/matrix.py

@@ -1,0 +1,15 @@
+import sys, os, math
+import numpy
+
+class Matrix:
+	def __init__(self, mat):
+		'''load from a simple 2d matrix to a numpy matrix'''
+		self.mat = numpy.matrix( mat );
+		self.origin_mat = mat;
+
+	def mat_rank(self):
+		return numpy.linalg.matrix_rank(self.mat);
+
+mat = [[1, 1, 1,1],[1, 1, 1,1],[1, 1, 1,1],[1, 1, 1,1]];
+nummat = Matrix( mat );
+print nummat.mat_rank();

### 2014-08-09 topology/priority_queue.py

@@ -1,0 +1,62 @@
+import sys, os
+import itertools
+from heapq import *
+
+class PriorityQueue:
+	def __init__(self):
+		self.mPriQue = []                    	# list of entries arranged in a heap
+		self.mEntryFinder = {}               	# mapping of tasks to entries
+		self.mREMOVED = '<self.mREMOVED-task>'  # placeholder for a self.mREMOVED task
+		self.mCounter = itertools.count()     	# unique sequence count
+
+
+	def push(self, task, priority=0):
+	        'Add a new task or update the priority of an existing task'
+	        if task in self.mEntryFinder:
+	            self.remove_task(task)
+	        count = next(self.mCounter)
+	        entry = [priority, count, task]
+	        self.mEntryFinder[task] = entry
+	        heappush(self.mPriQue, entry)
+
+	def remove_task(self, task):
+	        'Mark an existing task as self.mREMOVED.  Raise KeyError if not found.'
+	        entry = self.mEntryFinder.pop(task)
+	        entry[-1] = self.mREMOVED
+
+	def pop(self):
+	        'Remove and return the lowest priority task. Raise KeyError if empty.'
+	        while self.mPriQue:
+	            priority, count, task = heappop(self.mPriQue)
+	            if task is not self.mREMOVED:
+	                del self.mEntryFinder[task]
+	                return task
+	        raise KeyError('pop from an empty priority queue')
+
+	def get_all(self):
+		'''get all not removed items. the returned list will be sorted'''
+		tasks = [];
+		for priority, count, task in self.mPriQue:
+			if task is not self.mREMOVED:
+				tasks.append( task );
+		return tasks;		
+
+	def isEmpty(self):
+		return len(self.mPriQue) == 0;
+
+'''
+pq = PriorityQueue()
+
+pq.push(4,4);
+pq.push(3,3);
+pq.push(2,2);
+pq.push(6,6);
+pq.push(7,7);
+pq.push(9,9);
+
+print pq.pop()
+print pq.pop()
+pq.remove_task(6);
+pq.remove_task(7);
+print pq.get_all();
+'''

### 2014-08-09 topology/graph.py
update

@@ -1,5 +1,7 @@
 import sys, os, math
 
+from priority_queue import *
+
 class Node:
 	def __init__(self, name, group, value = 0):
 		self.name  = name;
@@ -149,7 +151,7 @@ class Graph:
 		return self.num_of_loops() == 0;
 
 	def mergeable_with(self, other):
-		'''define two graph to be mergable, if
+		'''define two graph to be mergable, if they satisfy both
 		1. they share some nodes
 		2. the new graph is loop free
 		'''
@@ -299,6 +301,53 @@ class GraphBreaker(object):
 		'''break the graph into several parts, and save them to another non-connected graph'''
 		graphs = [];
 		self_edges = self.origin_graph.get_all_edges();
+
+
+	def merge_graphs(self, graphs):
+		pq = PriorityQueue();
+		for graph in graphs:
+			pq.push( graph, graph.size() );
+
+		while not pq.isEmpty():
+			smallest_graph = pq.pop();
+			choices = [];
+			max_size = 1000;
+
+			small_size_graphs = pq.get_smalls( smallest_graph.size() ); # Choose all graphs such that 
+																		# 1. they have priority no less than current one, and 
+																		# 2. when merge with the smallest one they get a same size new graph
+			for graph in small_size_graphs:
+				if smallest_graph.mergeable_with( graph ):		# test if they are mergeable
+					choices.append( graph );
+
+			if len(graph) == 0:									# if no mergeable graph with the smallest one
+				continue;
+
+			# Now we have all graphs mergeable with the smallest graph that will produce the same sized new graph
+			''' naive strategy
+			graphs.remove(smallest);
+			graphs.remove( choices[0] );
+			pq.remove_task( choices[0] );
+			smallest_graph.self_merge_with( choices[0] );
+			graphs.append( smallest_graph );
+			pq.push( smallest_graph, smallest_graph.size() );
+			'''
+
+			'''better strategy:
+			--------------------------------------------------------------------------
+			define 'credit' for a list of graphs as:
+			The sum of the number of all mergeable graphs for every graph in the list
+			--------------------------------------------------------------------------
+			Merging two graphs means decreasing the credit by at least two.
+			With more credits, we can merge more graphs in the list.
+			So we prefer to merge graphs that results in larger credit. 
+			(Or, we prefer to merge graphs that decrease credit least.)
+			'''
+			
+
+
+
+
 
 
 graph = Graph();

### 2014-08-09 topology/priority_queue.py

@@ -39,7 +39,22 @@ class PriorityQueue:
 		for priority, count, task in self.mPriQue:
 			if task is not self.mREMOVED:
 				tasks.append( task );
-		return tasks;		
+		return tasks;
+
+	def get_smalls(self, prior):
+		'''get all tasks with the same priority( larger than prior )'''
+		tasks = [];
+		prev_prio = 0;
+		first = True;
+		for priority, count, task in self.mPriQue:
+			if task is not self.mREMOVED:
+				if first and priority >= prior:
+					prev_prio = priority;
+					first = False;
+
+				if priority == prev_prio:
+					tasks.append( task );
+					prev_prio = priority;
 
 	def isEmpty(self):
 		return len(self.mPriQue) == 0;

### 2014-08-12 topology/graph.py
fdafdsa

@@ -11,6 +11,9 @@ class Node:
 #	def __eq__( self, other ):
 #		return self.name == other.name and self.value == other.value;
 
+	def same_name_with( self, other ):
+		return self.name == other.name;
+
 class Graph:
 	def __init__(self):
 		self.graphdict = dict();
@@ -155,6 +158,8 @@ class Graph:
 		1. they share some nodes
 		2. the new graph is loop free
 		'''
+		if self == other:
+			return False;
 		share_nodes = self.share_nodes_with( other );
 		if not share_nodes:
 			return False;
@@ -162,12 +167,33 @@ class Graph:
 		new_graph_loop_free = merged_graph.loop_free();
 		return share_nodes and new_graph_loop_free;
 
+	def strong_mergeable_with(self, other):
+		'''define two graph to be strong mergable, if they satisfy all
+		1. they share some nodes
+		2. the new graph is loop free
+		3. no nodes have neighbors more than 2.
+		'''
+		if self == other:
+			return False;
+		share_nodes = self.share_nodes_with( other );
+		if not share_nodes:
+			return False;
+		merged_graph = self.merge_with( other );
+		new_graph_loop_free = merged_graph.loop_free();
 
+		nodes = merged_graph.get_all_nodes();
+		for node in nodes:
+			if len(merged_graph.get_edges_of( node )) > 2:
+				return False;
+
+		return share_nodes and new_graph_loop_free;
+
+	'''
 	def self_merge_with(self, other):
-		'''merge the other graph with self. do not return a new graph. self is changed'''
+		''merge the other graph with self. do not return a new graph. self is changed''
 		otheredges = other.get_all_edges();
 		self.add_edges( otheredges );
-		return;
+		return;'''
 
 	def merge_with( self, other ):
 		'''Merge with another graph. return a new graph, while self remain unchanged'''
@@ -302,36 +328,57 @@ class GraphBreaker(object):
 		graphs = [];
 		self_edges = self.origin_graph.get_all_edges();
 
+		for edge in self_edges:
+			graph = Graph();
+			graph.add_edges( edge );
+			graphs.append( graph );
+
+		return self.merge_graphs( graphs );
+
 
 	def merge_graphs(self, graphs):
 		pq = PriorityQueue();
 		for graph in graphs:
 			pq.push( graph, graph.size() );
-
-		while not pq.isEmpty():
[…]

### 2014-08-12 topology/priority_queue.py

@@ -56,8 +56,13 @@ class PriorityQueue:
 					tasks.append( task );
 					prev_prio = priority;
 
+		return tasks;
+
 	def isEmpty(self):
 		return len(self.mPriQue) == 0;
+
+	def size(self):
+		return len(self.mPriQue);
 
 '''
 pq = PriorityQueue()

### 2014-08-14 Writing/Final/article.tex
Dual Shape

\title{ Determine Paths in the Same Homotopy Class }
\author{
        Yinan Zhang\\
        Department of Computer Science\\
        Dartmouth College\\
        Hanover, New Hampshire 03755, \underline{US}
        \and
        Devin Balkcom \\
        Department of Computer Science\\
        Dartmouth College\\
        Hanover, New Hampshire 03755, \underline{US}
}
\date{\today}

\documentclass[11pt]{article}

\begin{document}
\maketitle

\begin{abstract}
Describing the  \ldots
\end{abstract}

\section{Introduction}
This is time for all good men to come to the aid of their party!

\section{Related Work}\label{related work}
In this section, we first discuss the basics of sampling-based motion planning and the method of sampling on medial axis. With the information of positions and their clearance in c-space, we have samples as spheres. We then discuss the dual shapes of the union of balls which plays an important role in understanding the shape of c-space and its topology. Some works on graph theory and topology will finally be introduced.

\begin{description}
\item[A] \emph{Sampling-based Motion Planning} \hfill \\

\item[B] \emph{Medial Axis Sampling} \hfill \\

\item[C] \emph{Dual Shapes of Unions of Balls} \hfill\\

\item[D] \emph{Betti Numbers} \hfill \\

\item[E] \emph{Homotopy Class} \hfill \\

\end{description}

\section{Our Method}\label{method}

Traditionally, sampling based algorithms will build a graph for configuration space. These kind of graphs is proved to be able to find near optimal path, but can hardly be used to analysis the topology of paths. We want to to build a stronger represent of c-space that is both able to cover optimal path and study the topology structure of c-space. In this section, we are trying to answer the question of "are two paths in the same homotopy class". We will first give the outline of our algorithm, and introduce each phase step by step.

\begin{description}

\item[A] \emph{The Algorithm} \hfill \\

\item[B] \emph{Sampling in C-Space} \hfill \\

\item[C] \emph{Constructing Hypergraph of C-Space} \hfill \\

\item[D] \emph{Breaking A Graph into Loop-free Parts} \hfill\\

\item[E] \emph{Determine Paths Homotopy Class} \hfill \\

\end{description}

\section{Experiments}\label{experiments}
We now describe the some experiments and their results.

\section{Conclusions and Future Work}\label{conclusions}
We worked hard, and achieved very little.

\bibliographystyle{abbrv}
\bibliography{main}

\end{document}

### 2014-08-14 UMAPRM.py

@@ -71,7 +71,7 @@ class Disc:
 		if surf is None:
 			return;
 
-		pygame.draw.circle( surf, color, (int(self.center.x), int(self.center.y)), int(self.radius) )
+		pygame.draw.circle( surf, color, (int(self.center.x), int(self.center.y)), int(self.radius), 1 )
 		
 		if mode == 2:
 			for point in self.samples:
@@ -178,6 +178,19 @@ class UMAPRMSampler:
 		self.world = world;
 		self.obstMgr = self.world.obstMgr;
 		self.MASamples = [];
+
+	def save_data( self, samples, filename ):
+		'''Save sampled spheres. Write data to a file'''
+		file2write = open( filename, 'w' );
+		formattedData = "";
+		for sphere in samples:
+			formattedData += str( sphere.center[0] ) + "\t";
+			formattedData += str( sphere.center[1] ) + "\t";
+			formattedData += str( sphere.radius);
+			formattedData += "\n";
+
+		file2write.write( formattedData );
+		file2write.close();
 
 	def nearPoint(self, pnt):
 		searcher = LineSearch(None, None, 0, self.obstMgr, self.world);
@@ -377,7 +390,7 @@ class UMAPRMSampler:
 		return maSamples;
 
 	def sampleMAbk(self, n, surf = None):
-		'''randomly sample disc on MA, and sample on the boundary of existing discs'''
+		'''randomly sample disc on MA, and sample on the boundary of existing discs with k-nearest'''
 		pntset = [];
 		for i in range(0, n):
 			#progressBar( float(len(pntset)) / n * 100);
@@ -421,6 +434,8 @@ class UMAPRMSampler:
 				#pntset.remove( point );
 
 		self.MASamples = copy.copy(maSamples);
+		print len(maSamples);
+		
 		########
 		## Deal with points left outside any existing discs.
 		#----- Don't do anything for now.
@@ -441,7 +456,7 @@ class UMAPRMSampler:
 					disc.samples += knear;
 					bndpntset += disc.getbndpoints();
 					if roundIdx == 1:
-						disc.render( surf);
+						disc.render( surf, 2 );
 						self.refreshPygame(0);
 
 			for bndpnt in bndpntset:
@@ -459,7 +474,7 @@ class UMAPRMSampler:
 					newDisc = Disc(bndpnt, dist2obst);
 					maSamples.append( newDisc );
 					newAdded += 1; 
[…]

### 2014-08-14 topology/alphashape.py

@@ -1,0 +1,216 @@
+
+import sys, os, math;
+import pygame;
+
+from triangulate import *;
+from geometry import *
+
+
+
+class HypergraphNode:
+	def __init__(self):
+		self.triangles = [];
+		self.nodes     = [];
+
+	def addTriangle(self, triangle):
+		if triangle not in self.triangles:
+			self.triangles.append( triangle );
+
+	def addNode(self, node):
+		if node not in self.nodes:
+			self.nodes.append( node );
+
+def isEdgeValid( edge ):
+	'''edge = (ball1, ball2, weight)'''
+	A = v2(edge[0][0],edge[0][1]);
+	B = v2(edge[1][0],edge[1][1]);
+	return (A-B).r() <= edge[0][2] + edge[1][2];  
+
+def triangleFilter( triangles, alpha = 0.5, surf = None ):
+	edges = [];
+	edge_points = [];
+
+	for triangle in triangles:
+
+		ball1 = triangle.spheres[0];
+		ball2 = triangle.spheres[1];
+		ball3 = triangle.spheres[2];
+
+		pa = triangle.vertices[0];
+		pb = triangle.vertices[1];
+		pc = triangle.vertices[2];
+
+		#Lengths of sides of triangle
+		a = (pa-pb).r();
+		b = (pb-pc).r();
+		c = (pc-pa).r();
+
+		# Semiperimeter of triangle 
+		s = (a+b+c) / 2.0;
+
+		# Area of triangle 
+		area = math.sqrt( s*(s-a)*(s-b)*(s-c) );
+
+		circum_r = a*b*c/(4.0*area);
+
+		# Radius filter
+		if circum_r < ball1[2] or circum_r < ball2[2] or circum_r < ball3[2]:
+			edges.append( (ball1, ball2, 0) );
+			edges.append( (ball2, ball3, 0) );
+			edges.append( (ball1, ball3, 0) );
+
+	return edges;
+
+def isTriangleValid( triangle, surface ):
+	ball1 = triangle.spheres[0];
+	ball2 = triangle.spheres[1];
+	ball3 = triangle.spheres[2];
+	A = v2(ball1[0], ball1[1]);		r_a = ball1[2];
+	B = v2(ball2[0], ball2[1]);		r_b = ball2[2];
+	C = v2(ball3[0], ball3[1]);		r_c = ball3[2];
+
+	#if (A-B).r() > (r_a+r_b) or (A-C).r() > (r_a + r_c) or (B-C).r() > (r_b+r_c):
[…]

### 2014-08-14 topology/cgal/helloWorld.cpp

@@ -1,0 +1,84 @@
+#include <CGAL/Exact_predicates_inexact_constructions_kernel.h>
+#include <CGAL/Weighted_point.h>
+#include <CGAL/Weighted_alpha_shape_euclidean_traits_2.h>
+#include <CGAL/Regular_triangulation_2.h>
+#include <CGAL/Alpha_shape_2.h>
+#include <iostream>
+#include <fstream>
+#include <vector>
+#include <list>
+typedef CGAL::Exact_predicates_inexact_constructions_kernel K;
+typedef K::FT FT;
+typedef K::Point_2 Point_base;
+typedef CGAL::Weighted_point<Point_base,FT>  Point;
+typedef CGAL::Weighted_alpha_shape_euclidean_traits_2<K> Gt;
+typedef CGAL::Regular_triangulation_vertex_base_2<Gt> Rvb;
+typedef CGAL::Alpha_shape_vertex_base_2<Gt,Rvb> Vb;
+typedef CGAL::Regular_triangulation_face_base_2<Gt> Rf;
+typedef CGAL::Alpha_shape_face_base_2<Gt, Rf>  Fb;
+typedef CGAL::Triangulation_data_structure_2<Vb,Fb> Tds;
+typedef CGAL::Regular_triangulation_2<Gt,Tds> Triangulation_2;
+typedef CGAL::Alpha_shape_2<Triangulation_2>  Alpha_shape_2;
+typedef Alpha_shape_2::Alpha_shape_edges_iterator Alpha_shape_edges_iterator;
+template <class InputIterator, class OutputIterator>
+void
+alpha_edges(InputIterator begin, InputIterator end,
+        const FT &Alpha,
+        bool mode,
+        OutputIterator out)
+  // Generate Alpha Shape
+{
+  std::vector<Gt::Segment_2> V_seg;
+  Alpha_shape_2 A(begin,end);
+  if (mode)
+    { A.set_mode(Alpha_shape_2::GENERAL); }
+  else
+    { A.set_mode(Alpha_shape_2::REGULARIZED); };
+  A.set_alpha(Alpha);
+  for(Alpha_shape_edges_iterator it =  A.alpha_shape_edges_begin();
+      it != A.alpha_shape_edges_end();
+      ++it){
+  
+
+    *out++ = A.segment(*it);
+  }
+}
+bool
+file_input(std::list<Point>& L)
+{
+  std::ifstream is("./balls.txt", std::ios::in);
+  if(is.fail())
+    {
[…]

### 2014-08-14 topology/geometry.py

@@ -1,0 +1,640 @@
+#! /usr/bin/python
+
+"""
+Reference: Trac 0.10.4 https://trac.assembla.com/icfpc08-csail/
+"""
+
+"""
+A small library of 2D geometric primitives.
+ - angle: a routine which normalizes angles to (-pi,pi].
+ - v2:           2D cartesian vectors in the plane.
+ - line_segment: a line segment from one 2D point to another 2D point.
+ - circle:       a circle in the plane.
+ - arc:          a directed arc of a circle.
+ - path:         a list of line_segment and arc objects.
+
+--------------------------
+Modified by Yinan Zhang.
+"""
+
+import pygame
+
+__author__ = 'Chris Lesniewski <ctl mit edu>'
+__revision__ = '$Revision$'
+
+
+from math import sqrt, pi, degrees, radians, cos, sin, acos, asin, atan2
+
+__all__ = [
+  'pi', 'degrees', # re-exported from math
+  'angle', 'v2', 'v3', 'line_segment', 'circle', 'arc', 'path',
+]
+ 
+
+
+# Evaluate this as a string so that constants can be folded.
+exec '''
+def angle( theta ):
+  'Normalize an angle to the range [-pi,pi].'
+  return ( ( theta + %(pi)r ) %% (2*%(pi)r) ) - %(pi)r
+''' % { 'pi': pi }
+
+#========================================================================================
+# 2D vector
+#========================================================================================
+class v2( object ):
+  'Represents a 2D point with coordinates (x,y).'
+  __slots__ = ['x','y']
+
+  def __init__( self, x, y ):
+    self.x = x
+    self.y = y
+
+  @classmethod
+  def polar( cls, r, radians ):
+    'Construct a vector from a length and angle.'
+    return cls( r*cos(radians), r*sin(radians) )
+
+  @classmethod
+  def from_angle( cls, radians ):
+    'Construct a unit vector from an angle.'
+    return cls( cos(radians), sin(radians) )
+
+  def __str__( self ):
+    return '(%.3f,%.3f)' % ( self.x, self.y )
+  def __repr__( self ):
+    return 'v2(%r,%r)' % ( self.x, self.y )
+  def jgraph( self ):
+    'Render as a jgraph command.'
+    return 'newcurve pts %f %f marktype box\n' % ( self.x, self.y )
+
+
+  def __eq__( self, other ):
+    return self.x == other.x and self.y == other.y
+  def __ne__( self, other ):
[…]

### 2014-08-14 topology/triangulate.py

@@ -1,0 +1,100 @@
+import sys, os, math
+import pygame
+import numpy
+
+from scipy.spatial import Delaunay
+from geometry import *
+
+class Triangle:
+	def __init__(self, vert1, vert2, vert3):
+		'''v1, v2, v3 are all instances of geometry.v2(x,y)'''
+		self.vertices = [vert1, vert2, vert3];
+		self.spheres = [];
+		self.ifValid = True;
+
+	def addSpheres(self, spheres):
+		self.spheres = spheres;
+
+	def findSpheres( self, spheres ):
+		for vert in self.vertices:
+			for sphere in spheres:
+				if (sphere[0]-vert.x)**2 + (sphere[1]-vert.y)**2 <= 2:
+					self.spheres.append( sphere );
+
+	def render(self, surface, mode = 1, color = ( 0, 255, 0 ) ):
+		pointlist = [ (self.vertices[0].x, self.vertices[0].y), (self.vertices[1].x, self.vertices[1].y), (self.vertices[2].x, self.vertices[2].y) ];
+
+		pygame.draw.polygon( surface, color, pointlist, mode );
+
+class Triangulator:
+	def __init__(self):
+		self. triangles = [];
+
+	def triangulate(self, points):
+		'''points has the form: [(x1,y1), (x2,y2), ...., (xn, yn)]'''
+		np_points = numpy.array( points );
+		tris 	  = Delaunay( points );
+		triIdx    = tris.vertices;
+		for tri in triIdx:
+			vert1 = v2(points[ tri[0] ][0], points[ tri[0] ][1] );
+			vert2 = v2(points[ tri[1] ][0], points[ tri[1] ][1] );
+			vert3 = v2(points[ tri[2] ][0], points[ tri[2] ][1] );
+			self.triangles.append( Triangle(vert1, vert2, vert3) );
+
+		return self.triangles;
+
+
+def load_data( filename):
+	'''load spheres information from file'''
+	file2read = open( filename, 'r' );
+	lineNum = 0;
+	spheres = [];
+	for line in file2read:
+		if( lineNum % 100 == 0 ):
+			print "Reading line: {0}".format( lineNum );
+		lineNum += 1;
+		strSphere = line;
+		info = strSphere.split( '\t' );
+		pos = [0] * 2;
+		pos[0] = float( info[0] );
+		pos[1] = float( info[1] );
+		radius = float( info[2] );
[…]

### 2014-08-15 topology/alphashape.py
Dual Shape Finished

@@ -1,24 +1,74 @@
 
-import sys, os, math;
+import sys, os, copy, math;
 import pygame;
 
 from triangulate import *;
 from geometry import *
-
+from graph import *
 
 
 class HypergraphNode:
 	def __init__(self):
 		self.triangles = [];
-		self.nodes     = [];
+		self.nodes     = [];    ## Spheres 
 
 	def addTriangle(self, triangle):
 		if triangle not in self.triangles:
 			self.triangles.append( triangle );
 
 	def addNode(self, node):
+		'''node must be a sphere'''
 		if node not in self.nodes:
 			self.nodes.append( node );
+
+	def getNodes(self):
+		if len(self.nodes) > 0 and len(self.triangles) == 0:
+			return self.nodes;
+		for tri in self.triangles:
+			spheres = tri.spheres;
+			for sphere in spheres:
+				if sphere not in self.nodes:
+					self.nodes.append( sphere );
+		return self.nodes;
+
+	def share_node_with(self, other):
+		self_nodes = self.getNodes();
+		for node in self_nodes:
+			if node in other.getNodes():
+				return True;
+		return False;
+
+	def copy(self):
+		newNode = HypergraphNode();
+		if len(self.triangles) == 0:
+			for node in self.nodes:
+				newNode.addNode( node );
+		for tri in self.triangles:
+			newNode.addTriangle(tri);
+		return newNode;
+
+
+	def merege_with( self, other ):
+		if self == other:
+			return None;
+		if self.share_node_with(other):
+			self_copy = self.copy();
+			for tri in other.triangles:
+				self_copy.addTriangle( tri );
+			return self_copy;
+		return None;
+
+	def has_edge( self, other, edges ):
+		self_balls  = self.getNodes();
+		other_balls = other.getNodes();
+		for ball in self_balls:
+			for other_ball in other_balls:
+				for edge in edges:
+					if (edge[0] == ball and edge[1] == other_ball) or (edge[1] == ball and edge[0] == other_ball):
+						return True;
+
+		return False; 
+
 
 def isEdgeValid( edge ):
 	'''edge = (ball1, ball2, weight)'''
[…]

### 2014-08-15 topology/graph.py

@@ -284,7 +284,7 @@ class Graph:
 		linkStr = "";
 		nodes = self.graphdict.keys();
 		for node in nodes:
-			nodeStr += "\t\t{\"name\":\"" + node.name + "\", \"group\":"+ str(node.group) +"},\n";
+			nodeStr += "\t\t{\"name\":\"" + str(node.name) + "\", \"group\":"+ str(node.group) +"},\n";
 			for edge in self.graphdict[node]:
 				linkStr += "\t\t{\"source\":"+ str(nodes.index(node)) +",\"target\":" + str(nodes.index(edge[0])) + ",\"value\":"+ str(edge[1]) +"},\n";
 
@@ -425,7 +425,7 @@ class GraphBreaker(object):
 		return new_graph;	
 
 
-
+'''
 graph = Graph();
 matrix = [ [0,1,0,1,1,0],
 		   [1,0,1,0,0,1],
@@ -457,3 +457,4 @@ graph.saveJson('./graph_drawing/data/graph2.json');
 graphBreaker = GraphBreaker(graph);
 breaked_graph = graphBreaker.break_it();
 breaked_graph.saveJson('./graph_drawing/data/broken_graph.json');
+'''

### 2014-08-15 Writing/Final/article.tex
Writing update

@@
 \section{Related Work}\label{related work}
-In this section, we first discuss the basics of sampling-based motion planning and the method of sampling on medial axis.
+
+\indent\indent In this section, we first discuss the basics of sampling-based motion planning and the method of sampling on medial axis.
 With the information of positions and their clearance in c-space, we have samples as spheres.
@@
 
-\begin{description}
-\item[A] \emph{Sampling-based Motion Planning} \hfill \\
+\paragraph{A} \emph{Sampling-based Motion Planning} \hfill \\
+\indent A robot is a movable object whose state can be described by $n$ parameters, or \emph{degrees of freedom} ($DOFs$).
+A point $<x_1, x_2, ..., x_n>$ in a n-dimensional space uniquely defines the configuration of a robot.
+Such space is called \emph{"Configuration Space"} or \emph{"C-space"}  ($C$).
+The subset of all feasible configurations is called the \emph{free space} (\emph{$C_{free}$}), while $C_{obst} = C \setminus C_{free}$ is the union of all infeasible configurations.
+\cite{UMAPRM} Path planning will generally be viewed as a search in a metric space $X$ for a continuous path from an initial state $x_{init}$ to a goal region $X_{goal} \subset X$.
+For a standard problem, $X = C$.
+\cite{RRT}
 
-\item[B] \emph{Medial Axis Sampling} \hfill \\
+\indent Sampling-based algorithms have been very successful and have seen many applications in industry for planning in high dimension space.
+Probablistic Roadmap \cite{PRM} and Rapidly-Exploring Random Tree \cite{RRT} are two outstanding methods.
+The basic idea under these methods is to randomly sample feasible configurations in $C-space$ and connect nearby valid samples as edges to construct a graph or tree structure, which careless about the dimension problem.
+By connecting start and goal configurations to the roadmap, a graph search, e.g., A*, can be performed to extract a near optimal solution path.
 
-\item[C] \emph{Dual Shapes of Unions of Balls} \hfill\\
+\paragraph{B} \emph{Medial Axis Sampling} \hfill \\
 
-\item[D] \emph{Betti Numbers} \hfill \\
+\paragraph{C} \emph{Dual Shapes of Unions of Balls} \hfill\\
 
-\item[E] \emph{Homotopy Class} \hfill \\
+\paragraph{D} \emph{Betti Numbers} \hfill \\
 
-\end{description}
+\paragraph{E} \emph{Homotopy Class} \hfill \\
 
@@
 
-Traditionally, sampling based algorithms will build a graph for configuration space.
+\indent \indent Traditionally, sampling based algorithms will build a graph for configuration space.
 These kind of graphs is proved to be able to find near optimal path, but can hardly be used to analysis the topology of paths.
-We want to to build a stronger represent of c-space that is both able to cover optimal path and study the topology structure of c-space.
+We want to to build a stronger represent of c-space that is both able to cover optimal path and study the topological structure of c-space.
 In this section, we are trying to answer the question of "are two paths in the same homotopy class".
@@
 \bibliographystyle{abbrv}
-\bibliography{main}
+\begin{thebibliography}{1}
+
+  \bibitem{UMAPRM} Yeh, Hsin-Yi Cindy, et al. "UMAPRM: Uniformly Sampling the Medial Axis."
+  \bibitem{RRT} LaValle, Steven M. "Rapidly-Exploring Random Trees A New Tool for Path Planning." (1998).
+  \bibitem{PRM} L.
+E.
+Kavraki, P.
+Svestka, L.
+E.
+K.
+P.
+Vestka, J.
+claude Latombe, and M.
+H.
+Overmars, “Probabilistic roadmaps for path planning in high-dimensional configuration spaces,” IEEE Trans.
+Robot.
+Autom., vol.
+12, pp.
+566–580, 1996.
+
+\end{thebibliography}
 

### 2014-08-16 Writing/Final/article.tex
writing update

@@
         Dartmouth College\\
-        Hanover, New Hampshire 03755, \underline{US}
+        Hanover, New Hampshire 03755, US
         \and
@@
         Dartmouth College\\
-        Hanover, New Hampshire 03755, \underline{US}
+        Hanover, New Hampshire 03755, US
 }
@@
 \documentclass[11pt]{article}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{graphicx}
+\DeclareGraphicsExtensions{.pdf,.png,.jpg, .gif}
+\usepackage{algpseudocode}
+
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{definition}[theorem]{Definition}
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%	Introducing Related Work
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Related Work}\label{related work}
@@
 Some works on graph theory and topology will finally be introduced.
+
+%====================================
+% Sampling Based Motion Planning
+%====================================
 
@@
 For a standard problem, $X = C$.
-\cite{RRT}
+\cite{RRT} What needs to be pointed out is that \emph{C-space} is very different from workspace which is usually formed by polygons.
+The shape of \emph{C-space} is usually unknown to us, unless the robot is a point.
 
@@
 Probablistic Roadmap \cite{PRM} and Rapidly-Exploring Random Tree \cite{RRT} are two outstanding methods.
-The basic idea under these methods is to randomly sample feasible configurations in $C-space$ and connect nearby valid samples as edges to construct a graph or tree structure, which careless about the dimension problem.
+The basic idea under these methods is to randomly sample feasible configurations in \emph{C-space} and connect nearby valid samples as edges to construct a graph or tree structure, which careless about the dimension problem.
 By connecting start and goal configurations to the roadmap, a graph search, e.g., A*, can be performed to extract a near optimal solution path.
 
+\indent One disadvantage of these methods is that we can't study the topological structure of C-space using only the data structures constructed.
+
+%====================================
+% Sampling on medial axis
+%====================================
 \paragraph{B} \emph{Medial Axis Sampling} \hfill \\
+\indent A simpler method that maintains the topology of \emph{C-space} but doesn't cover near optimal path is medial axis sampling.
+Medial Axis is also called Generallized Voronoi Diagram.
+The medial axis $MA(F)$ of free space $F$ is a strong deformation retract of $F$, which means $F$ can be continuously deformed onto $MA(F)$ while maintaining its topological structure.
+However, medial axis is hard to compute explicitly.
+
+\indent In Figure \cite{Book}, sec.
+5.6.3, Steven LaValle defined Medial Axis as "Let $(X, \rho)$ be a metric space.
+Let a \emph(maximal ball) be a ball $B(x,r) \subseteq X$ such that no other ball can be a proper subset the centers of all maximal balls trace out a one-dimensional set of points referred to as the \emph{medial axis}".
+
+\indent Mapping a pair of points $A$ and $B$ in free space onto $MA(F)$, there is a path between $A$ and $B$ if and only if there is a path between their images on $MA(F)$.
+Such path has a very nice property of the largest clearance from obstacles.
+
+\indent Steven A.
+Wilmart \cite{MAPRM} sampled on the medial axis of free space to build up a probabilistic roadmap planner.
+He also showed that "it is possible to efficiently retract a configuration, free or otherwise, onto the medial axis of the free space without having to compute the medial axis explicitly".
+
+\indent The basic idea of the algorithm proposed in \cite{MAPRM} is: given a point $A$ and its nearest point on the boundary of obstacles $A'$, a ray start from $A$ with direction $\overrightarrow{A'A}$ will always intersect with $MA(F)$.
+
+\indent This method results in sampling more nodes in narrow corridors, which is beneficial for improving performance on problems requiring traversal of such corridors.
+
+\indent However, such property makes the sampling method biased heavily towards certain portions of the medial axis.
+These biased property tend to ignore more critical parts of the space: large open free space.
+Sampling uniformly on the medial axis is sometimes more helpful.
+
+\indent Hsin-Yi (Cindy) Yeh \cite{UMAPRM} solved this problem by putting some random "sticks" with random directions in free space.
+Any surfaces will intersect uniformly with these sticks, thus searching on sticks to find points that intersect with medial axis will give nodes uniformly distributed on the medial axis.
+
+\indent Figure \ref{fig:Medial Axis} visualizes the shape of medial axis of a rectangle.
+
+\begin{figure}
+	\center{\includegraphics[scale=0.35]{./pics/MA.png}}
+	\caption{\label{fig:Medial Axis} Sampling on the Medial Axis of a rectangle space.\cite{Book}}
+\end{figure}
+
+%====================================
+% Dual shapes of unions of balls
+%====================================
 
 \paragraph{C} \emph{Dual Shapes of Unions of Balls} \hfill\\
+\indent Approximating the shape of an unknown area to study its properties is a very commonly used method.
+We have seen many such ideas in the study of biogeometry.
+As for robotics, a few people began to notice the achievements from biogeometry study and tried to apply similar methods to study the shape of \emph{C-space}.
 
+\indent Zoe McCarthy \cite{PathNonexistance} used samples generated by PRM to form the $\alpha$-shape of \emph{C-space}.
+She then proved there doesn't exist a path between a pair of configurations by proving they are in two different disconnected components of the shape.
+She declared it was the first time $\alpha$-shape is being used in motion planning.
+
+\indent Define a \emph{simplicial complex} $D$: a collection of simplices such that if $\bigtriangleup_T \subseteq D$ ( $\bigtriangleup_T$ is the convex hull of $T$ ), then if $U \subseteq T$, we have $\bigtriangleup_U \subseteq D$ and also that the intersection of two simplices in $D$ is either empty or another simplex in $D$.
+The $\alpha$-shape of a set of points $S$ is a generalization of the convex hull of those points.
+\cite{PathNonexistance}.
+H.
+Edelsbrunner first introduced them in \cite{PointSetShape}.
+By choosing different value of the one parameter $\alpha$, we can have a family of shapes with the same set of points.
+An example of $\alpha$-shape is in Figure \ref{fig:Alpha-shape}.
+
+\indent Choosing the best $\alpha$ value could be a bothering work.
+Assuming weighted points in the point set, by using a generalization of the Delaunay Triangulation, the Regular Triangulation, we can construct another shape using weights as flexible $\alpha$'s.
+Points with weights can be considered as balls.
+H.
+Edelsbrunner gave us this idea in \cite{DualShape}.
+Such shapes are also called Dual Shapes or Dual complex of unions of balls.
+The weighted $\alpha$-shape captures the topology of the union of balls with different radii.
+Figure \ref{fig:Dual Shape} shows an example of such weighted $\alpha$-shape.
+
+\begin{figure}
+	\center{\includegraphics[scale=0.7]{./pics/alphaShape.png}}
+	\caption{\label{fig:Alpha-shape} An example of $\alpha$-shape. \cite{PointSetShape}}
+\end{figure}
+
+\begin{figure}
+	\center{\includegraphics[scale=0.30]{./pics/dualshape.png}}
+	\caption{\label{fig:Dual Shape} An example of weighted $\alpha$-shape for a union of balls. \cite{DualShape}}
+\end{figure}
+
+%====================================
+% Betti Numbers
+%====================================
 \paragraph{D} \emph{Betti Numbers} \hfill \\
+\indent In algebraic topology, the Betti Numbers are used to distinguish topological spaces based on the connectivity of n-dimensional simplicial complexes.
+Informally, the \emph{n-th} Betti number ($\beta_n$) represents the rank of the \emph{n-th} homology group, which tells us the maximum number of cuts that can be mad before diving a surface into two pieces.
+\cite{betti wiki}
 
-\paragraph{E} \emph{Homotopy Class} \hfill \\
+\indent An example of Betti numbers will be a torus. Figure \ref{fig:Torus}
+
+\indent H. Edelsbrunner introduced a way to compute $n-th$ Betti number in \cite{Edel Book}, where he uses gaussian ellimination to compute the betti numbers with adjacency matrix.
+
+\indent Vanessa Robins \cite{alpha betti} provided more detailed explains and proofs on computing betti numbers. What's more, she put more thoughts on computing betti numbers for alpha shapes.
+
+\begin{figure}
+	\center{\includegraphics[scale=0.26]{./pics/Torus.png}}
+	\caption{\label{fig:Torus} The torus has one connected component($\beta_0$), two circular holes ($\beta_1$,the one in the center and the one in the middle of the "donut"), and one two-dimensional void ($\beta_2$, the inside of the "donut").\cite{betti wiki}}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%	Introducing Our Algorithm
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \indent \indent Traditionally, sampling based algorithms will build a graph for configuration space.
-These kind of graphs is proved to be able to find near optimal path, but can hardly be used to analysis the topology of paths.
-We want to to build a stronger represent of c-space that is both able to cover optimal path and study the topological structure of c-space.
-In this section, we are trying to answer the question of "are two paths in the same homotopy class".
-We will first give the outline of our algorithm, and introduce each phase step by step.
+These kind of graphs are proved to be able to find near optimal path, but can hardly be used to analysis the topology of paths.
+We want to to build a stronger representation of c-space that is both able to cover optimal path and study the topological structure of c-space.
+In this section, we are trying to solve the problem in 2D and answer the question "Is two paths in the same homotopy class" as a start point of using our method to study the topology of \emph{C-space}.
+We will first give the outline of the algorithm, and explain each step in detail.
 
-\begin{description}
+\paragraph{A} \emph{The Algorithm outline} \hfill \\
+\indent Before starting introducing our algorithm, we firstly clarify some preliminary tools we can have:
 
-\item[A] \emph{The Algorithm} \hfill \\
+%%%%%%%%%%%%%%%%================================================>>>>>>>>>>>>>>>>>>>>>>>>>>>>>>
+%%%%%%  We need to name our algorithm
+%%%%%%  Seriously
+%---------------------------------------------------------------------------------------------
+\begin{figure}
+  \begin{algorithmic}[1]
+  \Function{OurAlgorithm}{\emph{C-space}}
+    \State $pntset \gets$ randomly generated points in free space.
+    \State $maSamples \gets$ Empty Set.
+    \State $l \gets $ stick length.	 
+	\For{$point \in pntset$}
+		\State $dir \gets$ random direction  
+		\State $stick \gets$ ( point, l, dir ) \Comment{start point+length+direction=a stick}
+		\If{ $stick$ intersects with the medial axis }
 
-\item[B] \emph{Sampling in C-Space} \hfill \\
+			\indent\indent $sample \gets$ stick.search()
 
-\item[C] \emph{Constructing Hypergraph of C-Space} \hfill \\
+			\indent\indent $radius \gets$ clearance( sample ) \Comment{get the clearance at this point}
 
-\item[D] \emph{Breaking A Graph into Loop-free Parts} \hfill\\
+			\indent\indent $maSamples.append( ball(sample, radius) )$
+		\EndIf
+	\EndFor
 
-\item[E] \emph{Determine Paths Homotopy Class} \hfill \\
+	\Return $maSamples$;
+  \EndFunction
+  \end{algorithmic}
+  \caption{Algorithm Outline}
+\end{figure}
 
-\end{description}
+\paragraph{B} \emph{Sampling in C-space} \hfill \\
+
+\paragraph{C} \emph{Constructing Topology Roadmap of C-space} \hfill \\
+
+\paragraph{D} \emph{Breaking A Graph into Loop-free Parts} \hfill\\
+
+\paragraph{E} \emph{Determine Paths Homotopy Class} \hfill \\
+
+\section{Good Properties}\label{properties}
 
@@
 
+  \bibitem{Book} Steven M. LaValle, "Planning Algorithms", Cambridge University Press, ISBN 0-521-86205-1, 2006.
   \bibitem{UMAPRM} Yeh, Hsin-Yi Cindy, et al. "UMAPRM: Uniformly Sampling the Medial Axis."
@@
 566–580, 1996.
-
+  \bibitem{MAPRM} Wilmarth, Steven A., Nancy M.
+Amato, and Peter F.
+Stiller.
+"MAPRM: A probabilistic roadmap planner with sampling on the medial axis of the free space." Robotics and Automation, 1999.
+Proceedings.
+1999 IEEE International Conference on.
+Vol.
+2.
+IEEE, 1999.
+  \bibitem{DualShape} Edelsbrunner, Herbert. "The union of balls and its dual shape." Proceedings of the ninth annual symposium on Computational geometry. ACM, 1993.
+  \bibitem{PointSetShape} Edelsbrunner, Herbert; Kirkpatrick, David G.; Seidel, Raimund (1983), "On the shape of a set of points in the plane", IEEE Transactions on Information Theory 29 (4): 551–559, doi:10.1109/TIT.1983.1056714.
+  \bibitem{PathNonexistance} Z.
+McCarthy.
+Bretl, and S.
+Hutchinson, "Proving path non-existence using sampling and alpha shapes," in IEEE International Conference on Robotics and Automation (ICRA), May 2012.
+  \bibitem{betti wiki} "Betti Number", From Wikipedia -- The Free Encyclopedia. ( $http://en.wikipedia.org/wiki/Betti_number$ )    
+  \bibitem{Edel Book}Edelsbrunner, Herbert, and John Harer. "Computational topology: an introduction." American Mathematical Soc., 2010. page. 88 - 93.
+  \bibitem{alpha betti} Robins, Vanessa. "Computational topology for point data: Betti numbers of α-shapes." Morphology of Condensed Matter. Springer Berlin Heidelberg, 2002. 261-274.
 \end{thebibliography}

### 2014-08-16 Writing/Final/article.tex
writing update

@@
 \paragraph{A} \emph{The Algorithm outline} \hfill \\
-\indent Before starting introducing our algorithm, we firstly clarify some preliminary tools we can have:
+\indent Before starting introducing our algorithm, we firstly clarify some preliminary tools we can have: We are sampling in $(X, \rho)$ metric space.
+Let $x$ be a configuration in $X$(usually \emph{C-space}), $\rho(x)$ gives the clearance of configuration $x$.
+By \emph{"clearance"}, we mean its (estimated) distance to the nearest obstacles.
+Ball $B(x, \rho(x))$ is referred as a $"sample"$ in the rest of the section.
+We make no assumption of the shape of obstacles regions in \emph{C-space}.
+
+\indent The algorithm is shown in Figure \ref{fig:Algo}.
+It has four phases.
+The first phase is to generate some random configurations in \emph{C-space}, like all other sampling-based planning algorithms do, and keep only those feasible ones.
+Every feasible configuration will be kept until the third phase.
+($randomConfig$ keep unchanged.) In the second phase, we will sample balls centered on medial axis first and then try to cover the left area of $C_{free}$.
+Samples on the medial axis $MA(C_{free})$ will be used in phase three to construct the dual shape that captures the topology of $C_{free}$.
+After simplifying the dual shape, we will have a roadmap while maintaining the topological structure.
+Phase four break the topology roadmap into pieces such that no two piece can be merged without forming a loop.
+
+\indent We will now explain each phase in detail.
 
@@
   \begin{algorithmic}[1]
-  \Function{OurAlgorithm}{\emph{C-space}}
-    \State $pntset \gets$ randomly generated points in free space.
-    \State $maSamples \gets$ Empty Set.
-    \State $l \gets $ stick length.	 
-	\For{$point \in pntset$}
-		\State $dir \gets$ random direction  
-		\State $stick \gets$ ( point, l, dir ) \Comment{start point+length+direction=a stick}
-		\If{ $stick$ intersects with the medial axis }
+  \Function{WeNeedAGoodName}{\emph{C-space}}
 
-			\indent\indent $sample \gets$ stick.search()
+    \indent \State $randomConfigs \gets SampleRandomConfigurations( \emph{C-space}, number )$
 
-			\indent\indent $radius \gets$ clearance( sample ) \Comment{get the clearance at this point}
+    \indent \State $maSamples \gets SampleOnMedialAxis( randomConfigs )$
+    \indent \State $regSamples \gets SampleLeftArea(maSamples, randomConfigs)$
 
-			\indent\indent $maSamples.append( ball(sample, radius) )$
-		\EndIf
-	\EndFor
+    \indent \State $dualShape \gets WeightedAlphaShape( maSmaples )$
+    \indent \State $topologyRoadmap \gets Retract(dualShape)$
 
-	\Return $maSamples$;
+    \indent \State $brokenRoads \gets BreakGraph( topologyRoadmap )$
+
+    \indent
+
   \EndFunction
   \end{algorithmic}
-  \caption{Algorithm Outline}
+  \caption{\label{fig:Algo} Algorithm Outline}
 \end{figure}
@@
 \paragraph{B} \emph{Sampling in C-space} \hfill \\
+\indent As pointed out in Figure \ref{fig:Algo}, this phase has two parts: Sampling on medial axis, and sampling the rest of free space.
+
+\indent Sampling on medial axis is well studied in \cite{MAPRM} and \cite{UMAPRM}.
+Besides the positions of configurations, we also keep the clearance of each configuration, thus have some balls, or samples.
+We also require that no new ball, when sampling, is allowed to be centered inside any existing one.
+For details of the algorithms, please refer to these two papers.
+One thing worth our notice is that using only algorithm mentioned in \cite{MAPRM}, we can get good result in narrow corridor but are more likely to ignore large open area.
+While using only \cite{UMAPRM} method, we can cover large open area well, but more likely to produce disconnected balls in narrow corridor.
+Therefore, running both algorithm is highly recommended.
 

### 2014-08-18 Writing/Final/article.tex
writing update

@@
-\title{ Determine Paths in the Same Homotopy Class }
+\title{ Unions of Balls and Configuration Space }
 \author{
@@
 \begin{abstract}
-Describing the  \ldots
+Covering both the configuration space and represent the right topology is hard to achieve at the same time with traditional sampling-based motion planning algorithms, such as Probabilistic Roadmap and Rapidly-Exploring Random Tree.
+In this paper, we proposed a method that is able to cover near optimal path and study the shape and topology of configuration space.
 \end{abstract}
@@
 
+\indent The first betti number of a graph is very easy to compute. Given a graph $G$, with $n$ vertices, $m$ edges and $k$ components. It's 1st betti number is:
+
+$\beta_1 = m - n + k$
+
+\indent This can be proved straightforwardly by mathematical induction on the number of edges.
+A new edge either increments the number of 1-cycles or decrements the number of connected components.
+\cite{betti wiki}
+
 \indent H. Edelsbrunner introduced a way to compute $n-th$ Betti number in \cite{Edel Book}, where he uses gaussian ellimination to compute the betti numbers with adjacency matrix.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%	Introducing Our Algorithm
+%	Introduction to Our Algorithm
 %
@@
 
+%====================================
+% Algorithm outline
+%====================================
 \paragraph{A} \emph{The Algorithm outline} \hfill \\
@@
 
+    // Phase One
     \indent \State $randomConfigs \gets SampleRandomConfigurations( \emph{C-space}, number )$
 
+    // Phase Two
     \indent \State $maSamples \gets SampleOnMedialAxis( randomConfigs )$
@@
 
-    \indent \State $dualShape \gets WeightedAlphaShape( maSmaples )$
+    // Phase Three
+    \indent \State $dualShape \gets WeightedAlphaShape( some smaples )$
     \indent \State $topologyRoadmap \gets Retract(dualShape)$
 
+    // Phase Four
     \indent \State $brokenRoads \gets BreakGraph( topologyRoadmap )$
@@
 
+%====================================
+% Covering c-space
+%====================================
 \paragraph{B} \emph{Sampling in C-space} \hfill \\
@@
 
+\indent The reason we sample on medial axis first is that 1.
+these balls are maximal ones as the definition of medial axis suggests, and 2.
+medial axis $MA(C_{free})$ is a SDR of \emph{C-space}.
+\cite{MAPRM2}
+
+\indent Figure \ref{SampleLeftArea} describes how we sample area not yet covered by balls centered on medial axis.
+The basic idea behind the algorithm is to keep sampling new balls on the boundary of existing ones by "pushing" random configurations inside existing balls to the boundary of them and determine if they are in any other balls.
+We restrict that all balls to be larger than a minimal radius ball, thus void getting a lot of very small samples.
+
+\indent Getting configurations inside a ball doesn't have to be $O(n)$ costly.
+It can be done using KNN algorithm, which is more efficient than iterating everything.
+Since we generated random configuration $n$ times, not all are feasible, in a 2D space with area $A$.
+We expect to have $n/A$ configurations in an unit area.
+A ball with radius $r$ has area $\pi r^2$, approximately $k = \frac{n \pi r^2}{A}$ configurations are inside the ball.
+We then project these (uniformly distributed) configurations to the boundary of the ball.
+Actually, choosing a larger $k$ could be better: we virtually extend the radius of our discs, which results in a smaller density in arcs that are very close to obstacles than those far from obstacles.
+Samples got in this part is called \emph{regular samples}.
+
+\indent Figure \ref{Samples} is a result of this phase running in a rectangle world with 3 obstacles in the middle.
+Gray balls are centered on medial axis, while green ones are not.
+Red points are centers.
+
+\begin{figure}
+\begin{algorithmic}[1] 
+  \Function{SampleLeftArea}{ maSamples, randomConfigs }
+  	\State $regSamples \gets EmptySet$ \Comment{Set of balls not on MA}
+  	\State $newBall \gets$ True	\Comment{If we can get new balls}
+  	\State $lastRoundBalls \gets maSamples$
+  	\While{$newBall$}
+  		\State $newBall \gets False$
+		\State $bndConfigs \gets EmptySet$ \Comment{A set of ball boundary configs}  		
+  		\For {$ball \in lastRoundBalls$}
+  			\State $innerConfigs \gets KNearest(ball, randomConfigs)$; \Comment{KNN}
+  			\State $bndConfigs.append( getBoundaryConfigs(ball, innerConfigs) )$
+  		\EndFor
+  		\State $lastRoundBalls \gets EmptySet$
+  		\For{$config \in bndConfigs$}
+  			\If{$config$ not inside any existing ball} \Comment{ $O(n^2)$ time}
+  				\State $ball \gets getNewBall(config)$ \Comment{get a new ball}
+  				\If{$ball.radius \geq min\_radius$}
+  					\State $newBall \gets True$
+  					\State $lastRoundBalls.append( ball )$
+  					\State $regSamples.append(ball);$
+  				\EndIf
+  			\EndIf
+  		\EndFor
+  	\EndWhile
+  	\State \Return $regSamples$
+  \EndFunction
+  \end{algorithmic}
+  \caption{\label{SampleLeftArea} Algorithm to sample left free area}
+\end{figure}
+
+\begin{figure}
+	\center{\includegraphics[scale=0.3]{./pics/Samples.PNG}}
+	\caption{\label{Samples} Samples got by the algorithm}
+\end{figure}
+
+%====================================
+% Dual shape and topology roadmap
+%====================================
+
 \paragraph{C} \emph{Constructing Topology Roadmap of C-space} \hfill \\
+\indent After getting these samples, we can now start to build a structure that captures the topology of the space.
 
+\indent This phase, like the previous one, has two parts: 1. Construct the dual shape of medial axis samples got from phase one. 2. Simplify the dual shape to a simple graph.
+
+\indent In the first part, constructing the dual shape using only the medial axis sample could break the topology of medial axis.
+The reason is shown in Figure \ref{badthing}: three balls are all centered on medial axis, but their dual shape will be an empty triangle, which introduces a "hole" in that area.
+To solve this problem we can try to sample a ball centered at the the radical center after getting an empty triangle, and rebuild the dual shape for these four balls.
+\cite{radical center} Proving the solution is very simple: if there is no obstacles in that area, the newly sampled ball will cover the space, if there is obstacle, the ball will either not be sampled or not connect three of the balls.
+
+\indent With these balls, we then compute their dual shape, which is formed by some 1-simplices and 2-simplices in 2D.
+The runtime of computing dual shape will be $O(n^2)$ which is the worst case when doing regular triangulation of weighted points.
+Although using all balls will avoid problem as in Figure \ref{badthing}, we are making $n$ much larger, which results in a bad runtime of this step.
+
+\indent One might argue that we can simply get configurations on medial and connect them as a roadmap.
+However, this roadmap doesn't maintain the topology of \emph{C-space}.
+At some corners, we will still get triangles which don't have information if there are obstacles inside the triangle.
+By building the dual shape, this will no longer be a problem.
+
+\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, reconnect these retracted points with other ones using their previous connection.
+
+\begin{figure}
+	\center{\includegraphics[scale=1]{./pics/badthing.pdf}}
+	\caption{\label{badthing}} An example that medial axis samples break the topology structure of the medial axis.
+\end{figure}
+
+\begin{figure}
+	\center{\includegraphics[scale=0.3]{./pics/my_dualshape.PNG}}
+	\caption{\label{ourdualshape}} Dual shape of balls generated in phase 1 (centered on medial axis).
+\end{figure}
+
+\begin{figure}
+	\center{\includegraphics[scale=0.4]{./pics/simplified_graph.png}}
+	\caption{\label{simplifiedgraph}} Simplified graph of the dual shape in Figure \ref{ourdualshape}.
+\end{figure}
+
+%====================================
+% Break graph
+%====================================
 \paragraph{D} \emph{Breaking A Graph into Loop-free Parts} \hfill\\
+\indent After getting the topology roadmap, we technically already have a planner, but still we can simplify it.
+We now discuss breaking a graph into several components, such that no two components can merge into a new graph without forming a loop.
+By doing this, a graph is even simplified.
+Knowing which components are the start and goal configurations in, we can find a path connecting these components immediately.
+This technique can be a great improve when $C-space$ is very large and traditional \emph{PRM} or \emph{RRT} methods will take a long time to solve.
 
+\indent Let $g_1$ and $g_2$ be two graphs without loops. We say $g_1$ and $g_2$ to be mergeable if: 1. they share at least one common node, 2. the new graph formed by these two graph has no loop.
+
+\indent Determine if a simple graph has a loop is very easy using the first Betti number $\beta_1$ mentioned in section 2.
+
+\indent Figure \ref{breakgraph} shows our algorithm to break a graph.
+The idea behind this algorithm is to take every edges as an initial component, then iterate each component to find and merge with a mergeable component until there is no two mergeable components.
+
+\begin{figure}
+\begin{algorithmic}[1] 
+  \Function{BreakGraph}{ graph }
+  	\State $components \gets EmptySet$
+  	\For {$edge \in graph.edges$}
+  		\State components.append( new Graph(edge) )
+  	\EndFor
+
+  	\State \Return MergeComponents( components )
+  \EndFunction
+\end{algorithmic}
+
+\begin{algorithmic}[1]   
+  \Function{MergeComponents}{components}
+  	\State $pq \gets PriorityQueue()$
+    \For{$component \in components$}
+        \State $pq.push(component, component.size())$
+    \EndFor
+    \While{ $pq.size() > 1$ }
+    	\State $smallest\_component \gets pq.pop()$
+    	\State $mergeable\_component \gets$ \emph{find first mergeable component in pq}
+		\State $new\_component \gets smallest\_component.merge\_with( mergeable\_component )$
+    	\State $components.remove( smallest\_component )$
+    	\State $components.remove( mergeable\_component )$
+    	\State $pq.remove( mergeable\_component )$
+    	\State $components.append( new\_component )$
+    	\State $pq.push(new\_component, new\_component.size())$
+	\EndWhile
+
+    \State \Return $components$
+  \EndFunction  
+\end{algorithmic}
+	\caption{\label{breakgraph}} Breaking a graph into several loop-free components.
+\end{figure}
+
+\begin{figure}
+	{\includegraphics[scale=0.7]{./pics/initial.png}}
+	{\includegraphics[scale=0.7]{./pics/broken.png}}
+
+	{\includegraphics[scale=0.65]{./pics/initial2.png}}
+	{\includegraphics[scale=0.65]{./pics/broken2.png}}\
+	\caption{\label{brokengraphs} Some examples of breaking a graph. Graphs are visualized using $d3.js$ $(http://www.d3js.org)$ }
+\end{figure}
+
+%====================================
+% Path topology
+%====================================
 \paragraph{E} \emph{Determine Paths Homotopy Class} \hfill \\
+\indent A continuous function, or a map, $f: X \rightarrow Y$ is called a \emph{homotopy equivalence} if there is a map $g: X \rightarrow Y$ such that there exist a continuous function $H: X \times [0,1] \rightarrow Y$ with $H(x, 0) = f$ and $H(x,1) = g$.
 
+\indent Besides using those components to plan motions for a large \emph{C-space}, they can also be used to determine if two paths are in the same homotopy class.
+
+\indent Let $\sigma_1$ and $\sigma_2$ be two paths, with the same start and goal configuration, going through from components $g_1$ to $g_2$ via two nodes $A$ and $B$.
+$\sigma_1$ and $\sigma_2$ are homotopy equivalent if $A = B$.
+
+\indent Proof can be found in section 4.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%	Properties of Our Algorithm
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Good Properties}\label{properties}
 
-\section{Experiments}\label{experiments}
-We now describe the some experiments and their results.
+  \begin{theorem}
+  Let $S_{init}$ be the set of initial random configurations.
+With minimum radius of $r_{min}$, configurations with clearance larger than $r_{min}$ will be covered, when $|S_{init}| \rightarrow \infty$.
+  \end{theorem}
 
+  \paragraph{\emph{Proof:}} 
+  \indent When the number of initial random configurations approaches infinite, the boundaries of all existing balls are fully covered.
+So, every configuration not inside any existing balls will be samples as a ball, unless it's less than $r_{min}$ clearance.
+
+  \begin{theorem}
+  Let $B$ be the set of ball samples got in phase one. Then $|B|$ is finite.   
+  \end{theorem}
+  \paragraph{\emph{Proof:}} 
+  \indent We restrict balls to have no less than $r_{min}$ radius and new balls to be centered outside existing ones.
+Assume we partition the space into $r_{min} \cdot r_{min}$ cells in 2D.
+The number of cells is finite, if the space is finite.
+Putting balls with exactly $r_{min}$ radius in the centers of these cells will cover the space totally.
+The number of balls is finite.
+Phase one will generate balls no more than the number of balls generated in this way.
+Figure \ref{ourdualshape} shows the dual shape of balls generated by previous phase.
+
+  \begin{theorem}
+  Let $b \in B$ be an element of $B$, $A$ and $B$ are two configurations in \emph{C-space}.
+The optimal path $\sigma$ between $A$ and $B$ is in $\bigcup_{b\in B}$ if $\sigma$ has clearance no less than $r_min$.
+  \end{theorem}   
+  \paragraph{\emph{Proof}}
+  \indent This is a direct conclusion of previous theorem.
+
+  \begin{theorem}
+  Any path $\sigma$ can be continuously deformed into medial axis. 
+  \end{theorem}   
+  \paragraph{\emph{Proof}}
+  \indent This is the definition of Medial Axis $MA(C_{free})$ being a strong deformation retraction of $C_{free}$.
+
+  \begin{theorem}
+  Given path $\sigma_1$ and $\sigma_2$, we say they have the same homotopy type if their image in the topology roadmap is the same. 
+  \end{theorem}
+  \paragraph{\emph{Proof}}
+  \indent Let $x$ be a point in the space $X$, $B = \{ b_1, b_2, ..., b_n \}$ be the set of balls centered on medial axis. Define map $H(x)$:
+
+  $H(x) = b_i \indent, if \indent |x-b| < |x-b'|, b' \in B$
+
+  \indent This continuous function maps any point in the space to balls centered on medial axis. Dual shape maps any points in the balls to the topology roadmap we build.
+
+  \indent Therefore, if two paths have the same image in the topology roadmap. They have the same homotopy type.
+
+  \begin{theorem}
+  Let $g_1$ and $g_2$ be two loop-free graphs such that merging their common nodes will produce a new graph with loops, $\sigma_1$ and $\sigma_2$, with the same start and goal nodes, be two paths going from $g_1$ to $g_2$ via common nodes $A$ and $B$.
+$\sigma_1$ and $\sigma_2$ have different homotopy type if $A \neq B$
+  \end{theorem}
+  \paragraph{\emph{Proof}}
+  \indent Because $A$ and $B$ are two common nodes shared by $g_1$ and $g_2$, if $A \neq B$, merging $g_1$ and $g_2$ will create a graph with a loop going from $A \rightarrow B \rightarrow A$.
+Since $\sigma_1$ and $\sigma_2$ have the same start and goal nodes, merging them will also create a loop.
+So $\sigma_1$ and $\sigma_2$ have different homotopy type.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%	Experiments
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\section{Experiments}\label{experiments}
+%We now describe the some experiments and their results.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%	Conclusions and Future work
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions and Future Work}\label{conclusions}
@@
 IEEE, 1999.
+  \bibitem{MAPRM2} S.
+A.
+Wilmarth, N.
+M.
+Amato, and P.
+F.
+Stiller.
+MAPRM: A probabilistic roadmap planner with sampling on the medial axis of the free space.
+Technical Report TR98-022, Department of Computer Science, Texas A\&M University, College Station, TX, Nov.
+1998.
   \bibitem{DualShape} Edelsbrunner, Herbert. "The union of balls and its dual shape." Proceedings of the ninth annual symposium on Computational geometry. ACM, 1993.
   \bibitem{PointSetShape} Edelsbrunner, Herbert; Kirkpatrick, David G.; Seidel, Raimund (1983), "On the shape of a set of points in the plane", IEEE Transactions on Information Theory 29 (4): 551–559, doi:10.1109/TIT.1983.1056714.
+  \bibitem{radical center} "Radical Center", From Wolfram MathWorld -- the web's most extensive mathematics resource. ($http://mathworld.wolfram.com/RadicalCenter.html$)
   \bibitem{PathNonexistance} Z.

### 2014-08-18 UMAPRM.py

@@ -550,7 +550,6 @@ gameWorld.render( DISPLAYSURF );
 print "Start sampling"
 samples = sampler.sampleMAbk( 6000, DISPLAYSURF );
 sampler.save_data( samples, "./topology/balls.txt" )
-
 print "FINISHED!!!!"
 sys.exit();
 

### 2014-08-18 topology/triangulate.py

@@ -86,15 +86,21 @@ if __name__ == "__main__":
 	DISPLAYSURF.fill((255,255,255));
 	pygame.display.update();
 
+    
+	i = 0;
 	for sphere in spheres:
-		pygame.draw.circle( DISPLAYSURF, (200, 200, 200), (int(sphere[0]),int(sphere[1])), int(sphere[2]), 1 );
+		if i < 43:
+			pygame.draw.circle( DISPLAYSURF, (200, 200, 200), (int(sphere[0]),int(sphere[1])), int(sphere[2]), 2 );
+		else:
+			pygame.draw.circle( DISPLAYSURF, (0, 200, 0), (int(sphere[0]),int(sphere[1])), int(sphere[2]), 2 );
+		i += 1;
 
-	for tri in triangles:
-		tri.render( DISPLAYSURF );
+	#for tri in triangles:
+	#	tri.render( DISPLAYSURF );
 
 
 	for point in points:
 		pygame.draw.circle( DISPLAYSURF, (255, 0, 0), (int(point[0]),int(point[1])), 3 );
 
-	pygame.image.save( DISPLAYSURF, "Triangluation.PNG" );
+	pygame.image.save( DISPLAYSURF, "Samples.PNG" );
 

### 2014-08-18 Writing/Final/article.tex
writing update

@@
 \begin{abstract}
-Covering both the configuration space and represent the right topology is hard to achieve at the same time with traditional sampling-based motion planning algorithms, such as Probabilistic Roadmap and Rapidly-Exploring Random Tree.
+Covering both the configuration space, or \emph{C-space}, and represent the right topology is hard to achieve at the same time with traditional sampling-based motion planning algorithms, such as Probabilistic Roadmap and Rapidly-Exploring Random Tree.
 In this paper, we proposed a method that is able to cover near optimal path and study the shape and topology of configuration space.
+Our method samples a serious of balls to cover the space and use the dual shape of the union of balls to re-construct space.
+We analysis the coverage of the space and show how these balls and their dual shape can be used to generate a graph that maintains the topology of \emph{C-space}
 \end{abstract}
@@
 \section{Introduction}
-This is time for all good men to come to the aid of their party!
+\indent\indent Planning a collision-free motion for movable object could be very challenge, especially in high dimensional space, because of the lack of knowledge to understand the shape and top of configuration space.
+Meanwhile, motion planning has extensive applicationsto areas like augmented reality \cite{aug}, computer-aided design \cite{design} and bioinformatics \cite{bioinformatics}.
+More knowledge on \emph{C-space} will be benefit to these research.
+
+\indent Although we have seen some study in low dimensional space trying to characterize the topology of \emph{C-space} \cite{ConCompNum} \cite{interval}, these methods suffer dimension curse in high dimension space.
+
+\indent Sampling-based method for motion planning appear to be very successful \cite{Book}.
+These methods are usually proved to be \emph{probabilistically complete}, thus guarantee to find a path if it exists.
+Medial Axis sampling \cite{MAPRM} \cite{UMAPRM} attracted researchers attention for their property of characterizing the topology of \emph{C-space} and safe clearance to obstacles, however, no structures are made of these samples to properly represent the space.
+
+\indent Trying to answer the question "does a collision free path exist", Zoe McCarthy uses samples to build an $\alpha$-shape to better understand samples and space captured, which inspires us to explore more with $\alpha$-shape.
+
+\indent Approximating the "shape" of a given point set in a space is a frequently occurred question in many research areas, which is the intuitive of $\alpha$-shape.
+A relative notion is space-filling diagram which is used in chemistry and biology to represent molecular structures.
+\cite{alpha intro}.
+
+\indent In this paper, we will firstly introduce sampling algorithms to cover the \emph{C-space}, medial axis sampling methods are applied to reduce the number of samples and capture the topology of the space.
+We then use these samples, or balls, to construct the weighted $\alpha$-shape.
+After simplifying the $\alpha$-shape, we will still have a simple graph, which can be used for both motion planning and topology study.
+We at each step, we will demonstrate algorithm results of a 2D configuration space.
+Some properties of our algorithm are discussed in section 4.
 
@@
 As for robotics, a few people began to notice the achievements from biogeometry study and tried to apply similar methods to study the shape of \emph{C-space}.
+\cite{alpha intro}
 
@@
 Although using all balls will avoid problem as in Figure \ref{badthing}, we are making $n$ much larger, which results in a bad runtime of this step.
+(However, constructing the dual shape of all balls will be helpful to study the shape of \emph{C-space})
 
@@
 \section{Conclusions and Future Work}\label{conclusions}
-We worked hard, and achieved very little.
+\indent\indent The results demonstrated with our algorithm are sound for covering the \emph{C-space} and represent the topology.
+
+\indent However, we don't know what kind of issues there will be when implementing for high dimensional space.
+The time cost for constructing weighted $\alpha$-shape( dual shape ) of unions of balls is a concern.
+Because we need to check each \emph{k-simplex} while $k = 1, 2, 3, ..., d$, $d$ being the dimensions.
+So, our next goal is to implement the algorithm for 3D case, and then higher dimensions.
+
+\indent Our next direction is to study the properties and applications of weighted $\alpha$-shape, especially applications in bioinformatics and chemistry, then extend to high dimensions.
+
+\indent Another direction will be studying the topology using the topology roadmap we constructed. Its value is underestimated in this paper, and I believe we can find more there.
 
@@
 \begin{thebibliography}{1}
-
+  \bibitem{aug} J.-M. Lien, O. B. Bayazit, R.-T. Sowell, S. Rodriguez, and N. M. Amato. Shepherding behaviors. In Proc. IEEE Int. Conf. Robot.Autom. (ICRA), pages 4159–4164, April 2004.
+  \bibitem{design} O. B. Bayazit, G. Song, and N. M. Amato. Enhancing randomized motion planners: Exploring with haptic hints. In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pages 529–536, 2000.
+  \bibitem{bioinformatics} A.
+P.
+Singh, J.-C.
+Latombe, and D.
+L.
+Brutlag.
+A motion planning approach to flexible ligand binding.
+In Int.
+Conf.
+on Intelligent Systems for Molecular Biology (ISMB), pages 252–261, 1999.
+  \bibitem{ConCompNum} Delanoue, N.; Jaulin, L.; Cottenceau, B.
+(2006).
+"Counting the Number of Connected Components of a Set and Its Application to Robotics".
+Applied Parallel Computing, Lecture Notes in Computer Science 3732 (1).
+  \bibitem{interval} Jaulin, L. (2001). "Path planning using intervals and graphs". Reliable Computing 7 (1).  
   \bibitem{Book} Steven M. LaValle, "Planning Algorithms", Cambridge University Press, ISBN 0-521-86205-1, 2006.
@@
   \bibitem{DualShape} Edelsbrunner, Herbert. "The union of balls and its dual shape." Proceedings of the ninth annual symposium on Computational geometry. ACM, 1993.
+  \bibitem{alpha intro} "Alpha Shape Introduction", Duck University, ($http://biogeometry.duke.edu/software/alphashapes/$)
   \bibitem{PointSetShape} Edelsbrunner, Herbert; Kirkpatrick, David G.; Seidel, Raimund (1983), "On the shape of a set of points in the plane", IEEE Transactions on Information Theory 29 (4): 551–559, doi:10.1109/TIT.1983.1056714.

### 2014-08-19 Writing/Final/article.tex
Writing Update

@@
 \begin{abstract}
-Covering both the configuration space, or \emph{C-space}, and represent the right topology is hard to achieve at the same time with traditional sampling-based motion planning algorithms, such as Probabilistic Roadmap and Rapidly-Exploring Random Tree.
+Covering both the configuration space, or \emph{c-space}, and represent the right topology is hard to achieve at the same time with traditional sampling-based motion planning algorithms, such as Probabilistic Roadmap and Rapidly-Exploring Random Tree.
 In this paper, we proposed a method that is able to cover near optimal path and study the shape and topology of configuration space.
-Our method samples a serious of balls to cover the space and use the dual shape of the union of balls to re-construct space.
-We analysis the coverage of the space and show how these balls and their dual shape can be used to generate a graph that maintains the topology of \emph{C-space}
+Our method samples a serious of balls to cover the space and use the dual shape of the union of balls to re-construct the space.
+We analysis the coverage of the space and show how these balls and their dual shape can be used to generate a graph that maintains the topology of \emph{c-space}.
 \end{abstract}
@@
 \section{Introduction}
-\indent\indent Planning a collision-free motion for movable object could be very challenge, especially in high dimensional space, because of the lack of knowledge to understand the shape and top of configuration space.
+\indent\indent Planning a collision-free motion for movable objects could be very challenge, especially in high dimensional space, because of the lack of knowledge to understand the shape and topology of configuration space.
 Meanwhile, motion planning has extensive applicationsto areas like augmented reality \cite{aug}, computer-aided design \cite{design} and bioinformatics \cite{bioinformatics}.
-More knowledge on \emph{C-space} will be benefit to these research.
 
-\indent Although we have seen some study in low dimensional space trying to characterize the topology of \emph{C-space} \cite{ConCompNum} \cite{interval}, these methods suffer dimension curse in high dimension space.
+\indent Although we have seen some study in low dimensional space trying to characterize the topology of \emph{c-space} \cite{ConCompNum} \cite{interval}, these methods suffer dimension curse in higher dimensional space.
 
-\indent Sampling-based method for motion planning appear to be very successful \cite{Book}.
+\indent Sampling-based methods for motion planning appear to be very successful \cite{Book}.
 These methods are usually proved to be \emph{probabilistically complete}, thus guarantee to find a path if it exists.
-Medial Axis sampling \cite{MAPRM} \cite{UMAPRM} attracted researchers attention for their property of characterizing the topology of \emph{C-space} and safe clearance to obstacles, however, no structures are made of these samples to properly represent the space.
-
-\indent Trying to answer the question "does a collision free path exist", Zoe McCarthy uses samples to build an $\alpha$-shape to better understand samples and space captured, which inspires us to explore more with $\alpha$-shape.
+Medial Axis sampling \cite{MAPRM} \cite{UMAPRM} attracted researchers attention for their property of characterizing the topology of \emph{C-space} and safe clearance to obstacles, however, no structures are made with these samples to properly represent the space.
 
@@
 
-\indent In this paper, we will firstly introduce sampling algorithms to cover the \emph{C-space}, medial axis sampling methods are applied to reduce the number of samples and capture the topology of the space.
+\indent Trying to answer the question "does a collision free path exist", Zoe McCarthy uses samples to build an $\alpha$-shape to better understand samples and space captured, which inspires us to explore more with $\alpha$-shape.
+
+\indent In this paper, we will firstly introduce a sampling algorithm to cover the \emph{c-space}, medial axis sampling methods are applied to reduce the number of samples and capture the topology of the space.
 We then use these samples, or balls, to construct the weighted $\alpha$-shape.
 After simplifying the $\alpha$-shape, we will still have a simple graph, which can be used for both motion planning and topology study.
-We at each step, we will demonstrate algorithm results of a 2D configuration space.
+In each step, we will demonstrate algorithm results of a 2D configuration space.
 Some properties of our algorithm are discussed in section 4.
@@
 \indent\indent In this section, we first discuss the basics of sampling-based motion planning and the method of sampling on medial axis.
-With the information of positions and their clearance in c-space, we have samples as spheres.
-We then discuss the dual shapes of the union of balls which plays an important role in understanding the shape of c-space and its topology.
-Some works on graph theory and topology will finally be introduced.
+With the information of positions and their clearance in c-space, we have samples as spheres, or balls.
+We then discuss the dual shape of the union of balls which plays an important role in understanding the shape and topology of \emph{c-space}.
+Some works on graph theory and topology will finally be introduced.s
 
@@
 Such space is called \emph{"Configuration Space"} or \emph{"C-space"}  ($C$).
-The subset of all feasible configurations is called the \emph{free space} (\emph{$C_{free}$}), while $C_{obst} = C \setminus C_{free}$ is the union of all infeasible configurations.
-\cite{UMAPRM} Path planning will generally be viewed as a search in a metric space $X$ for a continuous path from an initial state $x_{init}$ to a goal region $X_{goal} \subset X$.
+The subset of all feasible (collision-free) configurations is called the \emph{free space} (\emph{$C_{free}$}), while $C_{obst} = C \setminus C_{free}$ is the union of all infeasible configurations.
+\cite{UMAPRM} Path planning will generally be viewed as a search in a metric space $X$ for continuous paths from an initial state $x_{init}$ to a goal region $X_{goal} \subset X$.
 For a standard problem, $X = C$.
 \cite{RRT} What needs to be pointed out is that \emph{C-space} is very different from workspace which is usually formed by polygons.
-The shape of \emph{C-space} is usually unknown to us, unless the robot is a point.
+The shape of \emph{C-space} is usually unknown to us, unless the robot is a point, in which case workspace is the \emph{C-space}.
 
@@
 Medial Axis is also called Generallized Voronoi Diagram.
-The medial axis $MA(F)$ of free space $F$ is a strong deformation retract of $F$, which means $F$ can be continuously deformed onto $MA(F)$ while maintaining its topological structure.
+The medial axis $MA(C_{free})$ of free space $C_{free}$ is a strong deformation retract of $C_{free}$, which means $C_{free}$ can be continuously deformed onto $MA(C_{free})$ while maintaining its topological structure.
 However, medial axis is hard to compute explicitly.
@@
 5.6.3, Steven LaValle defined Medial Axis as "Let $(X, \rho)$ be a metric space.
-Let a \emph(maximal ball) be a ball $B(x,r) \subseteq X$ such that no other ball can be a proper subset the centers of all maximal balls trace out a one-dimensional set of points referred to as the \emph{medial axis}".
+Let a \emph{maximal ball} be a ball $B(x,r) \subseteq X$ such that no other ball can be a proper subset.
+The centers of all maximal balls trace out a one-dimensional set of points referred to as the \emph{medial axis}".
 
-\indent Mapping a pair of points $A$ and $B$ in free space onto $MA(F)$, there is a path between $A$ and $B$ if and only if there is a path between their images on $MA(F)$.
+\indent Mapping a pair of points $A$ and $B$ in free space onto $MA(C_{free})$, there is a path between $A$ and $B$ if and only if there is a path between their images on $MA(C_{free})$.
 Such path has a very nice property of the largest clearance from obstacles.
@@
 
-\indent The basic idea of the algorithm proposed in \cite{MAPRM} is: given a point $A$ and its nearest point on the boundary of obstacles $A'$, a ray start from $A$ with direction $\overrightarrow{A'A}$ will always intersect with $MA(F)$.
+\indent The basic idea of the algorithm proposed in \cite{MAPRM} is: given a point $A$ and its nearest point on the boundary of obstacles $A'$, a ray start from $A$ with direction $\overrightarrow{A'A}$ will always intersect with $MA(C_{free})$.
 
@@
 \indent Approximating the shape of an unknown area to study its properties is a very commonly used method.
-We have seen many such ideas in the study of biogeometry.
+We have seen research ideas in the study of biogeometry to solve the problem.
 As for robotics, a few people began to notice the achievements from biogeometry study and tried to apply similar methods to study the shape of \emph{C-space}.
@@
 Edelsbrunner first introduced them in \cite{PointSetShape}.
-By choosing different value of the one parameter $\alpha$, we can have a family of shapes with the same set of points.
+By choosing different values of the one parameter $\alpha$, we can have a family of shapes with the same set of points.
 An example of $\alpha$-shape is in Figure \ref{fig:Alpha-shape}.
@@
 \indent In algebraic topology, the Betti Numbers are used to distinguish topological spaces based on the connectivity of n-dimensional simplicial complexes.
-Informally, the \emph{n-th} Betti number ($\beta_n$) represents the rank of the \emph{n-th} homology group, which tells us the maximum number of cuts that can be mad before diving a surface into two pieces.
+Informally, the \emph{n-th} Betti number ($\beta_n$) represents the rank of the \emph{n-th} homology group, which tells us the maximum number of cuts that can be made before diving a surface into two pieces.
 \cite{betti wiki}
@@
 
-\indent H. Edelsbrunner introduced a way to compute $n-th$ Betti number in \cite{Edel Book}, where he uses gaussian ellimination to compute the betti numbers with adjacency matrix.
+\indent H. Edelsbrunner introduced a way to compute \emph{n-th} Betti number in \cite{Edel Book}, where he uses gaussian ellimination to compute the betti numbers with adjacency matrix.
 
@@
 These kind of graphs are proved to be able to find near optimal path, but can hardly be used to analysis the topology of paths.
-We want to to build a stronger representation of c-space that is both able to cover optimal path and study the topological structure of c-space.
+We want to to build a stronger representation of \emph{C-space} that is both able to cover optimal path and study the topological structure.
 In this section, we are trying to solve the problem in 2D and answer the question "Is two paths in the same homotopy class" as a start point of using our method to study the topology of \emph{C-space}.
-We will first give the outline of the algorithm, and explain each step in detail.
+In this section, we will first give the outline of the algorithm, and explain each step in detail.
 
@@
 By \emph{"clearance"}, we mean its (estimated) distance to the nearest obstacles.
-Ball $B(x, \rho(x))$ is referred as a $"sample"$ in the rest of the section.
+Ball $B(x, \rho(x))$ is referred to as a $"sample"$ in the rest of the section.
 We make no assumption of the shape of obstacles regions in \emph{C-space}.
@@
 After simplifying the dual shape, we will have a roadmap while maintaining the topological structure.
-Phase four break the topology roadmap into pieces such that no two piece can be merged without forming a loop.
+Phase four breaks the topology roadmap into pieces such that no two piece can be merged into a new graph without forming a loop.
 
-\indent We will now explain each phase in detail.
+\indent We will now explain each phase in detail with demos.
 
@@
     // Phase Three
-    \indent \State $dualShape \gets WeightedAlphaShape( some smaples )$
+    \indent \State $dualShape \gets WeightedAlphaShape( maSmaples )$
     \indent \State $topologyRoadmap \gets Retract(dualShape)$
@@
 Besides the positions of configurations, we also keep the clearance of each configuration, thus have some balls, or samples.
-We also require that no new ball, when sampling, is allowed to be centered inside any existing one.
+We also require that no new ball, when sampling, is allowed to be centered inside any existing ones.
 For details of the algorithms, please refer to these two papers.
 One thing worth our notice is that using only algorithm mentioned in \cite{MAPRM}, we can get good result in narrow corridor but are more likely to ignore large open area.
-While using only \cite{UMAPRM} method, we can cover large open area well, but more likely to produce disconnected balls in narrow corridor.
-Therefore, running both algorithm is highly recommended.
+While using only \cite{UMAPRM} method, we can cover large open area well, but more likely to produce disconnected balls in narrow corridors.
+Therefore, running both algorithms is highly recommended.
 
-\indent The reason we sample on medial axis first is that 1.
-these balls are maximal ones as the definition of medial axis suggests, and 2.
-medial axis $MA(C_{free})$ is a SDR of \emph{C-space}.
+\indent The reason we sample on medial axis first is that 1.these balls are maximal ones as the definition of medial axis suggests, thus may reduce the number of samples we get, and 2.medial axis $MA(C_{free})$ is a SDR of \emph{C-space}.
 \cite{MAPRM2}
@@
 The basic idea behind the algorithm is to keep sampling new balls on the boundary of existing ones by "pushing" random configurations inside existing balls to the boundary of them and determine if they are in any other balls.
+If not, we sample a new ball.
 We restrict that all balls to be larger than a minimal radius ball, thus void getting a lot of very small samples.
@@
 It can be done using KNN algorithm, which is more efficient than iterating everything.
-Since we generated random configuration $n$ times, not all are feasible, in a 2D space with area $A$.
+Since we generated random configurations $n$ times(not all are feasible), in a 2D space with area $A$.
 We expect to have $n/A$ configurations in an unit area.
 A ball with radius $r$ has area $\pi r^2$, approximately $k = \frac{n \pi r^2}{A}$ configurations are inside the ball.
-We then project these (uniformly distributed) configurations to the boundary of the ball.
+We then project these (uniformly distributed) configurations to the boundary of the ball to sample new spheres.
 Actually, choosing a larger $k$ could be better: we virtually extend the radius of our discs, which results in a smaller density in arcs that are very close to obstacles than those far from obstacles.
-Samples got in this part is called \emph{regular samples}.
+Samples got in this part are called \emph{regular samples}.
 
-\indent Figure \ref{Samples} is a result of this phase running in a rectangle world with 3 obstacles in the middle.
+\indent Figure \ref{Samples} is a result of this phase running in a rectangle \emph{C-space} with 3 obstacles in the middle.
 Gray balls are centered on medial axis, while green ones are not.
-Red points are centers.
+Red points are ball centers.
 
@@
 
-\indent One might argue that we can simply get configurations on medial and connect them as a roadmap.
+\indent One might argue that we can simply get configurations on medial axis and connect them as a roadmap.
 However, this roadmap doesn't maintain the topology of \emph{C-space}.
@@
 \indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, reconnect these retracted points with other ones using their previous connection.
+By doing so, we got a simple graph that characterize the topology of \emph{C-space}.
+We would like to call it \emph{Topology Roadmap}.
+This roadmap can also be used to determine if paths exist between two configurations.
+An example of such roadmap is shown in Figure \ref{simplifiedgraph}
 
@@
 Knowing which components are the start and goal configurations in, we can find a path connecting these components immediately.
-This technique can be a great improve when $C-space$ is very large and traditional \emph{PRM} or \emph{RRT} methods will take a long time to solve.
+This technique can be a great improve when \emph{C-space} is very large and traditional \emph{PRM} or \emph{RRT} methods will take a long time to solve.
 
-\indent Let $g_1$ and $g_2$ be two graphs without loops. We say $g_1$ and $g_2$ to be mergeable if: 1. they share at least one common node, 2. the new graph formed by these two graph has no loop.
+\indent Let $g_1$ and $g_2$ be two graphs without loops.
+We say $g_1$ and $g_2$ to be \emph{mergeable} if: 1.
+they share at least one common node, 2.
+the new graph formed by these two graph has no loop.
 
@@
 %====================================
-\paragraph{E} \emph{Determine Paths Homotopy Class} \hfill \\
+\paragraph{E} \emph{Determine Paths in the Same Homotopy Class} \hfill \\
 \indent A continuous function, or a map, $f: X \rightarrow Y$ is called a \emph{homotopy equivalence} if there is a map $g: X \rightarrow Y$ such that there exist a continuous function $H: X \times [0,1] \rightarrow Y$ with $H(x, 0) = f$ and $H(x,1) = g$.
@@
   \indent When the number of initial random configurations approaches infinite, the boundaries of all existing balls are fully covered.
-So, every configuration not inside any existing balls will be samples as a ball, unless it's less than $r_{min}$ clearance.
+So, every configuration not inside any existing balls will be sampled as a ball, unless it's less than $r_{min}$ clearance.
 
@@
   \indent We restrict balls to have no less than $r_{min}$ radius and new balls to be centered outside existing ones.
-Assume we partition the space into $r_{min} \cdot r_{min}$ cells in 2D.
+Assume we partition the space into $r_{min} \times r_{min}$ cells in 2D.
 The number of cells is finite, if the space is finite.
@@
 
-  $H(x) = b_i \indent, if \indent |x-b| < |x-b'|, b' \in B$
+  $H(x) = b_i \indent, if \indent |x-b| \leq |x-b'|, b' \in B$
 
-  \indent This continuous function maps any point in the space to balls centered on medial axis. Dual shape maps any points in the balls to the topology roadmap we build.
+  \indent This continuous function maps any points in the space to balls centered on medial axis.
+While every point in the balls is mapped to the dual shape form by filled triangles, nodes and edges.
+Filled triangles are mapped to single nodes.
 
@@
   \begin{theorem}
-  Let $g_1$ and $g_2$ be two loop-free graphs such that merging their common nodes will produce a new graph with loops, $\sigma_1$ and $\sigma_2$, with the same start and goal nodes, be two paths going from $g_1$ to $g_2$ via common nodes $A$ and $B$.
+  Let $g_1$ and $g_2$ be two loop-free graphs such that merging their common nodes will produce a new graph with loops.
+Let $\sigma_1$ and $\sigma_2$, with the same start and goal nodes, be two paths going from $g_1$ to $g_2$ via common nodes $A$ and $B$.
 $\sigma_1$ and $\sigma_2$ have different homotopy type if $A \neq B$
@@
   \paragraph{\emph{Proof}}
-  \indent Because $A$ and $B$ are two common nodes shared by $g_1$ and $g_2$, if $A \neq B$, merging $g_1$ and $g_2$ will create a graph with a loop going from $A \rightarrow B \rightarrow A$.
-Since $\sigma_1$ and $\sigma_2$ have the same start and goal nodes, merging them will also create a loop.
+  \indent Let start and goal nodes be $S$ and $E$.
+Because $A$ and $B$ are two common nodes shared by $g_1$ and $g_2$, if $A \neq B$, merging $g_1$ and $g_2$ will create a graph with a loop going from $S \rightarrow A \rightarrow E \rightarrow B \rightarrow S$.
+The path in the upper of the loop and the path in the lower have different homotopy type.
+Since $\sigma_1$ and $\sigma_2$ have the same start and goal nodes, merging them will create a loop.
 So $\sigma_1$ and $\sigma_2$ have different homotopy type.

### 2014-08-22 Writing/Final/article.tex
experiments

@@
 \begin{abstract}
-Covering both the configuration space, or \emph{c-space}, and represent the right topology is hard to achieve at the same time with traditional sampling-based motion planning algorithms, such as Probabilistic Roadmap and Rapidly-Exploring Random Tree.
+Covering both the configuration space, or \emph{C-space}, and represent the right topology is hard to achieve at the same time with traditional sampling-based motion planning algorithms, such as Probabilistic Roadmap and Rapidly-Exploring Random Tree.
 In this paper, we proposed a method that is able to cover near optimal path and study the shape and topology of configuration space.
 Our method samples a serious of balls to cover the space and use the dual shape of the union of balls to re-construct the space.
-We analysis the coverage of the space and show how these balls and their dual shape can be used to generate a graph that maintains the topology of \emph{c-space}.
+The output of our algorithm can be viewed as a rich representation of \emph{C-space}.
+Benefits include (1)low memory for planning, (2) ability of analyzing shape and topology of \emph{C-space} and (3) fast planning for large space.
+We analysis the coverage of the space and show how these balls and their dual shape can be used to generate a graph that maintains the topology of \emph{C-space}.
 \end{abstract}
@@
 \section{Introduction}
-\indent\indent Planning a collision-free motion for movable objects could be very challenge, especially in high dimensional space, because of the lack of knowledge to understand the shape and topology of configuration space.
+
+\indent\indent A robot state can be represented using n parameters $<x_1, x_2, ..., x_n>$ as a point in a n-dimensional space $X$, called \emph{Configuration Space}, or \emph{C-space}\cite{UMAPRM}.
+In this paper, we present a new method to model \emph{C-space}.
+Our algorithm is sampling-based, We will sample balls in \emph{C-space} to cover the space.
+By using the dual shape of unions of balls we construct the shape of free space, and capture its topology.
+A topology roadmap will then be built which we can use to determine path homotopy type, to find paths in different homotopy classes, and to answer other topology questions.
+We implemented the algorithm in a 2D world with a point robot.
+
+\indent Representing \emph{C-space} is very fundamental for motion planning.
+Covering the space and characterize the topology are two concerns.
+By covering the space better, we can find better paths.
+By studying its topology, we can answer questions like "does a path exist between two configurations?", "does two paths has the same topology?" and "can we find two path that have different homotopy types?".
+These questions arise frequently in applications as predicting paths for unpredictable entities and deployment of multiple agents for efficient exploration of an environment\cite{pathtop}.
+Because of the extensive applications of motion planning to areas like augmented reality \cite{aug}, computer-aided design \cite{design} and bioinformatics \cite{bioinformatics}.
+Answering these questions could benefit many researches.
+
+\indent Previous methods have their disadvantages.
+Some sampling-based methods, such as \emph{PRM*} and \emph{RRT*} \cite{prmstar}, are able to cover the space, but failed to capture the topology \cite{sampissues} because of ``holes" in the roadmap and inability to determine if a ``hole" contains obstacles.
+\emph{Visibility-base Probabilistic Roadmap}, or \emph{vis-PRM} \cite{vprm}, tried to capture the topology by placing ``guards" to ``see" the space.
+However, they can't describe ``visible regions" and overlapping regions explicitly, which makes it difficult to analyze coverage and find optimal paths.
+Medial Axis sampling attracted researchers attention, such as \emph{MAPRM}\cite{MAPRM} and \emph{UMAPRM}\cite{UMAPRM}, for their property of characterizing the topology of \emph{C-space} and safe clearance to obstacles, however, no structures are made with these samples to properly represent the space.
+We have seen some studies in low dimensional space trying to characterize the topology of \emph{C-space}, such as \cite{ConCompNum} and \cite{interval}, these methods suffer dimension curse in higher dimensional space.
+In \cite{pathtopsearch} and \cite{pathtop}, Bhattacharya, et al, studied searching path in a graph with topological constrains, and their method can be extended to higher dimensional space
+
+%\indent Some sampling-based methods, such as \emph{PRM*} and \emph{RRT*} \cite{prmstar}, are able to cover the space, but failed to capture the topology \cite{sampissues} because of "holes" in the roadmap and inability to determine if a "hole" contains obstacles.
+Medial Axis sampling attracted researchers attention, such as \emph{MAPRM}\cite{MAPRM} and \emph{UMAPRM}\cite{UMAPRM}, for their property of characterizing the topology of \emph{C-space} and safe clearance to obstacles, however, no structures are made with these samples to properly represent the space.
+Another sampling-based algorithm that captures the topology of the space is \emph{Visibility-base Probabilistic Roadmap}, or \emph{vis-PRM} \cite{vprm}.
+Although \emph{vis-PRM} has some issues with complex narrow passages, using some sampling heuristics, like \emph{MAPRM}, such issues will be avoid.
+
+\indent Our method addresses these problems by sampling weighted configurations, or balls, and constructing the dual shape of union of balls.
+Thus we are able to analyze the coverage of the space and answer topology-related questions.
+Besides, our algorithm has many advantages.
+It requires low memory for planning paths, allows analysis of shape and topology of \emph{C-space} and fastens planning for large space.
+
+%\indent With sampling-based algorithms, planners will get a lot of feasible (collision-free) samples.
+These samples can actually be used to study the shape of \emph{C-space}.
+Approximating the "shape" of a given point set in a space is a frequently occurred question in many research areas, which is the intuitive of $\alpha$-shape.
+A relative notion is space-filling diagram which is used in chemistry and biology to represent molecular structures\cite{alpha intro}.
+McCarthy, et al, used this idea to answer the question "does a path exist between two configurations", which inspired us to explore more with $\alpha$-shape.
+
+\indent In this paper, we are sampling in $(X, \rho)$ metric space.
+Let $x$ be a configuration in $X$(usually \emph{C-space}), $\rho(x)$ gives the clearance of configuration $x$, negative if infeasible, positive if feasible.
+By \emph{"clearance"}, we mean its (estimated) distance to the nearest obstacles.
+Our experiments environment is a point robot with polygonal obstacles, so we can fast determine the clearance of a configuration.
+( In practice, workspace doesn't have to be the same as configuration space, as long as we can get the clearance of a configuration which can be done by checking the collision distance of a robot.
+)
+
+%\indent\indent Planning a collision-free motion for movable objects could be very challenge, especially in high dimensional space, because of the lack of knowledge to understand the shape and topology of configuration space.
 Meanwhile, motion planning has extensive applicationsto areas like augmented reality \cite{aug}, computer-aided design \cite{design} and bioinformatics \cite{bioinformatics}.
 
-\indent Although we have seen some study in low dimensional space trying to characterize the topology of \emph{c-space} \cite{ConCompNum} \cite{interval}, these methods suffer dimension curse in higher dimensional space.
+%\indent Although we have seen some study in low dimensional space trying to characterize the topology of \emph{C-space} \cite{ConCompNum} \cite{interval}, these methods suffer dimension curse in higher dimensional space.
 
-\indent Sampling-based methods for motion planning appear to be very successful \cite{Book}.
+%\indent Sampling-based methods for motion planning appear to be very successful \cite{Book}.
 These methods are usually proved to be \emph{probabilistically complete}, thus guarantee to find a path if it exists.
@@
 
-\indent Approximating the "shape" of a given point set in a space is a frequently occurred question in many research areas, which is the intuitive of $\alpha$-shape.
+%\indent Approximating the "shape" of a given point set in a space is a frequently occurred question in many research areas, which is the intuitive of $\alpha$-shape.
 A relative notion is space-filling diagram which is used in chemistry and biology to represent molecular structures.
@@
 
-\indent Trying to answer the question "does a collision free path exist", Zoe McCarthy uses samples to build an $\alpha$-shape to better understand samples and space captured, which inspires us to explore more with $\alpha$-shape.
+%\indent Trying to answer the question "does a collision free path exist", Zoe McCarthy uses samples to build an $\alpha$-shape to better understand samples and space captured, which inspires us to explore more with $\alpha$-shape.
 
-\indent In this paper, we will firstly introduce a sampling algorithm to cover the \emph{c-space}, medial axis sampling methods are applied to reduce the number of samples and capture the topology of the space.
+%\indent In this paper, we will firstly introduce a sampling algorithm to cover the \emph{C-space}, medial axis sampling methods are applied to reduce the number of samples and capture the topology of the space.
 We then use these samples, or balls, to construct the weighted $\alpha$-shape.
@@
 \indent\indent In this section, we first discuss the basics of sampling-based motion planning and the method of sampling on medial axis.
-With the information of positions and their clearance in c-space, we have samples as spheres, or balls.
-We then discuss the dual shape of the union of balls which plays an important role in understanding the shape and topology of \emph{c-space}.
+With the information of positions and their clearance in \emph{C-space}, we have samples as spheres, or balls.
+We then discuss the dual shape of the union of balls which plays an important role in understanding the shape and topology of \emph{C-space}.
 Some works on graph theory and topology will finally be introduced.s
@@
 Such space is called \emph{"Configuration Space"} or \emph{"C-space"}  ($C$).
-The subset of all feasible (collision-free) configurations is called the \emph{free space} (\emph{$C_{free}$}), while $C_{obst} = C \setminus C_{free}$ is the union of all infeasible configurations.
-\cite{UMAPRM} Path planning will generally be viewed as a search in a metric space $X$ for continuous paths from an initial state $x_{init}$ to a goal region $X_{goal} \subset X$.
-For a standard problem, $X = C$.
-\cite{RRT} What needs to be pointed out is that \emph{C-space} is very different from workspace which is usually formed by polygons.
+The subset of all feasible (collision-free) configurations is called the \emph{free space} (\emph{$C_{free}$}), while $C_{obst} = C \setminus C_{free}$ is the union of all infeasible configurations\cite{UMAPRM}.
+Path planning will generally be viewed as a search in a metric space $X$ for continuous paths from an initial state $x_{init}$ to a goal region $X_{goal} \subset X$.
+For a standard problem, $X = C$ \cite{RRT}.
+What needs to be pointed out is that \emph{C-space} is very different from workspace which is usually formed by polygons.
 The shape of \emph{C-space} is usually unknown to us, unless the robot is a point, in which case workspace is the \emph{C-space}.
@@
 By connecting start and goal configurations to the roadmap, a graph search, e.g., A*, can be performed to extract a near optimal solution path.
+Problem is it's hard to analyze coverage of the space with these methods.
+And ``holes" in a roadmap cannot tell if there are obstacles, thus we can't use it to analysis path topology.
+Our method can avoid these problems by analyzing balls and their dual shape.
 
-\indent One disadvantage of these methods is that we can't study the topological structure of C-space using only the data structures constructed.
+\indent Some methods do captures topology of \emph{C-space}.
+\emph{Visibility-based Probabilistic Roadmap}\cite{vprm} might be one of them.
+By randomly sampling ``guards" that can't see each other, the algorithm can produce guards that cover most of the space.
+Then connection nodes will be generated to connect guards.
+Our method is very much related to \emph{Vis-PRM}.
+``Guards" of \emph{Vis-PRM} describe their ``visible regions" implicitly, while our method limit a configuration to have a ``visible range", the clearance.
+Thus, we can describe overlapping regions and visible regions explicitly.
+
+\indent It's still possible to use \emph{PRM} to find paths with topology constrains.
+In \cite{pathtopsearch} and \cite{pathtop}, by combining integration theory with search techniques, Bhattacharya, et al, studied searching path in a graph with topological constrains, and their method can be extended to higher dimensional space.
+
+\indent Methods like \emph{PRM*} requires much memory to store the roadmap because of the large amount of vertices and greater amount of edges.
+Some algorithms, such as \cite{weifu} and \cite{bekris}, have been proposed to reduce the memory requirement by reducing edges of \emph{PRM*}.
+These methods try to solve the problem after it happened, while our method tries to avoid the problem from happening.
 
@@
 %====================================
-\paragraph{B} \emph{Medial Axis Sampling} \hfill \\
+\paragraph{C} \emph{Medial Axis Sampling} \hfill \\
 \indent A simpler method that maintains the topology of \emph{C-space} but doesn't cover near optimal path is medial axis sampling.
@@
 
-\indent In Figure \cite{Book}, sec.
-5.6.3, Steven LaValle defined Medial Axis as "Let $(X, \rho)$ be a metric space.
+\indent In \cite{Book}, sec.
+5.6.3, S.
+LaValle defined Medial Axis as "Let $(X, \rho)$ be a metric space.
 Let a \emph{maximal ball} be a ball $B(x,r) \subseteq X$ such that no other ball can be a proper subset.
@@
 
-\indent Steven A.
+\indent S.
 Wilmart \cite{MAPRM} sampled on the medial axis of free space to build up a probabilistic roadmap planner.
@@
 
-\indent Hsin-Yi (Cindy) Yeh \cite{UMAPRM} solved this problem by putting some random "sticks" with random directions in free space.
+\indent Yeh \cite{UMAPRM} solved this problem by putting some random "sticks" with random directions in free space.
 Any surfaces will intersect uniformly with these sticks, thus searching on sticks to find points that intersect with medial axis will give nodes uniformly distributed on the medial axis.
@@
 \begin{figure}
-	\center{\includegraphics[scale=0.35]{./pics/MA.png}}
-	\caption{\label{fig:Medial Axis} Sampling on the Medial Axis of a rectangle space.\cite{Book}}
+	\center{\includegraphics[scale=0.35]{./pics/MA.PNG}}
+	\caption{\label{fig:Medial Axis} Sampling on the Medial Axis of a rectangle space. The black blocks are obstacles. We will use this world as our working space in the following sections. }
 \end{figure}
@@
 
-\indent Zoe McCarthy \cite{PathNonexistance} used samples generated by PRM to form the $\alpha$-shape of \emph{C-space}.
+\indent We have seen papers concerning the shape of \emph{C-space}.
+Robin, et al, developed a computational method for detecting large convex regions of obstacle-free space\cite{largeconvex}.
+Knowing such information can be helpful to plan robot footstep locations while avoiding obstacles and other optimization problems.
+But this method can only capture local features.
+
+\indent Z.
+McCarthy, et al, \cite{PathNonexistance} used samples generated by PRM to form the $\alpha$-shape of \emph{C-space}.
 She then proved there doesn't exist a path between a pair of configurations by proving they are in two different disconnected components of the shape.
@@
 \indent Define a \emph{simplicial complex} $D$: a collection of simplices such that if $\bigtriangleup_T \subseteq D$ ( $\bigtriangleup_T$ is the convex hull of $T$ ), then if $U \subseteq T$, we have $\bigtriangleup_U \subseteq D$ and also that the intersection of two simplices in $D$ is either empty or another simplex in $D$.
-The $\alpha$-shape of a set of points $S$ is a generalization of the convex hull of those points.
-\cite{PathNonexistance}.
+The $\alpha$-shape of a set of points $S$ is a generalization of the convex hull of those points\cite{PathNonexistance}.
 H.
@@
 	\center{\includegraphics[scale=0.7]{./pics/alphaShape.png}}
-	\caption{\label{fig:Alpha-shape} An example of $\alpha$-shape. \cite{PointSetShape}}
+	\caption{\label{fig:Alpha-shape} An example of $\alpha$-shape}
 \end{figure}
@@
 	\center{\includegraphics[scale=0.30]{./pics/dualshape.png}}
-	\caption{\label{fig:Dual Shape} An example of weighted $\alpha$-shape for a union of balls. \cite{DualShape}}
+	\caption{\label{fig:Dual Shape} An example of weighted $\alpha$-shape for a union of balls. Copied from \cite{DualShape}}
 \end{figure}
@@
 
-\indent The first betti number of a graph is very easy to compute. Given a graph $G$, with $n$ vertices, $m$ edges and $k$ components. It's 1st betti number is:
+\indent The first Betti number of a graph is very easy to compute. Given a graph $G$, with $n$ vertices, $m$ edges and $k$ components. It's 1st Betti number is
 
-$\beta_1 = m - n + k$
+\begin{equation}
+\beta_1 = m - n + k
+\end{equation}
 
-\indent This can be proved straightforwardly by mathematical induction on the number of edges.
-A new edge either increments the number of 1-cycles or decrements the number of connected components.
-\cite{betti wiki}
+\indent Proof of this equation can be found in \cite{cyclomatic}.
 
-\indent H. Edelsbrunner introduced a way to compute \emph{n-th} Betti number in \cite{Edel Book}, where he uses gaussian ellimination to compute the betti numbers with adjacency matrix.
+\indent H. Edelsbrunner introduced a way to compute \emph{n-th} Betti number in \cite{Edel Book}, where he uses gaussian elimination to compute the Betti numbers with adjacency matrix.
 
-\indent Vanessa Robins \cite{alpha betti} provided more detailed explains and proofs on computing betti numbers. What's more, she put more thoughts on computing betti numbers for alpha shapes.
+\indent V.
+Robins \cite{alpha betti} provided a computational technique for computing Betti numbers with detailed explains and proofs.
+What's more, she put more thoughts on computing Betti numbers for alpha shapes.
 
@@
 	\center{\includegraphics[scale=0.26]{./pics/Torus.png}}
-	\caption{\label{fig:Torus} The torus has one connected component($\beta_0$), two circular holes ($\beta_1$,the one in the center and the one in the middle of the "donut"), and one two-dimensional void ($\beta_2$, the inside of the "donut").\cite{betti wiki}}
+	\caption{\label{fig:Torus} The torus has one connected component($\beta_0$), two circular holes ($\beta_1$,the one in the center and the one in the middle of the "donut"), and one two-dimensional void ($\beta_2$, the inside of the "donut").
+Copied from \cite{betti wiki}}
 \end{figure}
@@
 \indent \indent Traditionally, sampling based algorithms will build a graph for configuration space.
-These kind of graphs are proved to be able to find near optimal path, but can hardly be used to analysis the topology of paths.
+Some of these graphs, such as \emph{PRM*} and \emph{RRT*} \cite{prmstar}, are proved to be able to find near optimal path, but can hardly be used to analysis the topology of paths.
 We want to to build a stronger representation of \emph{C-space} that is both able to cover optimal path and study the topological structure.
@@
 In this section, we will first give the outline of the algorithm, and explain each step in detail.
+
+\indent In the rest of the section, we will use the term "configuration" to refer to a point in configurations space.  Ball $B(x, \rho(x))$ is referred to as a $"sample"$ in the rest of the section.
 
@@
 \paragraph{A} \emph{The Algorithm outline} \hfill \\
-\indent Before starting introducing our algorithm, we firstly clarify some preliminary tools we can have: We are sampling in $(X, \rho)$ metric space.
-Let $x$ be a configuration in $X$(usually \emph{C-space}), $\rho(x)$ gives the clearance of configuration $x$.
-By \emph{"clearance"}, we mean its (estimated) distance to the nearest obstacles.
-Ball $B(x, \rho(x))$ is referred to as a $"sample"$ in the rest of the section.
-We make no assumption of the shape of obstacles regions in \emph{C-space}.
 
@@
   \begin{algorithmic}[1]
-  \Function{WeNeedAGoodName}{\emph{C-space}}
+  \Function{RichCspaceRepresent}{\emph{C-space}, number}
 
@@
   \end{algorithmic}
-  \caption{\label{fig:Algo} Algorithm Outline}
+  \caption{\label{fig:Algo} Algorithm Outline. \emph{C-space} here means the metric space $(X, \rho)$ where we can know if a configuration is feasible and its clearance to nearest obstacles.}
 \end{figure}
@@
 %====================================
-% Covering c-space
+% Covering C-space
 %====================================
@@
 We expect to have $n/A$ configurations in an unit area.
-A ball with radius $r$ has area $\pi r^2$, approximately $k = \frac{n \pi r^2}{A}$ configurations are inside the ball.
+A ball with radius $r$ has area $\pi r^2$, approximately
+\begin{equation}
+k = n \cdot \pi r^2 / A
+\end{equation} 
+configurations are inside the ball.
 We then project these (uniformly distributed) configurations to the boundary of the ball to sample new spheres.
@@
 The reason is shown in Figure \ref{badthing}: three balls are all centered on medial axis, but their dual shape will be an empty triangle, which introduces a "hole" in that area.
-To solve this problem we can try to sample a ball centered at the the radical center after getting an empty triangle, and rebuild the dual shape for these four balls.
-\cite{radical center} Proving the solution is very simple: if there is no obstacles in that area, the newly sampled ball will cover the space, if there is obstacle, the ball will either not be sampled or not connect three of the balls.
+To solve this problem we can try to sample a ball centered at the radical center after getting an empty triangle, and rebuild the dual shape for these four balls\cite{radical center}.
+A simple proof: if there is no obstacles in that area, the newly sampled ball will connect three balls, if there is obstacle, the ball will either not be sampled or not connect three of the balls.
 
@@
 This roadmap can also be used to determine if paths exist between two configurations.
-An example of such roadmap is shown in Figure \ref{simplifiedgraph}
+An example of such roadmap is shown in Figure \ref{simplifiedgraph}.
+Filled triangles, along with large balls, are suggesting some large open areas, which is a problem \cite{largeconvex} is trying to address.
+
+\indent This is not the only method of building the topology roadmap of \emph{C-space}, another option will be to build a visibility roadmap, like \cite{vprm}, but using only ball centers as roadmap nodes.
+One might come up with other heuristics to achieve the same thing.
+Due to the limited number of balls, any algorithms can have a good performance.
+
+\indent
 
@@
 	\center{\includegraphics[scale=0.3]{./pics/my_dualshape.PNG}}
-	\caption{\label{ourdualshape}} Dual shape of balls generated in phase 1 (centered on medial axis).
+	\caption{\label{ourdualshape}} Dual shape of balls generated in phase 1 (centered on medial axis). Filled triangles, along with large balls, are suggesting some large open areas.  
 \end{figure}
@@
 
-\indent Determine if a simple graph has a loop is very easy using the first Betti number $\beta_1$ mentioned in section 2.
+\indent Determine if a simple graph has a loop is very easy using the first Betti number $\beta_1$ mentioned in section 2, equation (1).
 
@@
 The idea behind this algorithm is to take every edges as an initial component, then iterate each component to find and merge with a mergeable component until there is no two mergeable components.
+
+\indent By breaking a graph into several parts, we virtually break the space into several subspaces. In this sense, our method can be viewed as a space partition strategy.
 
@@
 \section{Good Properties}\label{properties}
-
+\indent\indent This section should be re-organized as below:
+  \subsection{Coverage Analysis}
   \begin{theorem}
@@
   \indent When the number of initial random configurations approaches infinite, the boundaries of all existing balls are fully covered.
-So, every configuration not inside any existing balls will be sampled as a ball, unless it's less than $r_{min}$ clearance.
+So, every configuration not inside any existing balls will be sampled as a ball, unless it's less than $r_{min}$ clearance.\\
 
+  As we can see, we can analyze the coverage of the space.
+Even more, we can explicitly describe the coverage of each ball in the algorithm.
+Using this property, we can find near optimal path.
+We will show some experiments in section 5.
+
+  \begin{theorem}
+  Let $b \in B$ be an element of $B$, $A$ and $B$ are two configurations in \emph{C-space}.
+The optimal path $\sigma$ between $A$ and $B$ is in $\bigcup_{b\in B}$ if $\sigma$ has clearance no less than $r_min$.
+  \end{theorem}   
+  \paragraph{\emph{Proof}}
+  \indent This is a direct conclusion of previous theorem.
+
+  \subsection{Low Memory Representation}  
   \begin{theorem}
@@
 Figure \ref{ourdualshape} shows the dual shape of balls generated by previous phase.
+\\
+
+  In practice, most balls are much larger than minimum radius.
+So the actually number of balls is very limited.
+We will see, in section 5, the number of balls required to cover a space tends to be stable.
+
+  \subsection{Analysis of Topology}
+
+  In this subsection, we will see how to use the structure built by our algorithm to determine path topology.
 
   \begin{theorem}
-  Let $b \in B$ be an element of $B$, $A$ and $B$ are two configurations in \emph{C-space}.
-The optimal path $\sigma$ between $A$ and $B$ is in $\bigcup_{b\in B}$ if $\sigma$ has clearance no less than $r_min$.
+  Any path $\sigma$ can be continuously deformed onto medial axis. 
   \end{theorem}   
   \paragraph{\emph{Proof}}
-  \indent This is a direct conclusion of previous theorem.
+  \indent This is the definition of Medial Axis $MA(C_{free})$ being a strong deformation retraction of $C_{free}$.\\
 
-  \begin{theorem}
-  Any path $\sigma$ can be continuously deformed into medial axis. 
-  \end{theorem}   
-  \paragraph{\emph{Proof}}
-  \indent This is the definition of Medial Axis $MA(C_{free})$ being a strong deformation retraction of $C_{free}$.
+  Given the theorem that any path can be deformed onto medial axis, we now use medial axis samples to determine if two paths have the same homotopy type.
 
@@
   \indent Let $x$ be a point in the space $X$, $B = \{ b_1, b_2, ..., b_n \}$ be the set of balls centered on medial axis. Define map $H(x)$:
-
-  $H(x) = b_i \indent, if \indent |x-b| \leq |x-b'|, b' \in B$
-
+  \begin{equation}
+  H(x) = b_i \indent, if \indent |x-b| \leq |x-b'|, b' \in B
+  \end{equation}
   \indent This continuous function maps any points in the space to balls centered on medial axis.
@@
 
-  \begin{theorem}
-  Let $g_1$ and $g_2$ be two loop-free graphs such that merging their common nodes will produce a new graph with loops.
+%  \begin{theorem}
+%  Let $g_1$ and $g_2$ be two loop-free graphs such that merging their common nodes will produce a new graph with loops.
 Let $\sigma_1$ and $\sigma_2$, with the same start and goal nodes, be two paths going from $g_1$ to $g_2$ via common nodes $A$ and $B$.
 $\sigma_1$ and $\sigma_2$ have different homotopy type if $A \neq B$
-  \end{theorem}
-  \paragraph{\emph{Proof}}
-  \indent Let start and goal nodes be $S$ and $E$.
+%  \end{theorem}
+%  \paragraph{\emph{Proof}}
+%  \indent Let start and goal nodes be $S$ and $E$.
 Because $A$ and $B$ are two common nodes shared by $g_1$ and $g_2$, if $A \neq B$, merging $g_1$ and $g_2$ will create a graph with a loop going from $S \rightarrow A \rightarrow E \rightarrow B \rightarrow S$.
@@
 
+  \subsection{Fast Planning}
+  \indent\indent By breaking a graph into several parts, we virtually break the space into several subspaces.
+In this sense, our method can be viewed as a space partition strategy.
+Every subspace is managed by a tree, and trees are connected with shared common nodes.
+Every node in a tree represents a cell of power-diagram, as suggested by equation (3).
+
+  \indent
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\section{Experiments}\label{experiments}
-%We now describe the some experiments and their results.
+\section{Experiments}\label{experiments}
+We now describe the some experiments and their results.
 
@@
 \begin{thebibliography}{1}
-  \bibitem{aug} J.-M. Lien, O. B. Bayazit, R.-T. Sowell, S. Rodriguez, and N. M. Amato. Shepherding behaviors. In Proc. IEEE Int. Conf. Robot.Autom. (ICRA), pages 4159–4164, April 2004.
-  \bibitem{design} O. B. Bayazit, G. Song, and N. M. Amato. Enhancing randomized motion planners: Exploring with haptic hints. In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pages 529–536, 2000.
+  \bibitem{weifu} Weifu Wang, Devin Balkcom, Amit Chakrabarti, ``A fast streaming spanner algorithm for incrementally constructing sparse roadmaps", IROS 2013.
+  \bibitem{bekris} Marble J and Bekris KE. ``Asymptotically near-optimal planning with probabilistic roadmap spanners", IEEE Transactions on Robotics, 29(3), 2013.
+  \bibitem{largeconvex} Robin L H Deits and Russ Tedrake.
+``Computing large convex regions of obstacle-free space through semidefinite programming".
+In Proceedings of the Eleventh International Workshop on the Algorithmic Foundations of Robotics (WAFR 2014), Istanbul, 2014.
+  \bibitem{sampissues} Lindemann, Stephen R., and Steven M. LaValle. ``Current issues in sampling-based motion planning." Robotics Research. Springer Berlin Heidelberg, 2005. 36-54.
+  \bibitem{pathtopsearch} Bhattacharya, Subhrajit, Maxim Likhachev, and Vijay Kumar. ``Topological constraints in search-based robot path planning." Autonomous Robots 33.3 (2012): 273-290.
+  \bibitem{pathtop} Bhattacharya, Subhrajit, Vijay Kumar, and Maxim Likhachev. ``Search-based path planning with homotopy class constraints." Third Annual Symposium on Combinatorial Search. 2010.
+  \bibitem{prmstar} Sertac Karaman, Emilio Frazzoli, ``Sampling-based Algorithms for Optimal Motion Planning", International Journal of Robotic Research - IJRR , vol.
+abs/1105.1, no.
+7, pp.
+846-894, 2011.
+  \bibitem{vprm} Thierry Siméon, Jean-paul Laumond, Carole Nissoux, ``Visibility-based probabilistic roadmaps for motion planning", Advanced Robotics , vol. 14, no. 6, pp. 477-493, 2000.
+  \bibitem{aug} J.-M. Lien, O. B. Bayazit, R.-T. Sowell, S. Rodriguez, and N. M. Amato. ``Shepherding behaviors". In Proc. IEEE Int. Conf. Robot.Autom. (ICRA), pages 4159–4164, April 2004.
+  \bibitem{design} O. B. Bayazit, G. Song, and N. M. Amato. ``Enhancing randomized motion planners: Exploring with haptic hints". In Proc. IEEE Int. Conf. Robot. Autom. (ICRA), pages 529–536, 2000.
   \bibitem{bioinformatics} A.
@@
 Brutlag.
-A motion planning approach to flexible ligand binding.
+``A motion planning approach to flexible ligand binding".
 In Int.
@@
 (2006).
-"Counting the Number of Connected Components of a Set and Its Application to Robotics".
+``Counting the Number of Connected Components of a Set and Its Application to Robotics".
 Applied Parallel Computing, Lecture Notes in Computer Science 3732 (1).
-  \bibitem{interval} Jaulin, L. (2001). "Path planning using intervals and graphs". Reliable Computing 7 (1).  
-  \bibitem{Book} Steven M. LaValle, "Planning Algorithms", Cambridge University Press, ISBN 0-521-86205-1, 2006.
-  \bibitem{UMAPRM} Yeh, Hsin-Yi Cindy, et al. "UMAPRM: Uniformly Sampling the Medial Axis."
-  \bibitem{RRT} LaValle, Steven M. "Rapidly-Exploring Random Trees A New Tool for Path Planning." (1998).
+  \bibitem{interval} Jaulin, L. (2001). ``Path planning using intervals and graphs". Reliable Computing 7 (1).  
+  \bibitem{Book} Steven M. LaValle, ``Planning Algorithms", Cambridge University Press, ISBN 0-521-86205-1, 2006.
+  \bibitem{UMAPRM} Yeh, Hsin-Yi Cindy, et al. ``UMAPRM: Uniformly Sampling the Medial Axis."
+  \bibitem{RRT} LaValle, Steven M. ``Rapidly-Exploring Random Trees A New Tool for Path Planning." (1998).
   \bibitem{PRM} L.
@@
 H.
-Overmars, “Probabilistic roadmaps for path planning in high-dimensional configuration spaces,” IEEE Trans.
+Overmars, ``Probabilistic roadmaps for path planning in high-dimensional configuration spaces" IEEE Trans.
 Robot.
@@
 Stiller.
-"MAPRM: A probabilistic roadmap planner with sampling on the medial axis of the free space." Robotics and Automation, 1999.
+``MAPRM: A probabilistic roadmap planner with sampling on the medial axis of the free space." Robotics and Automation, 1999.
 Proceedings.
@@
 Stiller.
-MAPRM: A probabilistic roadmap planner with sampling on the medial axis of the free space.
+``MAPRM: A probabilistic roadmap planner with sampling on the medial axis of the free space".
 Technical Report TR98-022, Department of Computer Science, Texas A\&M University, College Station, TX, Nov.
 1998.
-  \bibitem{DualShape} Edelsbrunner, Herbert. "The union of balls and its dual shape." Proceedings of the ninth annual symposium on Computational geometry. ACM, 1993.
-  \bibitem{alpha intro} "Alpha Shape Introduction", Duck University, ($http://biogeometry.duke.edu/software/alphashapes/$)
-  \bibitem{PointSetShape} Edelsbrunner, Herbert; Kirkpatrick, David G.; Seidel, Raimund (1983), "On the shape of a set of points in the plane", IEEE Transactions on Information Theory 29 (4): 551–559, doi:10.1109/TIT.1983.1056714.
-  \bibitem{radical center} "Radical Center", From Wolfram MathWorld -- the web's most extensive mathematics resource. ($http://mathworld.wolfram.com/RadicalCenter.html$)
+  \bibitem{DualShape} Edelsbrunner, Herbert. ``The union of balls and its dual shape." Proceedings of the ninth annual symposium on Computational geometry. ACM, 1993.
+  \bibitem{alpha intro} ``Alpha Shape Introduction", Duck University, ($http://biogeometry.duke.edu/software/alphashapes/$)
+  \bibitem{PointSetShape} Edelsbrunner, Herbert; Kirkpatrick, David G.; Seidel, Raimund (1983), ``On the shape of a set of points in the plane", IEEE Transactions on Information Theory 29 (4): 551–559, doi:10.1109/TIT.1983.1056714.
+  \bibitem{radical center} ``Radical Center", From Wolfram MathWorld -- the web's most extensive mathematics resource. ($http://mathworld.wolfram.com/RadicalCenter.html$)
   \bibitem{PathNonexistance} Z.
@@
 Bretl, and S.
-Hutchinson, "Proving path non-existence using sampling and alpha shapes," in IEEE International Conference on Robotics and Automation (ICRA), May 2012.
-  \bibitem{betti wiki} "Betti Number", From Wikipedia -- The Free Encyclopedia. ( $http://en.wikipedia.org/wiki/Betti_number$ )    
-  \bibitem{Edel Book}Edelsbrunner, Herbert, and John Harer. "Computational topology: an introduction." American Mathematical Soc., 2010. page. 88 - 93.
-  \bibitem{alpha betti} Robins, Vanessa. "Computational topology for point data: Betti numbers of α-shapes." Morphology of Condensed Matter. Springer Berlin Heidelberg, 2002. 261-274.
+Hutchinson, ``Proving path non-existence using sampling and alpha shapes," in IEEE International Conference on Robotics and Automation (ICRA), May 2012.
+  \bibitem{betti wiki} ``Betti Number", From Wikipedia -- The Free Encyclopedia. ( $http://en.wikipedia.org/wiki/Betti_number$ )   
+  \bibitem{cyclomatic} GYULA KAROLYI, AMBRUS PAL, ``The cyclomatic number of connected graphs without solvable orbits", Periodica Mathematica Hungarica, 01/2007; 
+  \bibitem{Edel Book}Edelsbrunner, Herbert, and John Harer. ``Computational topology: an introduction." American Mathematical Soc., 2010. page. 88 - 93.
+  \bibitem{alpha betti} Robins, Vanessa. ``Computational topology for point data: Betti numbers of α-shapes." Morphology of Condensed Matter. Springer Berlin Heidelberg, 2002. 261-274.
 \end{thebibliography}

### 2014-08-22 AstarPriorityQueue.py

@@ -1,0 +1,46 @@
+import sys, os
+import itertools
+from heapq import *
+
+class AstarPriorityQueue:
+    def __init__(self):
+        self.mPriQue = []                    	# list of entries arranged in a heap
+        self.mEntryFinder = {}               	# mapping of tasks to entries
+        self.mREMOVED = '<self.mREMOVED-task>'  # placeholder for a self.mREMOVED task
+        self.mCounter = itertools.count()     	# unique sequence count
+        
+    def push(self, task, priority):
+        'Add a new task or update the priority of an existing task'
+        if task in self.mEntryFinder:
+            self.remove_task(task)
+        count = next(self.mCounter)
+        entry = [priority, count, task]
+        self.mEntryFinder[task] = entry
+        heappush(self.mPriQue, entry)
+
+    def find(self, task):
+        if task in self.mEntryFinder:
+            return self.mEntryFinder[task];
+        else:
+            return None;
+
+    def remove_task(self, task):
+        'Mark an existing task as self.mREMOVED.  Raise KeyError if not found.'
+        entry = self.mEntryFinder.pop(task)
+        entry[-1] = self.mREMOVED
+
+    def pop(self):
+        'Remove and return the lowest priority task. Raise KeyError if empty.'
+        while self.mPriQue:
+            priority, count, task= heappop(self.mPriQue)
+            if task is not self.mREMOVED:
+                entry = self.mEntryFinder[task];
+                del self.mEntryFinder[task]
+                return task, entry[0];  # task, F
+        raise KeyError('pop from an empty priority queue')
+
+    def isEmpty(self):
+        return len(self.mPriQue) == 0;
+
+    def count(self):
+        return len(self.mPriQue);

### 2014-08-22 AstarSearcher.py

@@ -1,0 +1,320 @@
+
+import sys, os, datetime
+import math
+from collections import defaultdict
+from time import sleep
+import pygame
+
+from AstarPriorityQueue import *;
+from geometry import *;
+from obstacles import *
+from robot import *
+
+class Sphere:
+	'''A sphere in c-space is defined as (center, radius)'''
+	def __init__( self, center, radius ):
+		self.center = center;
+		self.radius = radius;
+
+	def contains( self, point ):
+		'''determine if the sphre contains a point'''
+		distSqr = (self.center - point).r()
+
+		if distSqr <= self.radius:
+			return True;
+		else:
+			return False;
+
+	def getBoundaryConfigs(self, num):
+		""" Get configs in the boundary of the sphere. For 2D only!!!!
+		@param num: the number of boundary configs you need. 
+		When num = 0, automatically get boundary configs.
+		"""
+		retSet = []
+		if( num == 0 ):
+			num = self.radius / 5 + 5;
+
+		dlt_ang = (2*math.pi) / float(num); # increment of angle;
+		for i in range(1, int(num)+1):
+			ang = dlt_ang * i;
+			newX = self.center.x+(self.radius+1.3)*math.cos( ang );
+			newY = self.center.y+(self.radius+1.3)*math.sin( ang );
+			retSet += [ v2(newX, newY) ]
+		return retSet;
+
+
+
+class SphereRelationDetector:
+	def __init__( self, spheres ):
+		"""Given a list of spheres detect the overlapping realationship between each sphere"""
+		self.mSpheres = spheres;
+		self.mOverlapDict = default( list );
+
+class AstarNode:
+	def __init__(self, pos, parent, sphere = None):
+		"""
+		@param pos:v2
+		@param parent: AstarNode
+		@param sphere: Sphere. The sphere the sample is in
+		"""
+		self.mPosition = pos;
+		self.mParentNode = parent;
+		self.mSphere = sphere;		# The sphere the sample is in
+		self.mG = 0;
+		self.mH = 0;
+		self.mF = 0; 				# F = cost + heuristic
+
+class AstarPlus(object):
+	"""description of class"""
+	def __init__( self, spheres ):
+		"""Constructor of AstarSearcher. The constructor will iterate each given spheres,
[…]

### 2014-08-22 MAPRM.py

@@ -460,21 +460,25 @@ pntOnMA, dist = searcher.searchISO( gameWorld.obstMgr, gameWorld, 30, DISPLAYSUR
 #samples = sampler.sampleISOn(30, DISPLAYSURF);
 #samples  = sampler.sampleMAn(DISPLAYSURF);
 #sampler.save_data( samples, "masamples.txt" );
-samples  = sampler.load_data( "masamples.txt" );
-samples2 = sampler.sampleMA( 2000 );
-samples3 = sampler.sampleISOn( 34, samples );
+#samples  = sampler.load_data( "masamples.txt" );
+samples2 = sampler.sampleMA( 3000 );
+#samples3 = sampler.sampleISOn( 34, samples );
 
 print "Finished!"
-
+'''
 for sample in samples:
 	pygame.draw.circle( DISPLAYSURF, (220, 220, 220), (int(sample[0].x), int(sample[0].y)), int(sample[1]) );
-
+'''
 #for sample in samples:
 #	pygame.draw.circle( DISPLAYSURF, (20, 20, 20), (int(sample[0].x), int(sample[0].y)), int(sample[1]), 1 );
 
 for sample in samples2:
 	pygame.draw.line( DISPLAYSURF, (30, 30, 30), (int(sample[0].x), int(sample[0].y)),(int(sample[0].x), int(sample[0].y)), 2 );	
 
+gameWorld.render(DISPLAYSURF);
+pygame.image.save( DISPLAYSURF, './imgs/medialaxis.PNG' );
+
+sys.exit()
 #for sample in samples:
 #	pygame.draw.circle( DISPLAYSURF, (30, 30, 30), (int(sample[0].x), int(sample[0].y)), int(sample[1]), 1 );
 #   pygame.draw.line( DISPLAYSURF, (30, 30, 30), (int(sample[0].x), int(sample[0].y)),(int(sample[0].x), int(sample[0].y)), 2 );

### 2014-08-22 obstacles.py

@@ -77,6 +77,8 @@ class ObstManager:
 
 	def intersects(self, robot):
 		'''determine if the robot intersects with any obstacles in the space'''
+		if robot is None:
+			return False;
 		if self.inside( robot.position() ):
 			return True;
 		for obst in self.obsts:

### 2014-08-22 topology/alphashape.py

@@ -315,14 +315,21 @@ def buildDualShape(spheres):
 	simple_graph_edges = [];
 	for node_i in hypergraphNodes:
 		simp_node_i = find_simple_node( node_i, simple_graph_nodes );
+		#print node_i.nodes[0];
 		for node_j in hypergraphNodes:
 			simp_node_j = find_simple_node( node_j, simple_graph_nodes );
 			if node_i.has_edge( node_j, edges ):
 				edge = ( simp_node_i, simp_node_j, 1 );
-				#pygame.draw.line(DISPLAYSURF, (255,0,0), (int(node_i.nodes[0][0]), int(node_i.nodes[0][1])), (int(node_j.nodes[0][0]), int(node_j.nodes[0][1])), 2 );
-				#pygame.display.update();
+				pygame.draw.line(DISPLAYSURF, (255,0,0), (int(node_i.nodes[0][0]), int(node_i.nodes[0][1])), (int(node_j.nodes[0][0]), int(node_j.nodes[0][1])), 2 );
+				pygame.display.update();
 				simple_graph_edges.append( edge );
 
+	for node in simple_graph_nodes:
+		print node.value.nodes[0];
+		node.value = ( node.value.nodes[0][0], node.value.nodes[0][1]);
+		
+
+	
 	graph = Graph();
 	graph.add_nodes( simple_graph_nodes );
 	graph.add_edges( simple_graph_edges );
@@ -333,6 +340,7 @@ def buildDualShape(spheres):
 	breaked_graph.saveJson('./graph_drawing/data/broken_graph.json');
 	'''
 
+    
 
 	pygame.image.save( DISPLAYSURF, "AlphaShape.PNG" );
 

### 2014-08-22 topology/graph.py

@@ -284,7 +284,7 @@ class Graph:
 		linkStr = "";
 		nodes = self.graphdict.keys();
 		for node in nodes:
-			nodeStr += "\t\t{\"name\":\"" + str(node.name) + "\", \"group\":"+ str(node.group) +"},\n";
+			nodeStr += "\t\t{\"name\":\"" + str(node.name) + "\", \"group\":"+ str(node.group) + ", \"value\":\"" + str(node.value)  +"\"},\n";
 			for edge in self.graphdict[node]:
 				linkStr += "\t\t{\"source\":"+ str(nodes.index(node)) +",\"target\":" + str(nodes.index(edge[0])) + ",\"value\":"+ str(edge[1]) +"},\n";
 

### 2014-08-22 world.py

@@ -10,17 +10,17 @@ from geometry import *
 
 
 class World:
-    '''World class'''
-    def __init__( self, width, height, obstacles, robot ):
-        self.WIDTH = width;
-        self.HEIGHT = height;
-        self.obstMgr = ObstManager( obstacles );
-        self.robot = robot;
+	'''World class'''
+	def __init__( self, width, height, obstacles, robot ):
+		self.WIDTH = width;
+		self.HEIGHT = height;
+		self.obstMgr = ObstManager( obstacles );
+		self.robot = robot;
 
-    def render(self, surface):
-        self.obstMgr.intersects( self.robot );
-        self.obstMgr.render(surface);
-        self.robot.render(surface);
+	def render(self, surface):
+		self.obstMgr.intersects( self.robot );
+		self.obstMgr.render(surface);
+		self.robot.render(surface);
 
 
 WIDTH = 800;
@@ -50,13 +50,13 @@ gameWorld = World( WIDTH, HEIGHT, obsts, diffDrive );
 
 
 ##################################################
-#####           Render the world
+#####		   Render the world
 ##################################################
 DISPLAYSURF.fill((240,235,240))
 for event in pygame.event.get():
-    if event.type == QUIT:
-        pygame.quit()
-        sys.exit()
+	if event.type == QUIT:
+		pygame.quit()
+		sys.exit()
 gameWorld.render( DISPLAYSURF );
 pygame.display.update();
 #pygame.image.save( DISPLAYSURF, 'world.PNG' );
@@ -64,19 +64,19 @@ pygame.display.update();
 
 '''
 while True:
-    DISPLAYSURF.fill((240,235,240))
+	DISPLAYSURF.fill((240,235,240))
 
-    #drawCircle( DISPLAYSURF, (850,850), 100 );
+	#drawCircle( DISPLAYSURF, (850,850), 100 );
 
-    for event in pygame.event.get():
-        if event.type == QUIT:
-            pygame.quit()
-            sys.exit()
-    
-    gameWorld.render( DISPLAYSURF );
+	for event in pygame.event.get():
+		if event.type == QUIT:
+			pygame.quit()
+			sys.exit()
+	
+	gameWorld.render( DISPLAYSURF );
 
-    pygame.display.update();
-    pass
+	pygame.display.update();
+	pass
 
 pygame.quit();
 '''
@@ -89,11 +89,12 @@ pygame.quit();
 
 
 ##################################################
[…]

### 2014-08-23 Writing/Final/article.tex
Writing Update

@@
 	\center{\includegraphics[scale=0.3]{./pics/Samples.PNG}}
-	\caption{\label{Samples} Samples got by the algorithm}
+	\caption{\label{Samples} Samples got by the algorithm. We have 43 medial axis samples(gray balls), and 76 regular samples(green balls). }
 \end{figure}
@@
 
+\indent Result of breaking Figure \ref{simplifiedgraph} can be seen in Figure \ref{broken}.
+
 \indent By breaking a graph into several parts, we virtually break the space into several subspaces. In this sense, our method can be viewed as a space partition strategy.
@@
 	\caption{\label{brokengraphs} Some examples of breaking a graph. Graphs are visualized using $d3.js$ $(http://www.d3js.org)$ }
+\end{figure}
+
+\begin{figure}
+	\center{ \includegraphics[scale=0.4]{./pics/broken_graph.png} }
+	\caption{\label{broken}} Broken graph of Figure \ref{simplifiedgraph}. The graph is divided two parts. Merging these two components will create loop. 
 \end{figure}
@@
   \subsection{Fast Planning}
-  \indent\indent By breaking a graph into several parts, we virtually break the space into several subspaces.
-In this sense, our method can be viewed as a space partition strategy.
+  \indent\indent By breaking a graph into several components, we virtually break the space into several subspaces.
 Every subspace is managed by a tree, and trees are connected with shared common nodes.
@@
 
-  \indent
+  \indent Consider each component as a graph node, connecting them will form a graph. A fast path searching algorithm will be: 1. search path between components, then 2. search path in each component.
+
+  \indent In the worst case of searching a graph, the time is
+
+  \indent fdaaaaaaaaaaaaaaaaaaaaaaaaagfdasgdsfagfdsafdsagdsafdsf
 
@@
 \section{Experiments}\label{experiments}
-We now describe the some experiments and their results.
+\indent\indent We now describe some experiments and their results.
+We are planning for a point robot in workspace shown in Figure \ref{fig:Medial Axis}.
+Thus the workspace is the same as configuration space.
 
+\subsection{Coverage of the space}
+
+\indent\indent Figure \ref{PvB} shows the relation between the number of initial configurations from Phase 1 and the number balls got in Phase 2.
+X axis ranges from  100 - 6000 with 100 increment as the number of initial configurations.
+Every setting runs 8 times.
+The number of balls in the Y axis is the average value of 8 results for each setting.
+With the increase of initial random configurations, the number of balls tends to be 120.
+
+\indent Figure \ref{fig:Medial Axis} is a $800\times 800$ workspace for a point robot.
+By analyzing each pixel, we can know whether it is covered by balls and get its distance from obstacle.
+Figure \ref{uncovered} shows the relation between the number of initial configurations, number of pixels uncovered by balls and their distance from obstacles.
+The Y axis ranges from 100-7000 with 200 increment as numbers of initial random configurations in Phase 1.
+X axis indicates the distance from obstacles.
+And Z axis is the number of pixels uncovered by balls.
+The minimum radius of balls is 10.
+As we can see, with the increase of initial configurations, the number of uncovered pixels drops sharply.
+The maximum distance uncovered pixel also decrease very quickly.
+
+\begin{figure}
+	\center{ \includegraphics[scale=0.2]{./pics/Analysis_PvB.png} }
+	\caption{\label{PvB}} Relation between number of initial configurations and balls. The number of balls tends to be around 120.
+\end{figure}
+
+\begin{figure}
+	\center{ \includegraphics[scale=0.4]{./pics/overview_uncovered_pixels.PNG} }
+	\caption{\label{uncovered}} Relation between number of initial configurations, uncovered pixels and their distance from obstacles.
+\end{figure}
+
+\subsection{Searching for Optimal Path}
+
+\indent\indent Balls generated in Phase 2 can be used to find near optimal paths using \emph{A*} algorithm.
+We are virtually building a graph by discretizing balls to boundary configurations.
+Every configuration is ``connected" to boundary configurations of the ball it is in.
+The difference between a \emph{PRM} is that we are not storing any connection information between configurations explicitly.
+
+\begin{figure}
+	\center{ \includegraphics[scale=0.35]{./pics/AstarSearch.PNG} }
+	\caption{\label{Astar}} Using \emph{A*} search algorithm to find an optimal path.
+We discretize balls to configurations on their boundaries.
+Thus, successors of a configuration are other boundary configurations of the ball current configuration is in.
+\end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \bibitem{betti wiki} ``Betti Number", From Wikipedia -- The Free Encyclopedia. ( $http://en.wikipedia.org/wiki/Betti_number$ )   
-  \bibitem{cyclomatic} GYULA KAROLYI, AMBRUS PAL, ``The cyclomatic number of connected graphs without solvable orbits", Periodica Mathematica Hungarica, 01/2007; 
+  \bibitem{cyclomatic} Gyula Karolyi, Ambrus Pal, ``The cyclomatic number of connected graphs without solvable orbits", Periodica Mathematica Hungarica, 01/2007; 
   \bibitem{Edel Book}Edelsbrunner, Herbert, and John Harer. ``Computational topology: an introduction." American Mathematical Soc., 2010. page. 88 - 93.

### 2014-08-23 topology/alphashape.py

@@ -334,11 +334,11 @@ def buildDualShape(spheres):
 	graph.add_nodes( simple_graph_nodes );
 	graph.add_edges( simple_graph_edges );
 	graph.saveJson('./graph_drawing/data/graph2.json');
-	'''
+	
 	graphBreaker = GraphBreaker(graph);
 	breaked_graph = graphBreaker.break_it();
 	breaked_graph.saveJson('./graph_drawing/data/broken_graph.json');
-	'''
+	
 
     
 

### 2014-08-23 topology/graph.py

@@ -182,9 +182,9 @@ class Graph:
 		new_graph_loop_free = merged_graph.loop_free();
 
 		nodes = merged_graph.get_all_nodes();
-		for node in nodes:
-			if len(merged_graph.get_edges_of( node )) > 2:
-				return False;
+		#for node in nodes:
+		#	if len(merged_graph.get_edges_of( node )) > 2:
+		#		return False;
 
 		return share_nodes and new_graph_loop_free;
 

### 2014-08-29 Writing/Final/article.tex
updates

@@
 
-\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, reconnect these retracted points with other ones using their previous connection.
+\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, while keep check the 1st betti number of these merged 2-simplices, reconnect these retracted points with other ones using their previous connection information.
 By doing so, we got a simple graph that characterize the topology of \emph{C-space}.

### 2014-08-30 Writing/Final/article.tex
update writing and different path topology

--- 2014-08-23 Writing/Final/article.tex
@@
 
+\indent While computing the betti number for filed triangles in 2D is not difficult too.
+Delfinado, et al, \cite{incre_betti} provided an incremental algorithm to compute betti numbers in arbitrary dimensions.
+In our case, we need only 1st betti number.
+Its algorithm can be stated as:
+
+\begin{algorithmic}[1]
+	\Function {IncrementalBetti}{$\sigma_1, \sigma_2, ..., \sigma_m$}
+		\State $\beta_0 = \beta_1 = \beta_2 = 0$
+		\For {$i \in $ \emph{0 to m}}
+			\If {$\sigma_i$ \emph{belongs to a k-cycle of $K_i$}}
+				\State $\beta_k \gets \beta_k + 1$
+			\Else
+				\State $\beta_{k-1} \gets \beta_{k-1} -1$
+			\EndIf
+		\EndFor
+	\EndFunction 
+\end{algorithmic}
+
+where $\sigma_1, \sigma_2, ..., \sigma_m$ is a sequence of simplices, and $K_i = \{ \sigma_1, \sigma_2, ..., \sigma_i \}$.
+
+\indent The proof of correctness of the algorithm can be found in \cite{incre_betti}. \\
+
 \indent H. Edelsbrunner introduced a way to compute \emph{n-th} Betti number in \cite{Edel Book}, where he uses gaussian elimination to compute the Betti numbers with adjacency matrix.
@@
 \begin{figure}
-	\center{\includegraphics[scale=0.26]{./pics/Torus.png}}
+	\center{\includegraphics[scale=0.28]{./pics/Torus.png}}
 	\caption{\label{fig:Torus} The torus has one connected component($\beta_0$), two circular holes ($\beta_1$,the one in the center and the one in the middle of the "donut"), and one two-dimensional void ($\beta_2$, the inside of the "donut").
@@
 
-\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, reconnect these retracted points with other ones using their previous connection.
+\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, while keep check the 1st betti number of these merged 2-simplices( using the algorithm described in \cite{incre_betti} ), reconnect these retracted points with other ones using their previous connection information.
 By doing so, we got a simple graph that characterize the topology of \emph{C-space}.
@@
 
-  \indent In the worst case of searching a graph, the time is
-
-  \indent fdaaaaaaaaaaaaaaaaaaaaaaaaagfdasgdsfagfdsafdsagdsafdsf
+  \indent In the worst case of searching a graph, the time is exponential to the length of the path.
+but it could be polynomial if the graph is actually a tree.
+While breaking a graph into several components, these components form a new graph with much less nodes.
+Even in the worst case, the search for path between components can be much faster than original graph.
+Then we search in each components(trees) with smaller size compare to the whole graph.
+The time cost should be less then search the original graph directly.
 
@@
 \end{figure}
+
+\subsection{Different Homotopy Type Paths }
+\indent\indent In last section, we searched the near optimal path between two configurations. Now we will show how to find paths with different homotopy types.
+
+\indent The corresponding start and goal nodes in the simplified graph( Figure \ref{simplifiedgraph} ) is 12 and 21.
+Searching the graph for all paths will give us paths with different homotopy types.
+Figure \ref{paths} shows the 8 different paths.
+
+\begin{enumerate}
+	\item 12--6--19--10--2--0--4--8--1--20--7--21	
+	\item 12--6--19--10--2--0--11--14--21	
+	\item 12--6--19--10--2--23--5--17--3--1--8--4--0--11--14--21	
+	\item 12--6--19--10--2--23--5--17--3--1--20--7--21	
+	\item 12--13--9--3--1--8--4--0--11--14--21	
+	\item 12--13--9--3--1--20--7--21	
+	\item 12--13--9--3--17--5--23--2--0--4--8--1--20--7--21	
+	\item	12--13--9--3--17--5--23--2--0--11--14--21	
+\end{enumerate}
+
+\begin{figure}
+	{\includegraphics[scale=0.28]{./pics/paths/1.png}}
+	{\includegraphics[scale=0.28]{./pics/paths/2.png}}
+	{\includegraphics[scale=0.28]{./pics/paths/3.png}}
+	{\includegraphics[scale=0.28]{./pics/paths/4.png}}
+	{\includegraphics[scale=0.28]{./pics/paths/5.png}}
+	{\includegraphics[scale=0.28]{./pics/paths/6.png}}
+	{\includegraphics[scale=0.28]{./pics/paths/7.png}}
+	{\includegraphics[scale=0.28]{./pics/paths/8.png}}
+	\caption{\label{paths} 8 paths with different homotopy types. }
+\end{figure}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\indent Our next direction is to study the properties and applications of weighted $\alpha$-shape, especially applications in bioinformatics and chemistry, then extend to high dimensions.
+\indent There are many directions we can go from here.
 
-\indent Another direction will be studying the topology using the topology roadmap we constructed. Its value is underestimated in this paper, and I believe we can find more there.
+\indent We can use the topology roadmap to study paths and their topology in C-space.
+We can analyze the shape of C-space and locate large open area.
+We can try to use this presentations for nonholonomic motion planning problems.
 
@@
 \begin{thebibliography}{1}
+  \bibitem{incre_betti} Delfinado, Cecil Jose A., and Herbert Edelsbrunner.
+"An incremental algorithm for Betti numbers of simplicial complexes on the 3-sphere." Computer Aided Geometric Design 12.7 (1995): 771-784.
   \bibitem{weifu} Weifu Wang, Devin Balkcom, Amit Chakrabarti, ``A fast streaming spanner algorithm for incrementally constructing sparse roadmaps", IROS 2013.

### 2014-08-30 topology/alphashape.py

@@ -325,7 +325,7 @@ def buildDualShape(spheres):
 				simple_graph_edges.append( edge );
 
 	for node in simple_graph_nodes:
-		print node.value.nodes[0];
+		#print node.value.nodes[0];
 		node.value = ( node.value.nodes[0][0], node.value.nodes[0][1]);
 		
 
@@ -334,12 +334,19 @@ def buildDualShape(spheres):
 	graph.add_nodes( simple_graph_nodes );
 	graph.add_edges( simple_graph_edges );
 	graph.saveJson('./graph_drawing/data/graph2.json');
-	
+	'''
 	graphBreaker = GraphBreaker(graph);
 	breaked_graph = graphBreaker.break_it();
 	breaked_graph.saveJson('./graph_drawing/data/broken_graph.json');
-	
+	'''
 
+	paths = graph.find_all_paths(simple_graph_nodes[12], simple_graph_nodes[21]);
+	for path in paths:
+		print "=========================================\n";
+		pathStr = '';
+		for node in path:
+			pathStr += str(node.name) + '\t';
+		print pathStr
     
 
 	pygame.image.save( DISPLAYSURF, "AlphaShape.PNG" );

### 2014-08-30 topology/graph.py

@@ -232,7 +232,7 @@ class Graph:
 		for edge in self.graphdict[start]:
 			node = edge[0];
 			if node not in path:
-				newpaths = find_all_paths(self.graphdict, node, end, path);
+				newpaths = self.find_all_paths( node, end, path);
 				for newpath in newpaths:
 					paths.append(newpath);
 		return paths;
